### 2024-08-29 src/IEEE-conference-template-062824.tex
update

\documentclass[conference]{IEEEtran}
\IEEEoverridecommandlockouts
% The preceding line is only needed to identify funding in the first footnote. If that is unneeded, please comment it out.
%Template version as of 6/27/2024

\usepackage{cite}
\usepackage{amsmath,amssymb,amsfonts}
\usepackage{algorithmic}
\usepackage{graphicx}
\usepackage{textcomp}
\usepackage{xcolor}
\def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
    T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}
\begin{document}

\title{TSSLM: Target Speaker Separation using Discrete Tokens and Language Models\\
\thanks{Identify applicable funding agency here. If none, delete this.}
}

\author{\IEEEauthorblockN{1\textsuperscript{st} Beilong Tang}
\IEEEauthorblockA{\textit{Duke Kunshan University} \\
\textit{name of organization (of Aff.)}\\
Kunshan, China \\
bt132@duke.edu}
\and
\IEEEauthorblockN{2\textsuperscript{nd} Given Name Surname}
\IEEEauthorblockA{\textit{dept. name of organization (of Aff.)} \\
\textit{name of organization (of Aff.)}\\
City, Country \\
email address or ORCID}
\and
\IEEEauthorblockN{3\textsuperscript{rd} Given Name Surname}
\IEEEauthorblockA{\textit{dept. name of organization (of Aff.)} \\
\textit{name of organization (of Aff.)}\\
City, Country \\
email address or ORCID}
\and
\IEEEauthorblockN{4\textsuperscript{th} Given Name Surname}
\IEEEauthorblockA{\textit{dept. name of organization (of Aff.)} \\
\textit{name of organization (of Aff.)}\\
City, Country \\
email address or ORCID}
\and
\IEEEauthorblockN{5\textsuperscript{th} Given Name Surname}
\IEEEauthorblockA{\textit{dept. name of organization (of Aff.)} \\
\textit{name of organization (of Aff.)}\\
City, Country \\
email address or ORCID}
\and
\IEEEauthorblockN{6\textsuperscript{th} Given Name Surname}
\IEEEauthorblockA{\textit{dept. name of organization (of Aff.)} \\
\textit{name of organization (of Aff.)}\\
City, Country \\
email address or ORCID}
}

\maketitle

\begin{abstract}
This document is a model and instructions for \LaTeX.
This and the IEEEtran.cls file define the components of your paper [title, text, heads, etc.]. *CRITICAL: Do Not Use Symbols, Special Characters, Footnotes, 
or Math in Paper Title or Abstract.
\end{abstract}

\begin{IEEEkeywords}
component, formatting, style, styling, insert.
\end{IEEEkeywords}

\section{Introduction}
This document is a model and instructions for \LaTeX.
Please observe the conference page limits. For more information about how to become an IEEE Conference author or how to write your paper, please visit   IEEE Conference Author Center website: https://conferences.ieeeauthorcenter.ieee.org/.

\subsection{Maintaining the Integrity of the Specifications}

The IEEEtran class file is used to format your paper and style the text. All margins, 
column widths, line spaces, and text fonts are prescribed; please do not 
alter them. You may note peculiarities. For example, the head margin
measures proportionately more than is customary. This measurement 
and others are deliberate, using specifications that anticipate your paper 
as one part of the entire proceedings, and not as an independent document. 
Please do not revise any of the current designations.

\section{Prepare Your Paper Before Styling}
Before you begin to format your paper, first write and save the content as a 
separate text file. Complete all content and organizational editing before 
formatting. Please note sections \ref{AA} to \ref{FAT} below for more information on 
proofreading, spelling and grammar.

Keep your text and graphic files separate until after the text has been 
formatted and styled. Do not number text heads---{\LaTeX} will do that 
for you.

\subsection{Abbreviations and Acronyms}\label{AA}
Define abbreviations and acronyms the first time they are used in the text, 
even after they have been defined in the abstract. Abbreviations such as 
IEEE, SI, MKS, CGS, ac, dc, and rms do not have to be defined. Do not use 
abbreviations in the title or heads unless they are unavoidable.

\subsection{Units}
\begin{itemize}
\item Use either SI (MKS) or CGS as primary units. (SI units are encouraged.) English units may be used as secondary units (in parentheses). An exception would be the use of English units as identifiers in trade, such as ``3.5-inch disk drive''.
\item Avoid combining SI and CGS units, such as current in amperes and magnetic field in oersteds. This often leads to confusion because equations do not balance dimensionally. If you must use mixed units, clearly state the units for each quantity that you use in an equation.
\item Do not mix complete spellings and abbreviations of units: ``Wb/m\textsuperscript{2}'' or ``webers per square meter'', not ``webers/m\textsuperscript{2}''. Spell out units when they appear in text: ``. . . a few henries'', not ``. . . a few H''.
\item Use a zero before decimal points: ``0.25'', not ``.25''. Use ``cm\textsuperscript{3}'', not ``cc''.)
\end{itemize}

\subsection{Equations}
Number equations consecutively. To make your 
equations more compact, you may use the solidus (~/~), the exp function, or 
appropriate exponents. Italicize Roman symbols for quantities and variables, 
but not Greek symbols. Use a long dash rather than a hyphen for a minus 
sign. Punctuate equations with commas or periods when they are part of a 
sentence, as in:
\begin{equation}
a+b=\gamma\label{eq}
\end{equation}

Be sure that the 
symbols in your equation have been defined before or immediately following 
the equation. Use ``\eqref{eq}'', not ``Eq.~\eqref{eq}'' or ``equation \eqref{eq}'', except at 
the beginning of a sentence: ``Equation \eqref{eq} is . . .''

\subsection{\LaTeX-Specific Advice}

Please use ``soft'' (e.g., \verb|\eqref{Eq}|) cross references instead
of ``hard'' references (e.g., \verb|(1)|). That will make it possible
to combine sections, add equations, or change the order of figures or
citations without having to go through the file line by line.

Please don't use the \verb|{eqnarray}| equation environment. Use
\verb|{align}| or \verb|{IEEEeqnarray}| instead. The \verb|{eqnarray}|
environment leaves unsightly spaces around relation symbols.

Please note that the \verb|{subequations}| environment in {\LaTeX}
will increment the main equation counter even when there are no
equation numbers displayed. If you forget that, you might write an
article in which the equation numbers skip from (17) to (20), causing
the copy editors to wonder if you've discovered a new method of
counting.

{\BibTeX} does not work by magic. It doesn't get the bibliographic
data from thin air but from .bib files. If you use {\BibTeX} to produce a
bibliography you must send the .bib files.

{\LaTeX} can't read your mind. If you assign the same label to a
subsubsection and a table, you might find that Table I has been cross
referenced as Table IV-B3.

{\LaTeX} does not have precognitive abilities. If you put a
\verb|\label| command before the command that updates the counter it's
supposed to be using, the label will pick up the last counter to be
cross referenced instead. In particular, a \verb|\label| command
should not go before the caption of a figure or a table.

Do not use \verb|\nonumber| inside the \verb|{array}| environment. It
will not stop equation numbers inside \verb|{array}| (there won't be
any anyway) and it might stop a wanted equation number in the
surrounding equation.

\subsection{Some Common Mistakes}\label{SCM}
\begin{itemize}
\item The word ``data'' is plural, not singular.
\item The subscript for the permeability of vacuum $\mu_{0}$, and other common scientific constants, is zero with subscript formatting, not a lowercase letter ``o''.
\item In American English, commas, semicolons, periods, question and exclamation marks are located within quotation marks only when a complete thought or name is cited, such as a title or full quotation. When quotation marks are used, instead of a bold or italic typeface, to highlight a word or phrase, punctuation should appear outside of the quotation marks. A parenthetical phrase or statement at the end of a sentence is punctuated outside of the closing parenthesis (like this). (A parenthetical sentence is punctuated within the parentheses.)
\item A graph within a graph is an ``inset'', not an ``insert''. The word alternatively is preferred to the word ``alternately'' (unless you really mean something that alternates).
\item Do not use the word ``essentially'' to mean ``approximately'' or ``effectively''.
\item In your paper title, if the words ``that uses'' can accurately replace the word ``using'', capitalize the ``u''; if not, keep using lower-cased.
\item Be aware of the different meanings of the homophones ``affect'' and ``effect'', ``complement'' and ``compliment'', ``discreet'' and ``discrete'', ``principal'' and ``principle''.
\item Do not confuse ``imply'' and ``infer''.
\item The prefix ``non'' is not a word; it should be joined to the word it modifies, usually without a hyphen.
\item There is no period after the ``et'' in the Latin abbreviation ``et al.''.
\item The abbreviation ``i.e.'' means ``that is'', and the abbreviation ``e.g.'' means ``for example''.
\end{itemize}
An excellent style manual for science writers is \cite{b7}.

\subsection{Authors and Affiliations}\label{AAA}
\textbf{The class file is designed for, but not limited to, six authors.} A 
minimum of one author is required for all conference articles. Author names 
should be listed starting from left to right and then moving down to the 
next line. This is the author sequence that will be used in future citations 
and by indexing services. Names should not be listed in columns nor group by 
affiliation. Please keep your affiliations as succinct as possible (for 
example, do not differentiate among departments of the same organization).

\subsection{Identify the Headings}\label{ITH}
Headings, or heads, are organizational devices that guide the reader through 
your paper. There are two types: component heads and text heads.

Component heads identify the different components of your paper and are not 
topically subordinate to each other. Examples include Acknowledgments and 
References and, for these, the correct style to use is ``Heading 5''. Use 
``figure caption'' for your Figure captions, and ``table head'' for your 
table title. Run-in heads, such as ``Abstract'', will require you to apply a 
style (in this case, italic) in addition to the style provided by the drop 
down menu to differentiate the head from the text.

Text heads organize the topics on a relational, hierarchical basis. For 
example, the paper title is the primary text head because all subsequent 
material relates and elaborates on this one topic. If there are two or more 
sub-topics, the next level head (uppercase Roman numerals) should be used 
and, conversely, if there are not at least two sub-topics, then no subheads 
should be introduced.

\subsection{Figures and Tables}\label{FAT}
\paragraph{Positioning Figures and Tables} Place figures and tables at the top and 
bottom of columns. Avoid placing them in the middle of columns. Large 
figures and tables may span across both columns. Figure captions should be 
below the figures; table heads should appear above the tables. Insert 
figures and tables after they are cited in the text. Use the abbreviation 
``Fig.~\ref{fig}'', even at the beginning of a sentence.

\begin{table}[htbp]
\caption{Table Type Styles}
\begin{center}
\begin{tabular}{|c|c|c|c|}
\hline
\textbf{Table}&\multicolumn{3}{|c|}{\textbf{Table Column Head}} \\
\cline{2-4} 
\textbf{Head} & \textbf{\textit{Table column subhead}}& \textbf{\textit{Subhead}}& \textbf{\textit{Subhead}} \\
\hline
copy& More table copy$^{\mathrm{a}}$& &  \\
\hline
\multicolumn{4}{l}{$^{\mathrm{a}}$Sample of a Table footnote.}
\end{tabular}
\label{tab1}
\end{center}
\end{table}

\begin{figure}[htbp]
\centerline{\includegraphics{fig1.png}}
\caption{Example of a figure caption.}
\label{fig}
\end{figure}

Figure Labels: Use 8 point Times New Roman for Figure labels. Use words 
rather than symbols or abbreviations when writing Figure axis labels to 
avoid confusing the reader. As an example, write the quantity 
``Magnetization'', or ``Magnetization, M'', not just ``M''. If including 
units in the label, present them within parentheses. Do not label axes only 
with units. In the example, write ``Magnetization (A/m)'' or ``Magnetization 
\{A[m(1)]\}'', not just ``A/m''. Do not label axes with a ratio of 
quantities and units. For example, write ``Temperature (K)'', not 
``Temperature/K''.

\section*{Acknowledgment}

The preferred spelling of the word ``acknowledgment'' in America is without 
an ``e'' after the ``g''. Avoid the stilted expression ``one of us (R. B. 
G.) thanks $\ldots$''. Instead, try ``R. B. G. thanks$\ldots$''. Put sponsor 
acknowledgments in the unnumbered footnote on the first page.

\section*{References}

Please number citations consecutively within brackets \cite{b1}. The 
sentence punctuation follows the bracket \cite{b2}. Refer simply to the reference 
number, as in \cite{b3}---do not use ``Ref. \cite{b3}'' or ``reference \cite{b3}'' except at 
the beginning of a sentence: ``Reference \cite{b3} was the first $\ldots$''

Number footnotes separately in superscripts. Place the actual footnote at 
the bottom of the column in which it was cited. Do not put footnotes in the 
abstract or reference list. Use letters for table footnotes.

Unless there are six authors or more give all authors' names; do not use 
``et al.''. Papers that have not been published, even if they have been 
submitted for publication, should be cited as ``unpublished'' \cite{b4}. Papers 
that have been accepted for publication should be cited as ``in press'' \cite{b5}. 
Capitalize only the first word in a paper title, except for proper nouns and 
element symbols.

For papers published in translation journals, please give the English 
citation first, followed by the original foreign-language citation \cite{b6}.

\begin{thebibliography}{00}
\bibitem{b1} G. Eason, B. Noble, and I. N. Sneddon, ``On certain integrals of Lipschitz-Hankel type involving products of Bessel functions,'' Phil. Trans. Roy. Soc. London, vol. A247, pp. 529--551, April 1955.
\bibitem{b2} J. Clerk Maxwell, A Treatise on Electricity and Magnetism, 3rd ed., vol. 2. Oxford: Clarendon, 1892, pp.68--73.
\bibitem{b3} I. S. Jacobs and C. P. Bean, ``Fine particles, thin films and exchange anisotropy,'' in Magnetism, vol. III, G. T. Rado and H. Suhl, Eds. New York: Academic, 1963, pp. 271--350.
\bibitem{b4} K. Elissa, ``Title of paper if known,'' unpublished.
\bibitem{b5} R. Nicole, ``Title of paper with only first word capitalized,'' J. Name Stand. Abbrev., in press.
\bibitem{b6} Y. Yorozu, M. Hirano, K. Oka, and Y. Tagawa, ``Electron spectroscopy studies on magneto-optical media and plastic substrate interface,'' IEEE Transl. J. Magn. Japan, vol. 2, pp. 740--741, August 1987 [Digests 9th Annual Conf. Magnetics Japan, p. 301, 1982].
\bibitem{b7} M. Young, The Technical Writer's Handbook. Mill Valley, CA: University Science, 1989.
\bibitem{b8} D. P. Kingma and M. Welling, ``Auto-encoding variational Bayes,'' 2013, arXiv:1312.6114. [Online]. Available: https://arxiv.org/abs/1312.6114
\bibitem{b9} S. Liu, ``Wi-Fi Energy Detection Testbed (12MTC),'' 2023, gitHub repository. [Online]. Available: https://github.com/liustone99/Wi-Fi-Energy-Detection-Testbed-12MTC
\bibitem{b10} ``Treatment episode data set: discharges (TEDS-D): concatenated, 2006 to 2009.'' U.S. Department of Health and Human Services, Substance Abuse and Mental Health Services Administration, Office of Applied Studies, August, 2013, DOI:10.3886/ICPSR30122.v2
\bibitem{b11} K. Eves and J. Valasek, ``Adaptive control for singularly perturbed systems examples,'' Code Ocean, Aug. 2023. [Online]. Available: https://codeocean.com/capsule/4989235/tree
\end{thebibliography}

\vspace{12pt}
\color{red}
IEEE conference templates contain guidance text for composing and formatting conference papers. Please ensure that all template text is removed from your conference paper prior to submission to the conference. Failure to remove the template text from your paper may result in your paper not being published.

\end{document}

### 2024-09-02 src/paper.tex
update

--- 2024-08-29 src/IEEE-conference-template-062824.tex
@@
 
-\title{TSSLM: Target Speaker Separation using Discrete Tokens and Language Models\\
+\title{Exploration in Target Speaker Separation using Discrete Tokens and Language Models\\
 \thanks{Identify applicable funding agency here. If none, delete this.}
@@
 \IEEEauthorblockA{\textit{Duke Kunshan University} \\
-\textit{name of organization (of Aff.)}\\
+% \textit{name of organization (of Aff.)}\\
 Kunshan, China \\
@@
 email address or ORCID}
-\and
-\IEEEauthorblockN{4\textsuperscript{th} Given Name Surname}
-\IEEEauthorblockA{\textit{dept. name of organization (of Aff.)} \\
-\textit{name of organization (of Aff.)}\\
-City, Country \\
-email address or ORCID}
-\and
-\IEEEauthorblockN{5\textsuperscript{th} Given Name Surname}
-\IEEEauthorblockA{\textit{dept. name of organization (of Aff.)} \\
-\textit{name of organization (of Aff.)}\\
-City, Country \\
-email address or ORCID}
-\and
-\IEEEauthorblockN{6\textsuperscript{th} Given Name Surname}
-\IEEEauthorblockA{\textit{dept. name of organization (of Aff.)} \\
-\textit{name of organization (of Aff.)}\\
-City, Country \\
-email address or ORCID}
+% \and
+% \IEEEauthorblockN{4\textsuperscript{th} Given Name Surname}
+% \IEEEauthorblockA{\textit{dept. name of organization (of Aff.)} \\
+% \textit{name of organization (of Aff.)}\\
+% City, Country \\
+% email address or ORCID}
+% \and
+% \IEEEauthorblockN{5\textsuperscript{th} Given Name Surname}
+% \IEEEauthorblockA{\textit{dept. name of organization (of Aff.)} \\
+% \textit{name of organization (of Aff.)}\\
+% City, Country \\
+% email address or ORCID}
+% \and
+% \IEEEauthorblockN{6\textsuperscript{th} Given Name Surname}
+% \IEEEauthorblockA{\textit{dept. name of organization (of Aff.)} \\
+% \textit{name of organization (of Aff.)}\\
+% City, Country \\
+% email address or ORCID}
 }
@@
 \begin{IEEEkeywords}
-component, formatting, style, styling, insert.
+target speaker separation, language models, audio discretization
 \end{IEEEkeywords}
@@
 \section{Introduction}
-This document is a model and instructions for \LaTeX.
-Please observe the conference page limits.
-For more information about how to become an IEEE Conference author or how to write your paper, please visit   IEEE Conference Author Center website: https://conferences.ieeeauthorcenter.ieee.org/.
-
-\subsection{Maintaining the Integrity of the Specifications}
-
-The IEEEtran class file is used to format your paper and style the text. All margins, 
-column widths, line spaces, and text fonts are prescribed; please do not 
-alter them. You may note peculiarities. For example, the head margin
-measures proportionately more than is customary. This measurement 
-and others are deliberate, using specifications that anticipate your paper 
-as one part of the entire proceedings, and not as an independent document. 
-Please do not revise any of the current designations.
-
-\section{Prepare Your Paper Before Styling}
-Before you begin to format your paper, first write and save the content as a 
-separate text file. Complete all content and organizational editing before 
-formatting. Please note sections \ref{AA} to \ref{FAT} below for more information on 
-proofreading, spelling and grammar.
-
-Keep your text and graphic files separate until after the text has been 
-formatted and styled. Do not number text heads---{\LaTeX} will do that 
-for you.
-
-\subsection{Abbreviations and Acronyms}\label{AA}
-Define abbreviations and acronyms the first time they are used in the text, 
-even after they have been defined in the abstract. Abbreviations such as 
-IEEE, SI, MKS, CGS, ac, dc, and rms do not have to be defined. Do not use 
-abbreviations in the title or heads unless they are unavoidable.
+Speech separation is a fundamental task in separating two speakers' voices from a mixture.
 
@@
 Unless there are six authors or more give all authors' names; do not use 
-``et al.''. Papers that have not been published, even if they have been 
+``et al.''. Papers that \cite{b8} have not been published, even if they have been 
 submitted for publication, should be cited as ``unpublished'' \cite{b4}. Papers 
 that have been accepted for publication should be cited as ``in press'' \cite{b5}. 
-Capitalize only the first word in a paper title, except for proper nouns and 
+Capitalize only the \cite{b11}  first word \cite{b9} in a paper title, except for proper nouns and 
 element symbols.
 
-For papers published in translation journals, please give the English 
+For papers published in translation journals, please give the English \cite{b10}
 citation first, followed by the original foreign-language citation \cite{b6}.
-
-\begin{thebibliography}{00}
-\bibitem{b1} G.
-Eason, B.
-Noble, and I.
-N.
-Sneddon, ``On certain integrals of Lipschitz-Hankel type involving products of Bessel functions,'' Phil.
-Trans.
-Roy.
-Soc.
-London, vol.
-A247, pp.
-529--551, April 1955.
-\bibitem{b2} J. Clerk Maxwell, A Treatise on Electricity and Magnetism, 3rd ed., vol. 2. Oxford: Clarendon, 1892, pp.68--73.
-\bibitem{b3} I. S. Jacobs and C. P. Bean, ``Fine particles, thin films and exchange anisotropy,'' in Magnetism, vol. III, G. T. Rado and H. Suhl, Eds. New York: Academic, 1963, pp. 271--350.
-\bibitem{b4} K. Elissa, ``Title of paper if known,'' unpublished.
-\bibitem{b5} R. Nicole, ``Title of paper with only first word capitalized,'' J. Name Stand. Abbrev., in press.
-\bibitem{b6} Y.
-Yorozu, M.
-Hirano, K.
-Oka, and Y.
-Tagawa, ``Electron spectroscopy studies on magneto-optical media and plastic substrate interface,'' IEEE Transl.
-J.
-Magn.
-Japan, vol.
-2, pp.
-740--741, August 1987 [Digests 9th Annual Conf.
-Magnetics Japan, p.
-301, 1982].
-\bibitem{b7} M. Young, The Technical Writer's Handbook. Mill Valley, CA: University Science, 1989.
-\bibitem{b8} D. P. Kingma and M. Welling, ``Auto-encoding variational Bayes,'' 2013, arXiv:1312.6114. [Online]. Available: https://arxiv.org/abs/1312.6114
-\bibitem{b9} S. Liu, ``Wi-Fi Energy Detection Testbed (12MTC),'' 2023, gitHub repository. [Online]. Available: https://github.com/liustone99/Wi-Fi-Energy-Detection-Testbed-12MTC
-\bibitem{b10} ``Treatment episode data set: discharges (TEDS-D): concatenated, 2006 to 2009.'' U.S.
-Department of Health and Human Services, Substance Abuse and Mental Health Services Administration, Office of Applied Studies, August, 2013, DOI:10.3886/ICPSR30122.v2
-\bibitem{b11} K. Eves and J. Valasek, ``Adaptive control for singularly perturbed systems examples,'' Code Ocean, Aug. 2023. [Online]. Available: https://codeocean.com/capsule/4989235/tree
-\end{thebibliography}
+\bibliographystyle{IEEEtran}
+\bibliography{references}
 

### 2024-09-02 src/paper.tex
update

@@
 
-\title{Exploration in Target Speaker Separation using Discrete Tokens and Language Models\\
+\title{Exploration in Target Speaker Extraction using Discrete Tokens and Language Models\\
 \thanks{Identify applicable funding agency here. If none, delete this.}
@@
 \begin{IEEEkeywords}
-target speaker separation, language models, audio discretization
+target speaker extraction, speech separation, language models, audio discretization
 \end{IEEEkeywords}
@@
 \section{Introduction}
-Speech separation is a fundamental task in separating two speakers' voices from a mixture.
+Speech separation, the so-called cocktail party problem \cite{cocktail}, focuses on separating each individual speaker's source from a mixture with multiple speakers.
+In real life, speech signals are usually companied with background noise or other speakers' speeches. 
+Our humans might grasp the speech but machine is not the case.
+These signals may not be optimal for tasks like speaker verification. 
+Target speaker extraction is a sub-task of speech separation.
 

### 2024-09-02 src/paper.tex
update

@@
 Speech separation, the so-called cocktail party problem \cite{cocktail}, focuses on separating each individual speaker's source from a mixture with multiple speakers.
+This task is easy for humans but not for computers.
 In real life, speech signals are usually companied with background noise or other speakers' speeches. 
-Our humans might grasp the speech but machine is not the case.
-These signals may not be optimal for tasks like speaker verification. 
-Target speaker extraction is a sub-task of speech separation.
+These corrupted signals may not be optimal for tasks like speaker verification \cite{rao2019targetspeakerextractionoverlapped,9414017}, and speech recognition \cite{molkov2017SpeakerAwareNN, 8462661}, emphasizing the importance of this task.
+
+Unlike blind speech separation, which focuses on separating each utterance from a mixture 
+of known speakers, target speaker extraction aims at only extracting the 
+target speaker's voice given another auxiliary information of the target speaker. The separation
 

### 2024-09-02 src/paper.tex
update

@@
 
-\title{Exploration in Target Speaker Extraction using Discrete Tokens and Language Models\\
+\title{Exploration in Target Speaker Extraction using Discrete Representations 
 \thanks{Identify applicable funding agency here. If none, delete this.}
@@
 of known speakers, target speaker extraction aims at only extracting the 
-target speaker's voice given another auxiliary information of the target speaker. The separation
+target speaker's voice given another auxiliary information of the target speaker. Due to the 
+development of Deep Neural Network (DNN), many models nowadays are discriminative models. They 
+utilize a masking strategy to minimize the distance between the clean speech and estimated 
+speech directly \cite{luo2019conv,spex_plus,sepformer,sef_net}. However, these discriminative 
+models may not generalize well to unseen data and might even introduce unwanted distortions \cite{distortion}.
 

### 2024-09-03 src/paper.tex
update

@@
 models may not generalize well to unseen data and might even introduce unwanted distortions \cite{distortion}.
+To solve these issues, researchers have proposed generative models.
+This method aims to learn the underlying distribution of the target speaker’s voice and use this knowledge to generate the clean speech of the target speaker from a mixture of voices rather
+than directly mapping from mixed speech to clean speech. Some generative models, like diffusion
+models \cite{target_diff} and variational autoencoders (VAE) \cite{vae} have been studied.
+It has been demonstrated that generative models can achieve results comparable to those of discriminative models \cite{target_diff,tokensplit}.
+
+Recently, self-supervised Learning (SSL) models like HuBERT \cite{} and WavLM \cite{wavlm} have demonstrated
+excellent performances on many downstream tasks like blind speech separation,
 

### 2024-09-03 src/paper.tex
update

--- 2024-09-02 src/paper.tex
@@
 
-\title{Exploration in Target Speaker Extraction using Discrete Representations 
+\title{Exploration in Target Speaker Extraction using Discrete Representations and Language Models
 \thanks{Identify applicable funding agency here. If none, delete this.}
@@
 models may not generalize well to unseen data and might even introduce unwanted distortions \cite{distortion}.
+To solve these issues, researchers have proposed generative models.
+This method aims to learn the underlying distribution of the target speaker's voice and use this knowledge to generate the clean speech of the target speaker from a mixture of voices rather
+than directly mapping from mixed speech to clean speech. Some generative models, like diffusion
+models \cite{target_diff} and variational autoencoders (VAE) \cite{vae} have been studied.
+It has been demonstrated that generative models can achieve results comparable to those of discriminative models \cite{target_diff,tokensplit}.
+
+Recently, self-supervised Learning (SSL) models like HuBERT \cite{hubert} and WavLM \cite{wavlm} have demonstrated
+excellent performances on many downstream tasks \cite{superb}. These SSL models extract  
+continuous representations containing rich semantic and timbre information of a given speech.
 

### 2024-09-03 src/paper.tex
update

@@
 
-\title{Exploration in Target Speaker Extraction using Discrete Representations and Language Models
+\title{Target Speaker Extraction using Discrete Representations from Self-Supervised Models and Language Models
 \thanks{Identify applicable funding agency here. If none, delete this.}
@@
 In real life, speech signals are usually companied with background noise or other speakers' speeches. 
-These corrupted signals may not be optimal for tasks like speaker verification \cite{rao2019targetspeakerextractionoverlapped,9414017}, and speech recognition \cite{molkov2017SpeakerAwareNN, 8462661}, emphasizing the importance of this task.
+These corrupted signals may not be optimal for tasks like speaker verification \cite{rao2019targetspeakerextractionoverlapped,9414017}, and speech recognition \cite{molkov2017SpeakerAwareNN, 8462661}, emphasizing the importance of having good and robust
+speech separation models.
 
@@
 
-Recently, self-supervised Learning (SSL) models like HuBERT \cite{hubert} and WavLM \cite{wavlm} have demonstrated
+Discretization of audio has been studied due to the advancement of language models (LM). 
+This approach translates the audio into discrete tokens simulating text vocabularies and uses LMs to 
+model them. This approach simplifies audio generation tasks by transforming the complex 
+regression problems into classification problems \cite{dasb}. There are currently two approaches for
+audio discretization, the first one uses neural audio codecs \cite{dac}. This approach 
+typically captures the acoustic features of the audio \cite{speech_tokenizer}. The second approach 
+utilizes  self-supervised Learning (SSL) models like HuBERT \cite{hubert} and WavLM \cite{wavlm}.
+SSL models have demonstrated 
 excellent performances on many downstream tasks \cite{superb}. These SSL models extract  
 continuous representations containing rich semantic and timbre information of a given speech. 
+In this paper, we mainly explore how far we can go
 

### 2024-09-03 src/paper.tex
update

@@
 excellent performances on many downstream tasks \cite{superb}. These SSL models extract  
-continuous representations containing rich semantic and timbre information of a given speech. 
-In this paper, we mainly explore how far we can go
+continuous representations containing rich semantic and timbre information from a given speech. 
+As demonstrated in \cite{dasb}, SSL models perform better than audio codec in tasks like speech 
+enhancement and speech separation. Therefore, in this 
+paper, we mainly explore the discretization of SSL models.
+
+Discretization methods have been studied for speech enhancement \cite{selm} and blind speech separation \cite{dasb}, however, this approach has been rarely for target speaker extraction.
+TokenSplit \cite{tokensplit} needs the transcript of the speech to achieve satisfying results.
+In
+real life, however, speech is rarely provided with its transcript.
 

### 2024-09-03 src/paper.tex
update

@@
 
-Discretization methods have been studied for speech enhancement \cite{selm} and blind speech separation \cite{dasb}, however, this approach has been rarely for target speaker extraction.
-TokenSplit \cite{tokensplit} needs the transcript of the speech to achieve satisfying results.
-In
+Discretization methods have been studied for speech 
+enhancement \cite{selm} and blind speech separation \cite{dasb}, however, this approach has 
+been rarely studied for target speaker extraction. TokenSplit \cite{tokensplit} utilizes 
+Large Language Model to do blind speech separation instead of target speaker extraction. 
+Also, it  needs the 
+transcript of the speech to achieve satisfying results. In 
 real life, however, speech is rarely provided with its transcript.

### 2024-09-03 src/paper.tex
update

--- 2024-09-03 src/paper.tex
@@
 
-Discretization methods have been studied for speech enhancement \cite{selm} and blind speech separation \cite{dasb}, however, this approach has been rarely for target speaker extraction.
-TokenSplit \cite{tokensplit} needs the transcript of the speech to achieve satisfying results.
-In
-real life, however, speech is rarely provided with its transcript.
+Discretization methods have been studied for speech 
+enhancement \cite{selm} and blind speech separation \cite{dasb,tokensplit}, 
+however, this approach has 
+been rarely studied for target speaker extraction. Our work focuses on utilizing discrete tokens 
+to do target speaker extraction.
 

### 2024-09-03 src/paper.tex
update

@@
 
-\title{Target Speaker Extraction using Discrete Representations from Self-Supervised Models and Language Models
+\title{Target Speaker Extraction using Discrete Representations from 
+Self-Supervised Models and Language Models
 \thanks{Identify applicable funding agency here. If none, delete this.}
@@
 however, this approach has 
-been rarely studied for target speaker extraction. Our work focuses on utilizing discrete tokens 
-to do target speaker extraction.
+been rarely studied for target speaker extraction. In this paper, we present a novel way to do 
+target speaker extraction using discrete tokens and LMs. Inspired by the blind speech separation 
+networks proposed in DASB \cite{dasb}, our model has three stages: encoding, modeling and decoding.
+For the encoding stage.
 

### 2024-09-03 src/paper.tex
u
update

@@
 \usepackage{xcolor}
+
 \def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
@@
 networks proposed in DASB \cite{dasb}, our model has three stages: encoding, modeling and decoding.
-For the encoding stage.
+For the encoding stage, reference speech and mixed speech are tokenized using WavLM and 
+Kmeans as tokenizer. Unlike SELM \cite{selm}, which uses the 6th layer of wavlm as input, 
+we follow the recipes in \cite{dasb} and uses the output from hidden 
+layers 1, 3, 7, 12, 18, 23. Our results indicate that using 6 layers as input is better 
+than using only the 6th layer. 
+For the decoding stage, we used the pretrained unit hifi-gan 
+in \cite{unit_hifi} to reconstruct the 
+discrete tokens back to audio. 
+\cite{dasb}. 
+\begin{figure*}
+\centering
+\includegraphics[width=\textwidth]{assets/model.pdf}
+\caption{model}
+\label{model}
+\end{figure*}
 

### 2024-09-03 src/paper.tex
update

--- 2024-09-03 src/paper.tex
@@
 networks proposed in DASB \cite{dasb}, our model has three stages: encoding, modeling and decoding.
-For the encoding stage.
+For the encoding stage, reference speech and mixed speech are tokenized using WavLM and 
+Kmeans as tokenizer. Unlike SELM \cite{selm}, which uses the 6th layer of wavlm as input to the Kmeans layer, 
+we follow the recipes in \cite{dasb} and uses the output from hidden 
+layers 1, 3, 7, 12, 18, 23 of WavLM as input to the Kmeans layer. 6 Kmeans models
+are trained and applied on each layer output respectively. 
+Our results indicate that using multiple layers as 
+input is better 
+than using only the 6th layer.
+
+For the decoding stage, we used the pretrained unit HiFi-GAN 
+in \cite{unit_hifi} to reconstruct the 
+discrete tokens back to audio. Unlike SELM \cite{selm}, where a conformer 
+detokenizer is trained 
+to reconstruct the WavLM embeddings using Kmeans center embeddings before HiFi-GAN, \cite{unit_hifi} has proposed a scalable HiFi-GAN using dropout mechanism to directly 
+reconstruct audio from multiple layers of tokens without a conformer detokenizer. It 
+has also eliminated the trouble of training a HiFi-GAN for each layer. The encoder and 
+decoder is freezed during the training.
+
+\begin{figure*}[t]
+\centering
+\includegraphics[width=\textwidth]{assets/model.pdf}
+\caption{model}
+\label{model}
+\end{figure*}
 

### 2024-09-03 src/paper.tex
update

@@
 input is better 
-than using only the 6th layer.
+than using only the 6th layer. The reference speech is fed to the encoder directly. 
+However, for the mixed speech, instead of directly passing it to the WavLM model, we first concatenated the reference speech on both sides 
+of it before passing. After tokenization, we use only the tokens 
+corresponding to the mixed speech. For the modeling stage, we utilized an attention 
+embedding mechanism to add each embeddings of all layers together. We used a Cross 
+Attention mechanism similar in \cite{sef_net} to inject the speaker information. 
+An encoder-only LM is applied to
 

### 2024-09-04 src/paper.tex
update

@@
 For the encoding stage, reference speech and mixed speech are tokenized using WavLM and 
-Kmeans as tokenizer. Unlike SELM \cite{selm}, which uses the 6th layer of wavlm as input to the Kmeans layer, 
+Kmeans as tokenizer. Unlike SELM \cite{selm}, which uses the 6th layer of WavLM as input to the Kmeans layer, 
 we follow the recipes in \cite{dasb} and uses the output from hidden 
@@
 Attention mechanism similar in \cite{sef_net} to inject the speaker information. 
-An encoder-only LM is applied to
-
+An encoder-only LM, following by a linear classifier, is applied after the cross attention module
+to output the reconstructed tokens. 
 For the decoding stage, we used the pretrained unit HiFi-GAN 
@@
 has also eliminated the trouble of training a HiFi-GAN for each layer. The encoder and 
-decoder is freezed during the training.
+decoder is freezed during the training. The model overview is in Fig.\ref{model}. 
+Through extensive studies, we have demonstrated this method has achieved comparable results in terms 
+of speech quality and intelligibility. To the best of our knowledge, we are the first to explore 
+using discrete tokens to conduct target speaker extraction.
 

### 2024-09-04 src/paper.tex
update

@@
 \usepackage{xcolor}
+\usepackage{bm}
 
@@
 been rarely studied for target speaker extraction. In this paper, we present a novel way to do 
-target speaker extraction using discrete tokens and LMs. Inspired by the blind speech separation 
+target speaker extraction using discrete tokens and LMs (TSELM). Inspired by the blind speech separation 
 networks proposed in DASB \cite{dasb}, our model has three stages: encoding, modeling and decoding.
@@
 \includegraphics[width=\textwidth]{assets/model.pdf}
-\caption{model}
+\caption{Overview of TSELM.}
 \label{model}
 \end{figure*}
+
+\section{Method}
+
+\subsection{Encoding}
+We use pretrained SSL model WavLM Large \cite{wavlm} to 
+encode the speech into continuous representations. We use the output from 6 hidden 
+layers 1, 3, 7, 12, 18, 23. Given a speech signal \(s \in R^{T'} \), the output 
+of WavLM will be a tensor \(\bm{r}\) of shape \(n_l \times T \times E\) where 
+\(n_l\) specifies the number 
+of output layers (6 in this case), and  \(T\) is the time 
+dimension and \(E\) stands for the 
+embedding dimension, specifically 1024 in WavLM Large. The Kmeans tokenizer uses \(n_l\) numbers of  Kmeans model 
+separately on each output layer. Each model uses the same clustering number denoted by \(K\).
+After tokenization, the continuous embedding \(\bm{r}\) will be transformed to a tensor \(\bm{d}\) of shape \(6 \times T\) where each value is \(\in K\)
 

### 2024-09-04 src/paper.tex
update

--- 2024-09-04 src/paper.tex
@@
 \includegraphics[width=\textwidth]{assets/model.pdf}
-\caption{model}
+\caption{Overview of TSELM.}
 \label{model}
 \end{figure*}
+
+\section{Method}
+
+\subsection{Encoding}
+We use pretrained SSL model WavLM Large \cite{wavlm} to 
+encode the speech into continuous representations. We use the output from 6 hidden 
+layers 1, 3, 7, 12, 18, 23. Given a speech signal \(s \in R^{T'} \), the output 
+of WavLM will be a tensor \(\bm{r}\) of shape \(n \times T \times E\) where 
+\(n\) specifies the number 
+of output layers (6 in this case), and  \(T\) is the time 
+dimension and \(E\) stands for the 
+embedding dimension, specifically 1024 in WavLM Large. The Kmeans tokenizer uses \(n\) numbers of  Kmeans model 
+separately on each output layer. Each model uses the same clustering number denoted by \(K\).
+After tokenization, the continuous embedding \(\bm{r}\) will be transformed to a tensor \(\bm{d}\) of shape \(n \times T\) where each value \(\bm{d}_{(n_i,t)} \in (0, K-1), n_i \in (0,n), t \in 
+(0, T)\). We choose \(K\) to be 1000 in our experiments.
+
+The encoding strategy on the mixed speech plays a pivotal role in the model performance. 
+We follow the 
+aforementioned procedure for reference speech to get tensor \(\bm{d_r}\) of shape . But for the mixed speech.
 

### 2024-09-04 src/paper.tex
update

@@
 After tokenization, the continuous embedding \(\bm{r}\) will be transformed to a tensor \(\bm{d}\) of shape \(n \times T\) where each value \(\bm{d}_{(n_i,t)} \in (0, K-1), n_i \in (0,n), t \in 
-(0, T)\). We choose \(K\) to be 1000 in our experiments.
+(0, T)\). We choose \(K\) to be 1000 in our experiments. For reference speech and mixed speech, we 
+use the same Kmeans model and the same layer output of WavLM.
 
@@
 We follow the 
-aforementioned procedure for reference speech to get tensor \(\bm{d_r}\) of shape . But for the mixed speech.
+aforementioned procedure for 
+reference speech to get tensor \(\bm{d_r}\) of shape \(n \times T_r\). But for the mixed 
+speech, instead of directly following the procedure, we first concatenate it with 
+the reference speech to get \(s' = [s_r, s_m, s_r] \in R^{()}\)
 

### 2024-09-04 src/paper.tex
update

@@
 
-The encoding strategy on the mixed speech plays a pivotal role in the model performance. 
+The encoding strategy on the mixed speech plays a pivotal role in the model performance. Assume we 
+have a reference speech \(s_r \in R^{T^r} \) and mixed speech \(s \in R^{T'}\). 
 We follow the 
@@
 speech, instead of directly following the procedure, we first concatenate it with 
-the reference speech to get \(s' = [s_r, s_m, s_r] \in R^{()}\)
+the reference speech to get \(s' = [s_r, s_m, s_r] \in R^{(T^r+T'+T^r)}\). Then we use this speech 
+as input for the encoder, obtaining output \(d'\) of shape \(n \times \)
 

### 2024-09-04 src/paper.tex
update

@@
 the reference speech to get \(s' = [s_r, s_m, s_r] \in R^{(T^r+T'+T^r)}\). Then we use this speech 
-as input for the encoder, obtaining output \(d'\) of shape \(n \times \)
+as input for the encoder, obtaining output \(\bm{d'}\) of shape \(n \times (T_r+T+T_r)\) where \(T\) 
+denotes the length of output by directly passing the mixed speech without concatenation.
 

### 2024-09-04 src/paper.tex
update

@@
 (0, T)\). We choose \(K\) to be 1000 in our experiments. For reference speech and mixed speech, we 
-use the same Kmeans model and the same layer output of WavLM.
+use the same Kmeans model and the same layer output of WavLM. The encoder is freezed during training.
 
@@
 as input for the encoder, obtaining output \(\bm{d'}\) of shape \(n \times (T_r+T+T_r)\) where \(T\) 
-denotes the length of output by directly passing the mixed speech without concatenation.
+denotes the length of output by directly passing the mixed speech without concatenation. \(\bm{d'}\) 
+contains the discrete tokens for two pieces of the same reference speech and one piece of the mixed 
+speech, we select tensor \(\bm{d}\) belonging only to the mixed speech of shape \(n\times T\) as the 
+encoder output. This process is inspired by the training schema of WavLM \cite{wavlm}. To ensure the 
+model correctly outputs rich information of the target speaker, it is trained by 
+having a clean speech overlapped with another interference less than 50\% of the length of the clean 
+speech and using the first utterance as the main speaker. By this way, the model identifiers the 
+main speaker and produces embedding focusing on the main speaker. Our later experiments showed that 
+this strategy plays an important role in the model performance.
+
+\subsection{Modeling}
 

### 2024-09-04 src/paper.tex
update

@@
 \subsection{Modeling}
+\begin{figure}
+\centering
+\includegraphics[width=0.35\textwidth]{assets/cross_attention.pdf}
+\caption{Overview of TSELM.}
+\label{cross_attention}
+\end{figure}
+\subsubsection{Attention Embedding}
+After obtaining the discrete tensor \(\bm{d}\) with shape \(n\times T\), we use 6
+learnable embedding tables each with \(K\) entires to embed the 6 layers 
+respectively, each resulting in a tensor of shape \(T \times E\). 
+After embedding, we follow the same recipe as in \cite{dasb} to 
+aggregate the tensor by using attention mechanism to sum all the 6 tensors.
 

### 2024-09-04 src/paper.tex
update

@@
 After embedding, we follow the same recipe as in \cite{dasb} to 
-aggregate the tensor by using attention mechanism to sum all the 6 tensors.
+aggregate the tensor by using attention mechanism to sum all the 6 tensors. This summation 
+keeps the information of each layer while reducing the system complexity by reducing the 
+dimension of layers.
+
+\subsubsection{Cross Attention}
+The key factor in target speaker extraction is to inject the information of target speaker 
+into the mixture. SEF-Net \cite{sef_net} has proposed an embedding free way to inject the 
+target speaker information into the mixture by using cross attention module. This approach 
+has
 

### 2024-09-04 src/paper.tex
update

@@
 The key factor in target speaker extraction is to inject the information of target speaker 
-into the mixture. SEF-Net \cite{sef_net} has proposed an embedding free way to inject the 
-target speaker information into the mixture by using cross attention module. This approach 
-has
+into the mixture. Spex+ \cite{spex_plus} jointly trains a speaker verification task module 
+besides the separator, which might not be optimal for the separator task \cite{sef_net}. SEF-Net \cite{sef_net} has proposed an speaker embedding free way to inject the 
+target speaker information into the mixture by using cross attention module.
 

### 2024-09-04 src/paper.tex
update

--- 2024-09-04 src/paper.tex
@@
 After embedding, we follow the same recipe as in \cite{dasb} to 
-aggregate the tensor by using attention mechanism to sum all the 6 tensors.
+aggregate the tensor by using attention mechanism to sum all the 6 tensors. This summation 
+keeps the information of each layer while reducing the system complexity by reducing the 
+dimension of layers.
+
+\subsubsection{Cross Attention}
+One of the key factors in target speaker extraction is to 
+inject the information of target speaker 
+into the mixture. Spex+ \cite{spex_plus} jointly trains a speaker verification task module 
+besides the separator, which might not be optimal for the separator task \cite{sef_net}. SEF-Net \cite{sef_net} has proposed an speaker embedding free way to inject the 
+target speaker information into the mixture by using cross attention module, and it has 
+achieved superior performance compared to other methods. Therefore, we apply 
+the cross attention module to inject the reference embedding into the mixture.
 

### 2024-09-04 src/paper.tex
update

@@
 \includegraphics[width=0.35\textwidth]{assets/cross_attention.pdf}
-\caption{Overview of TSELM.}
+\caption{Details of Cross Attention mechanism.}
 \label{cross_attention}
@@
 keeps the information of each layer while reducing the system complexity by reducing the 
-dimension of layers.
+dimension of layers. After attention embedding, we obtain reference embedding \(E_r\) and 
+mixture embedding \(E_m\).
 
@@
 achieved superior performance compared to other methods. Therefore, we apply 
-the cross attention module to inject the reference embedding into the mixture.
+the cross attention module to inject the reference embedding into the mixture. The details 
+are in Fig.\ref{cross_attention}.
+The cross attention module consists of a Positional 
+Embedding layer, a cross-multiple head attention module, 
+and a FiLM module. 
+We use \(E_m\) as Query and \(E_r\) as Key and Value for 
+the attention module.
 

### 2024-09-04 src/paper.tex
update

--- 2024-09-04 src/paper.tex
@@
 achieved superior performance compared to other methods. Therefore, we apply 
-the cross attention module to inject the reference embedding into the mixture.
+the cross attention module to inject the reference embedding into the mixture. The details 
+are in Fig.\ref{cross_attention}.
+The cross attention module consists of a positional 
+embedding layer, a cross-multiple head attention module, 
+and a FiLM module. 
+We use \(E_m\) as query and \(E_r\) as key and value for 
+the attention module. The output of the cross-multiple head attention module \(E_{spk}\)
+is passed together with \(E_m\) to get the final output of the module.
 

### 2024-09-04 src/paper.tex
update

@@
 the attention module. The output of the cross-multiple head attention module \(E_{spk}\)
-is passed together with \(E_m\) to get the final output of the module.
+is passed together with \(E_m\) to the feature-wise linear modulation (FiLM) get the final output of the module. The output of 
+FiLM is denoted as
 

### 2024-09-04 src/paper.tex
update

@@
 \and
-\IEEEauthorblockN{2\textsuperscript{nd} Given Name Surname}
-\IEEEauthorblockA{\textit{dept. name of organization (of Aff.)} \\
-\textit{name of organization (of Aff.)}\\
-City, Country \\
-email address or ORCID}
+\IEEEauthorblockN{2\textsuperscript{nd} Zhan Jin}
+\IEEEauthorblockA{\textit{Duke Kunshan University} \\
+Kunshan, China \\
+zhan.jin@whu.edu.cn}
 \and
-\IEEEauthorblockN{3\textsuperscript{rd} Given Name Surname}
-\IEEEauthorblockA{\textit{dept. name of organization (of Aff.)} \\
-\textit{name of organization (of Aff.)}\\
-City, Country \\
-email address or ORCID}
-% \and
-% \IEEEauthorblockN{4\textsuperscript{th} Given Name Surname}
-% \IEEEauthorblockA{\textit{dept. name of organization (of Aff.)} \\
+\IEEEauthorblockN{3\textsuperscript{rd} Bang Zeng}
+\IEEEauthorblockA{\textit{Duke Kunshan University} \\
 % \textit{name of organization (of Aff.)}\\
-% City, Country \\
-% email address or ORCID}
-% \and
-% \IEEEauthorblockN{5\textsuperscript{th} Given Name Surname}
-% \IEEEauthorblockA{\textit{dept. name of organization (of Aff.)} \\
+Kunshan, China \\
+bangzeng@whu.edu.cn}
+\and
+\IEEEauthorblockN{4\textsuperscript{th} Ming Li}
+\IEEEauthorblockA{\textit{Duke Kunshan University} \\
 % \textit{name of organization (of Aff.)}\\
-% City, Country \\
-% email address or ORCID}
-% \and
-% \IEEEauthorblockN{6\textsuperscript{th} Given Name Surname}
-% \IEEEauthorblockA{\textit{dept. name of organization (of Aff.)} \\
-% \textit{name of organization (of Aff.)}\\
-% City, Country \\
-% email address or ORCID}
+Kunshan, China \\
+ming.li369@dukekunshan.edu.cn}
 }
@@
 is passed together with \(E_m\) to the feature-wise linear modulation (FiLM) get the final output of the module. The output of 
-FiLM is denoted as
+FiLM is denoted as \(E_f = FiLM(E_m, E_{spk}) = \gamma E_{spk} \cdot E_m  + \beta E_{spk} \) where 
+\(\gamma\) and \(\beta\) are learnable parameters denoting the scaling and shifting vectors 
+respectively. The output is then fed to the language model for later modeling.
 

### 2024-09-04 src/paper.tex
update

@@
 respectively. The output is then fed to the language model for later modeling.  
+\subsubsection{Language Modeling}
+We use encoder-only language models containing multiple self-attention modules to model the injected 
+embedding \(E_f\). Due to encoder-only style, the LM is able to learn from all the positions. 
+Finally, 6 linear classifiers each with dimension \(K\) is used to produce the probability 
+distribution of each layer respectively.
+Cross-entropy loss is applied between 
+the output tokens and the clean tokens through discretizing the 
+ground truth clean audio . 
+\subsection{Decoding}
 

### 2024-09-04 src/paper.tex
update

@@
 \section{Method}
+Our model consists of three stages: encoding, modeling, and decoding. The encoder and decoder are 
+pretrained models freezed during training. For the encoding stage, we use multiple layers of WavLM 
+and publicly available Kmeans 
+models in \cite{dasb} to produce the discretized tokens. We use a special concatenation 
+strategy to encode the mixture speech. For decoders, we use the scalable HiFi-GAN available in 
+\cite{dasb} to reconstruct the audio from discretized tokens. Our main focus is on the
+modeling stage. We apply an attention embedding mechanism to embed discrete tokens from different 
+layers into one single embedding. Encoder-only LM and linear classifier is applied afterwards to optimize the likelihood of probability 
+distribution of the clean tokens.
 
@@
 ground truth clean audio .
-\subsection{Decoding}
 

### 2024-09-04 src/paper.tex
update

@@
 Our model consists of three stages: encoding, modeling, and decoding. The encoder and decoder are 
-pretrained models freezed during training. For the encoding stage, we use multiple layers of WavLM 
+pretrained models and they are freezed during training. For the encoding stage, we use multiple layers of WavLM 
 and publicly available Kmeans 
@@
 ground truth clean audio .
+
+\section{Experiments}
+
+\subsection{Datasets and evaluation metrics}
+
+\subsubsection{Training sets}
+We use the pretrained WavLM Large \cite{wavlm} and it is freezed during training. The Kmeans tokenizer is trained on the
 

### 2024-09-05 src/paper.tex
update

@@
 \and
-\IEEEauthorblockN{2\textsuperscript{nd} Zhan Jin}
-\IEEEauthorblockA{\textit{Duke Kunshan University} \\
-Kunshan, China \\
-zhan.jin@whu.edu.cn}
-\and
-\IEEEauthorblockN{3\textsuperscript{rd} Bang Zeng}
+\IEEEauthorblockN{2\textsuperscript{nd} Bang Zeng}
 \IEEEauthorblockA{\textit{Duke Kunshan University} \\
@@
 bangzeng@whu.edu.cn}
+\and
+\IEEEauthorblockN{3\textsuperscript{rd} Zhan Jin}
+\IEEEauthorblockA{\textit{Duke Kunshan University} \\
+Kunshan, China \\
+zhan.jin@whu.edu.cn}
 \and
@@
 the output tokens and the clean tokens through discretizing the 
-ground truth clean audio .
+ground truth clean audio.
 
@@
 \subsubsection{Training sets}
-We use the pretrained WavLM Large \cite{wavlm} and it is freezed during training. The Kmeans tokenizer is trained on the
+We use the publicly available Kmeans tokenizer and scalable 
+HiFi-GAN decoder in \cite{speechbrain}. The Kmeans tokenizer
+is trained on \texttt{train\_clean\_100}, \texttt{train\_clean\_360}, and \texttt{train\_other\_500} of
+LibriSpeech \cite{librispeech}, and the scalable HiFi-GAN is trained on \texttt{train\_clean\_100} of 
+LibriTTS \cite{libritts}. The modeling stage is trained on 
+\texttt{train\_clean\_100} and \texttt{train\_clean\_360} of LibriSpeech. All training data are 
+generated on the fly with relative SNR between 0 dB to 5 dB.
 

### 2024-09-05 src/paper.tex
update

@@
 
-\subsubsection{Training sets}
+\subsubsection{Training}
 We use the publicly available Kmeans tokenizer and scalable 
@@
 \texttt{train\_clean\_100} and \texttt{train\_clean\_360} of LibriSpeech. All training data are 
-generated on the fly with relative SNR between 0 dB to 5 dB.
+generated on the fly with relative SNR between 0 dB to 5 dB. The mixture audio is segmented to 3 
+seconds and the reference speech is segmented to 4 seconds. 
+We use embedding dimension \(d=1024\) and
+
+% \subsubsection{Test sets}
+% We use the \texttt{dev} set of Libri2Mix \cite{librimix} to test our model performance and other baseline models.
+
+% \subsubsection{Evaluation Metrics}
+% As mentioned in studies
 

### 2024-09-05 src/paper.tex
update

@@
 bangzeng@whu.edu.cn}
+% \and
+% \IEEEauthorblockN{3\textsuperscript{rd} Zhan Jin}
+% \IEEEauthorblockA{\textit{Duke Kunshan University} \\
+% Kunshan, China \\
+% zhan.jin@whu.edu.cn}
 \and
-\IEEEauthorblockN{3\textsuperscript{rd} Zhan Jin}
-\IEEEauthorblockA{\textit{Duke Kunshan University} \\
-Kunshan, China \\
-zhan.jin@whu.edu.cn}
-\and
-\IEEEauthorblockN{4\textsuperscript{th} Ming Li}
+\IEEEauthorblockN{3\textsuperscript{re} Ming Li}
 \IEEEauthorblockA{\textit{Duke Kunshan University} \\
@@
 seconds and the reference speech is segmented to 4 seconds. 
-We use embedding dimension \(d=1024\) and
+We use embedding dimension 1024, sinusoidal positional embedding, and 4 transformer 
+encoders each with 16 heads and MLP with hidden dimension of 1024 in the cross attention module. 
+We use separate embedding tables for reference and mixed speech due to our observations that not 
+sharing embeddings does slightly better than sharing embeddings.
 

### 2024-09-05 src/paper.tex
update

@@
 seconds and the reference speech is segmented to 4 seconds.
+
+We use the output from hidden layers 1, 3, 7, 12, 18, 23 from WavLM Large for tokenization. 
 We use embedding dimension 1024, sinusoidal positional embedding, and 4 transformer 
-encoders each with 16 heads and MLP with hidden dimension of 1024 in the cross attention module. 
-We use separate embedding tables for reference and mixed speech due to our observations that not 
-sharing embeddings does slightly better than sharing embeddings.
+encoders each with 16 heads and MLP with hidden dimension of 1024 in the cross attention module. We 
+use layer norm after the cross attention module. 
+We use separate embedding tables in attention embedding module for reference and mixed speech due to our observations that not 
+sharing embeddings does slightly better than sharing embeddings. The small version of TSELM-S uses 
+embedding dimension \(d\) = 256, absolute sinusoidal positional embedding, and there are
 

### 2024-09-05 src/paper.tex
update

@@
 are in Fig.\ref{cross_attention}.
-The cross attention module consists of a positional 
-embedding layer, a cross-multiple head attention module, 
+The cross attention module consists of a stack of cross-multiple head attention modules, 
 and a FiLM module. 
@@
 We use the output from hidden layers 1, 3, 7, 12, 18, 23 from WavLM Large for tokenization. 
-We use embedding dimension 1024, sinusoidal positional embedding, and 4 transformer 
+We use embedding dimension 1024,  4 transformer 
 encoders each with 16 heads and MLP with hidden dimension of 1024 in the cross attention module. We 

### 2024-09-05 src/paper.tex
update

@@
 We use separate embedding tables in attention embedding module for reference and mixed speech due to our observations that not 
-sharing embeddings does slightly better than sharing embeddings. The small version of TSELM-S uses 
-embedding dimension \(d\) = 256, absolute sinusoidal positional embedding, and there are
+sharing embeddings does slightly better than sharing embeddings. The LM of small version TSELM-S uses 
+embedding dimension \(d\) = 256, absolute sinusoidal positional embedding, conformer encoders as backbone of LM. The conformer encoder is composed of 
+6 layers with kernel size 31 each with 4 heads and an MLP with hidden dimension 2048. The medium version TSELM-M uses \(d\) = 512 with 8 layers and 8 heads and the large version TSELM-L uses 
+\(d\) = 768 with 12 layers and 16 heads.
 

### 2024-09-05 src/paper.tex
update

@@
 
-\subsection{Datasets and evaluation metrics}
+\subsection{Training}
 
-\subsubsection{Training}
 We use the publicly available Kmeans tokenizer and scalable 
@@
 
-We use the output from hidden layers 1, 3, 7, 12, 18, 23 from WavLM Large for tokenization. 
+We use the output from hidden layers 1, 3, 7, 12, 18, 23 from WavLM Large and Kmeans model with 
+\(K=1000\).
 We use embedding dimension 1024,  4 transformer 
@@
 \(d\) = 768 with 12 layers and 16 heads.
+
+\subsection{Evaluation}
+We use the \texttt{dev} set of Libri2Mix \cite{librimix} to test our model performance and other baseline models.
 

### 2024-09-05 src/paper.tex
update

@@
 
+It is shown that metrics like PESQ, SI-SNR, STOI do not reflect speech quality of output of 
+vocoders due to the fact that the vocoder output does not focus strictly on frame alignment
+\cite{tokensplit,selm}. To measure the speech quality, 
+speech intelligibility, and speech similarity.  We have used
+
 % \subsubsection{Test sets}
@@
 
+\begin{center}
+\begin{tabular}{ c c c }
+    \hline
+    cell1 & cell2 & cell3 \\ 
+    \hline
+    cell4 & cell5 & cell6 \\  
+    cell7 & cell8 & cell9    
+\end{tabular}
+\end{center}
+
 \begin{table}[htbp]

### 2024-09-05 src/paper.tex
update

@@
 6 layers with kernel size 31 each with 4 heads and an MLP with hidden dimension 2048. The medium version TSELM-M uses \(d\) = 512 with 8 layers and 8 heads and the large version TSELM-L uses 
-\(d\) = 768 with 12 layers and 16 heads.
+\(d\) = 768 with 12 layers and 16 heads. We use AdamW as 
+our optimizer for all the experiments. The learning rate 
+is \(5 \times 10^{-4}\) for TSELM-S and \(5 \times 10^{-5}\) for TSELM-M and TSELM-L.
 
 \subsection{Evaluation}
-We use the \texttt{dev} set of Libri2Mix \cite{librimix} to test our model performance and other baseline models.
+We use the \texttt{dev} set of Libri2Mix \cite{librimix} to test our model performance and compare it with 
+other baseline models.
 

### 2024-09-05 src/paper.tex
update

@@
 our optimizer for all the experiments. The learning rate 
-is \(5 \times 10^{-4}\) for TSELM-S and \(5 \times 10^{-5}\) for TSELM-M and TSELM-L.
+is \(5 \times 10^{-4}\) for TSELM-S and \(5 \times 10^{-5}\) for TSELM-M and TSELM-L. We use 8 16Gb ram GPUs. Our batch size is set to 128. We train the model for 40k steps.
 
@@
 vocoders due to the fact that the vocoder output does not focus strictly on frame alignment
-\cite{tokensplit,selm}. To measure the speech quality, 
-speech intelligibility, and speech similarity.  We have used
+\cite{tokensplit,selm}. We used DNSMOS \cite{dnsmos} to measure the speech quality, and differential 
+word error 
+rate (dWER) \cite{dwer} to measure the speech intelligibility. For speaker similarity, we use the 
+public WeSpeaker \cite{wespeaker}.
 

### 2024-09-05 src/paper.tex
update

@@
 \usepackage{bm}
+\usepackage{multirow}
+\usepackage{tabularx, colortbl, makecell}
 
@@
 
+\begin{table}
+    % \setlength{\tabcolsep}{12pt} % Adjust column spacing
+    % \renewcommand{\arraystretch}{1.3}
+    \begin{center}
+        \begin{tabular}{llllll}
+            System                & type & size & DNSMOS & dWER   & Sim  \\
+            Mixture               & -          & -          & 2.68   & 79.3\% & -        \\
+            Target & -          & -          & 3.32   & 11.3\% & 0.653    \\
+                                  &            &            &        &        &          \\
+            Spex+                 & Continuous & 11M        & 2.98   & 19.3\% & 0.923    \\
+            Continuous     & Continuous & 220M       & 3.27   & 14.7\% & 0.877    \\
+            TSELM       & Hybrid     & 468M       & 3.22   & 19.8\% & 0.924\_d \\
+                                  &            &            &        &        &          \\
+            TSELM-S               & Discrete   & 354M       & 3.24   & 28.1\% & 0.892\_d \\
+            TSELM-M               & Discrete   & 389M       & 3.22   & 28.4\% & 0.901\_d \\
+            TSELM-L               & Discrete   & 468M       & 3.22   & 27.1\% & 0.905\_d
+            \end{tabular}
+      \end{center}
+      \caption{This table }
+  \end{table}
+
+\subsection{Baseline models}
+
+TSELM is compared with
+
 % \subsubsection{Test sets}
@@
 
-\begin{center}
-\begin{tabular}{ c c c }
-    \hline
-    cell1 & cell2 & cell3 \\ 
-    \hline
-    cell4 & cell5 & cell6 \\  
-    cell7 & cell8 & cell9    
-\end{tabular}
-\end{center}
+% % \begin{center}
+% \begin{table*}{ c c c c c c c c }
+%     \hline
+%     System & Type & Model size & DNSMOS & dWER & Spk Sim 
+% \end{table*}
+% % \end{center}
+
+% \begin{table*}[t]
+%     \centering
+%     \begin{tabular}{lcr}
+%         \hline
+%       \multirow{2}{System} & 2 & 3 \\
+%       4 & 5 & 6 \\
+%       7 & 8 & 9
+%     \end{tabular}
+%     \caption{Blabla}
+%     \label{tab:1}
+%   \end{table*}
 

### 2024-09-05 src/paper.tex
update

--- 2024-09-05 src/paper.tex
@@
 
+\begin{table*}
+    \setlength{\tabcolsep}{12pt} % Adjust column spacing
+    \renewcommand{\arraystretch}{1.3}
+    \begin{center}
+        \begin{tabular}{cccccccc}
+            \Xhline{2\arrayrulewidth} % Bold top line
+            \multirow{2}{*}{System} & \multirow{2}{*}{Model type} & \multirow{2}{*}{Model size} & \multicolumn{3}{c}{DNSMOS} & \multirow{2}{*}{dWER} & \multirow{2}{*}{Spk Sim} \\
+                                    &                             &                             & SIG     & BAK     & OVL    &                       &                          \\
+            \hline
+            Mixture                 & -                           & -                           & 3.39    & 3.14    & 2.68   & 79.3\%                & -                        \\
+            Target-discrete-wavlm   & -                           & -                           & 3.57    & 4.10    & 3.32   & 11.3\%                & 0.653                    \\
+            \hline
+            Spex+                   & Continuous                  & 11M                         & 3.36    & 3.76    & 2.98   & 19.3\%                & 0.923                    \\
+            Continuous-wavlm        & Continuous                  & 220M                        & 3.56    & 4.06    & 3.27   & 14.7\%                & 0.877                    \\
+            TSELM-L-Hybrid          & Hybrid                      & 468M                        & 3.50    & 4.06    & 3.22   & 19.8\%                & 0.924\_d                 \\
+            \hline
+            TSELM-S                 & Discrete                    & 354M                        & 3.50    & 4.07    & 3.24   & 28.1\%                & 0.892\_d                 \\
+            TSELM-M                 & Discrete                    & 389M                        & 3.49    & 4.05    & 3.22   & 28.4\%                & 0.901\_d                 \\
+            TSELM-L                 & Discrete                    & 468M                        & 3.49    & 4.05    & 3.22   & 27.1\%                & 0.905\_d \\
+            \Xhline{2\arrayrulewidth} % Bold top line              
+            \end{tabular}
+      \end{center}
+      \caption{This table }
+  \end{table*}
+
+\subsection{Baseline models}
+
+TSELM is compared with
+
 % \subsubsection{Test sets}

### 2024-09-05 src/paper.tex
update

@@
             Spex+                   & Continuous                  & 11M                         & 3.36    & 3.76    & 2.98   & 19.3\%                & 0.923                    \\
+            \hline
             Continuous-wavlm        & Continuous                  & 220M                        & 3.56    & 4.06    & 3.27   & 14.7\%                & 0.877                    \\

### 2024-09-05 src/paper.tex
update

@@
 \end{IEEEkeywords}
+\begin{figure*}[t]
+    \centering
+    \includegraphics[width=\textwidth]{assets/model.pdf}
+    \caption{Overview of TSELM.}
+    \label{model}
+    \end{figure*}
+
+    \begin{figure}
+        \centering
+        \includegraphics[width=0.35\textwidth]{assets/cross_attention.pdf}
+        \caption{Details of Cross Attention mechanism.}
+        \label{cross_attention}
+        \end{figure}
 
@@
 
-\begin{figure*}[t]
-\centering
-\includegraphics[width=\textwidth]{assets/model.pdf}
-\caption{Overview of TSELM.}
-\label{model}
-\end{figure*}
-
 \section{Method}
@@
 \subsection{Encoding}
+
+\begin{table*}
+    \setlength{\tabcolsep}{12pt} % Adjust column spacing
+    \renewcommand{\arraystretch}{1.3}
+    \begin{center}
+        \begin{tabular}{cccccccc}
+            \Xhline{2\arrayrulewidth} % Bold top line
+            \multirow{2}{*}{System} & \multirow{2}{*}{Model type} & \multirow{2}{*}{Model size} & \multicolumn{3}{c}{DNSMOS} & \multirow{2}{*}{dWER} & \multirow{2}{*}{Spk Sim} \\
+                                    &                             &                             & SIG     & BAK     & OVL    &                       &                          \\
+            \hline
+            Mixture                 & -                           & -                           & 3.39    & 3.14    & 2.68   & 79.3\%                & -                        \\
+            Target-discrete-wavlm   & -                           & 330M                           & 3.57    & 4.10    & 3.32   & 11.3\%                & 0.653                    \\
+            \hline
+            Spex+                   & Continuous                  & 11M                         & 3.36    & 3.76    & 2.98   & 19.3\%                & 0.923                    \\
+            \hline
+            Continuous-wavlm        & Continuous                  & 220M                        & 3.56    & 4.06    & 3.27   & 14.7\%                & 0.877                    \\
+            TSELM-L-Hybrid          & Hybrid                      & 468M                        & 3.50    & 4.06    & 3.22   & 19.8\%                & 0.924\_d                 \\
+            \hline
+            TSELM-S                 & Discrete                    & 354M                        & 3.50    & 4.07    & 3.24   & 28.1\%                & 0.892\_d                 \\
+            TSELM-M                 & Discrete                    & 389M                        & 3.49    & 4.05    & 3.22   & 28.4\%                & 0.901\_d                 \\
+            TSELM-L                 & Discrete                    & 468M                        & 3.49    & 4.05    & 3.22   & 27.1\%                & 0.905\_d \\
+            \Xhline{2\arrayrulewidth} % Bold top line              
+            \end{tabular}
+      \end{center}
+      \caption{This table }
+  \end{table*}
+
 We use pretrained SSL model WavLM Large \cite{wavlm} to 
@@
 \subsection{Modeling}
-\begin{figure}
-\centering
-\includegraphics[width=0.35\textwidth]{assets/cross_attention.pdf}
-\caption{Details of Cross Attention mechanism.}
-\label{cross_attention}
-\end{figure}
 \subsubsection{Attention Embedding}
@@
 
-\begin{table*}
-    \setlength{\tabcolsep}{12pt} % Adjust column spacing
-    \renewcommand{\arraystretch}{1.3}
-    \begin{center}
-        \begin{tabular}{cccccccc}
-            \Xhline{2\arrayrulewidth} % Bold top line
-            \multirow{2}{*}{System} & \multirow{2}{*}{Model type} & \multirow{2}{*}{Model size} & \multicolumn{3}{c}{DNSMOS} & \multirow{2}{*}{dWER} & \multirow{2}{*}{Spk Sim} \\
-                                    &                             &                             & SIG     & BAK     & OVL    &                       &                          \\
-            \hline
-            Mixture                 & -                           & -                           & 3.39    & 3.14    & 2.68   & 79.3\%                & -                        \\
-            Target-discrete-wavlm   & -                           & -                           & 3.57    & 4.10    & 3.32   & 11.3\%                & 0.653                    \\
-            \hline
-            Spex+                   & Continuous                  & 11M                         & 3.36    & 3.76    & 2.98   & 19.3\%                & 0.923                    \\
-            \hline
-            Continuous-wavlm        & Continuous                  & 220M                        & 3.56    & 4.06    & 3.27   & 14.7\%                & 0.877                    \\
-            TSELM-L-Hybrid          & Hybrid                      & 468M                        & 3.50    & 4.06    & 3.22   & 19.8\%                & 0.924\_d                 \\
-            \hline
-            TSELM-S                 & Discrete                    & 354M                        & 3.50    & 4.07    & 3.24   & 28.1\%                & 0.892\_d                 \\
-            TSELM-M                 & Discrete                    & 389M                        & 3.49    & 4.05    & 3.22   & 28.4\%                & 0.901\_d                 \\
-            TSELM-L                 & Discrete                    & 468M                        & 3.49    & 4.05    & 3.22   & 27.1\%                & 0.905\_d \\
-            \Xhline{2\arrayrulewidth} % Bold top line              
-            \end{tabular}
-      \end{center}
-      \caption{This table }
-  \end{table*}
-
 \subsection{Baseline models}
@@
 TSELM is compared with
-
-% \subsubsection{Test sets}
-% We use the \texttt{dev} set of Libri2Mix \cite{librimix} to test our model performance and other baseline models.
-
-% \subsubsection{Evaluation Metrics}
-% As mentioned in studies
-
-\subsection{Units}
-\begin{itemize}
-\item Use either SI (MKS) or CGS as primary units.
-(SI units are encouraged.) English units may be used as secondary units (in parentheses).
-An exception would be the use of English units as identifiers in trade, such as ``3.5-inch disk drive''.
-\item Avoid combining SI and CGS units, such as current in amperes and magnetic field in oersteds.
-This often leads to confusion because equations do not balance dimensionally.
-If you must use mixed units, clearly state the units for each quantity that you use in an equation.
-\item Do not mix complete spellings and abbreviations of units: ``Wb/m\textsuperscript{2}'' or ``webers per square meter'', not ``webers/m\textsuperscript{2}''.
-Spell out units when they appear in text: ``.
-.
-.
-a few henries'', not ``.
-.
-.
-a few H''.
-\item Use a zero before decimal points: ``0.25'', not ``.25''. Use ``cm\textsuperscript{3}'', not ``cc''.)
-\end{itemize}
-
-\subsection{Equations}
-Number equations consecutively. To make your 
-equations more compact, you may use the solidus (~/~), the exp function, or 
-appropriate exponents. Italicize Roman symbols for quantities and variables, 
-but not Greek symbols. Use a long dash rather than a hyphen for a minus 
-sign. Punctuate equations with commas or periods when they are part of a 
-sentence, as in:
-\begin{equation}
-a+b=\gamma\label{eq}
-\end{equation}
-
-Be sure that the 
-symbols in your equation have been defined before or immediately following 
-the equation. Use ``\eqref{eq}'', not ``Eq.~\eqref{eq}'' or ``equation \eqref{eq}'', except at 
-the beginning of a sentence: ``Equation \eqref{eq} is . . .''
-
-\subsection{\LaTeX-Specific Advice}
-
-Please use ``soft'' (e.g., \verb|\eqref{Eq}|) cross references instead
-of ``hard'' references (e.g., \verb|(1)|). That will make it possible
-to combine sections, add equations, or change the order of figures or
-citations without having to go through the file line by line.
-
-Please don't use the \verb|{eqnarray}| equation environment. Use
-\verb|{align}| or \verb|{IEEEeqnarray}| instead. The \verb|{eqnarray}|
-environment leaves unsightly spaces around relation symbols.
-
-Please note that the \verb|{subequations}| environment in {\LaTeX}
-will increment the main equation counter even when there are no
-equation numbers displayed. If you forget that, you might write an
-article in which the equation numbers skip from (17) to (20), causing
-the copy editors to wonder if you've discovered a new method of
-counting.
-
-{\BibTeX} does not work by magic. It doesn't get the bibliographic
-data from thin air but from .bib files. If you use {\BibTeX} to produce a
-bibliography you must send the .bib files.
-
-{\LaTeX} can't read your mind. If you assign the same label to a
-subsubsection and a table, you might find that Table I has been cross
-referenced as Table IV-B3.
-
-{\LaTeX} does not have precognitive abilities. If you put a
-\verb|\label| command before the command that updates the counter it's
-supposed to be using, the label will pick up the last counter to be
-cross referenced instead. In particular, a \verb|\label| command
-should not go before the caption of a figure or a table.
-
-Do not use \verb|\nonumber| inside the \verb|{array}| environment. It
-will not stop equation numbers inside \verb|{array}| (there won't be
-any anyway) and it might stop a wanted equation number in the
-surrounding equation.
-
-\subsection{Some Common Mistakes}\label{SCM}
-\begin{itemize}
-\item The word ``data'' is plural, not singular.
-\item The subscript for the permeability of vacuum $\mu_{0}$, and other common scientific constants, is zero with subscript formatting, not a lowercase letter ``o''.
-\item In American English, commas, semicolons, periods, question and exclamation marks are located within quotation marks only when a complete thought or name is cited, such as a title or full quotation.
-When quotation marks are used, instead of a bold or italic typeface, to highlight a word or phrase, punctuation should appear outside of the quotation marks.
-A parenthetical phrase or statement at the end of a sentence is punctuated outside of the closing parenthesis (like this).
-(A parenthetical sentence is punctuated within the parentheses.)
-\item A graph within a graph is an ``inset'', not an ``insert''. The word alternatively is preferred to the word ``alternately'' (unless you really mean something that alternates).
-\item Do not use the word ``essentially'' to mean ``approximately'' or ``effectively''.
-\item In your paper title, if the words ``that uses'' can accurately replace the word ``using'', capitalize the ``u''; if not, keep using lower-cased.
-\item Be aware of the different meanings of the homophones ``affect'' and ``effect'', ``complement'' and ``compliment'', ``discreet'' and ``discrete'', ``principal'' and ``principle''.
-\item Do not confuse ``imply'' and ``infer''.
-\item The prefix ``non'' is not a word; it should be joined to the word it modifies, usually without a hyphen.
-\item There is no period after the ``et'' in the Latin abbreviation ``et al.''.
-\item The abbreviation ``i.e.'' means ``that is'', and the abbreviation ``e.g.'' means ``for example''.
-\end{itemize}
-An excellent style manual for science writers is \cite{b7}.
-
-\subsection{Authors and Affiliations}\label{AAA}
-\textbf{The class file is designed for, but not limited to, six authors.} A 
-minimum of one author is required for all conference articles. Author names 
-should be listed starting from left to right and then moving down to the 
-next line. This is the author sequence that will be used in future citations 
-and by indexing services. Names should not be listed in columns nor group by 
-affiliation. Please keep your affiliations as succinct as possible (for 
-example, do not differentiate among departments of the same organization).
-
-\subsection{Identify the Headings}\label{ITH}
-Headings, or heads, are organizational devices that guide the reader through 
-your paper. There are two types: component heads and text heads.
-
-Component heads identify the different components of your paper and are not 
-topically subordinate to each other. Examples include Acknowledgments and 
-References and, for these, the correct style to use is ``Heading 5''. Use 
-``figure caption'' for your Figure captions, and ``table head'' for your 
-table title. Run-in heads, such as ``Abstract'', will require you to apply a 
-style (in this case, italic) in addition to the style provided by the drop 
-down menu to differentiate the head from the text.
-
-Text heads organize the topics on a relational, hierarchical basis. For 
-example, the paper title is the primary text head because all subsequent 
-material relates and elaborates on this one topic. If there are two or more 
-sub-topics, the next level head (uppercase Roman numerals) should be used 
-and, conversely, if there are not at least two sub-topics, then no subheads 
-should be introduced.
-
-\subsection{Figures and Tables}\label{FAT}
-\paragraph{Positioning Figures and Tables} Place figures and tables at the top and 
-bottom of columns. Avoid placing them in the middle of columns. Large 
-figures and tables may span across both columns. Figure captions should be 
-below the figures; table heads should appear above the tables. Insert 
-figures and tables after they are cited in the text. Use the abbreviation 
-``Fig.~\ref{fig}'', even at the beginning of a sentence.
-
-% % \begin{center}
-% \begin{table*}{ c c c c c c c c }
-%     \hline
-%     System & Type & Model size & DNSMOS & dWER & Spk Sim 
-% \end{table*}
-% % \end{center}
-
-% \begin{table*}[t]
-%     \centering
-%     \begin{tabular}{lcr}
-%         \hline
-%       \multirow{2}{System} & 2 & 3 \\
-%       4 & 5 & 6 \\
-%       7 & 8 & 9
-%     \end{tabular}
-%     \caption{Blabla}
-%     \label{tab:1}
-%   \end{table*}
-
-\begin{table}[htbp]
-\caption{Table Type Styles}
-\begin{center}
-\begin{tabular}{|c|c|c|c|}
-\hline
-\textbf{Table}&\multicolumn{3}{|c|}{\textbf{Table Column Head}} \\
-\cline{2-4} 
-\textbf{Head} & \textbf{\textit{Table column subhead}}& \textbf{\textit{Subhead}}& \textbf{\textit{Subhead}} \\
-\hline
-copy& More table copy$^{\mathrm{a}}$& &  \\
-\hline
-\multicolumn{4}{l}{$^{\mathrm{a}}$Sample of a Table footnote.}
-\end{tabular}
-\label{tab1}
-\end{center}
-\end{table}
-
-\begin{figure}[htbp]
-\centerline{\includegraphics{fig1.png}}
-\caption{Example of a figure caption.}
-\label{fig}
-\end{figure}
-
-Figure Labels: Use 8 point Times New Roman for Figure labels. Use words 
-rather than symbols or abbreviations when writing Figure axis labels to 
-avoid confusing the reader. As an example, write the quantity 
-``Magnetization'', or ``Magnetization, M'', not just ``M''. If including 
-units in the label, present them within parentheses. Do not label axes only 
-with units. In the example, write ``Magnetization (A/m)'' or ``Magnetization 
-\{A[m(1)]\}'', not just ``A/m''. Do not label axes with a ratio of 
-quantities and units. For example, write ``Temperature (K)'', not 
-``Temperature/K''.
 
@@
 
-\section*{References}
-
-Please number citations consecutively within brackets \cite{b1}. The 
-sentence punctuation follows the bracket \cite{b2}. Refer simply to the reference 
-number, as in \cite{b3}---do not use ``Ref. \cite{b3}'' or ``reference \cite{b3}'' except at 
-the beginning of a sentence: ``Reference \cite{b3} was the first $\ldots$''
-
-Number footnotes separately in superscripts. Place the actual footnote at 
-the bottom of the column in which it was cited. Do not put footnotes in the 
-abstract or reference list. Use letters for table footnotes.
-
-Unless there are six authors or more give all authors' names; do not use 
-``et al.''. Papers that \cite{b8} have not been published, even if they have been 
-submitted for publication, should be cited as ``unpublished'' \cite{b4}. Papers 
-that have been accepted for publication should be cited as ``in press'' \cite{b5}. 
-Capitalize only the \cite{b11}  first word \cite{b9} in a paper title, except for proper nouns and 
-element symbols.
-
-For papers published in translation journals, please give the English \cite{b10}
-citation first, followed by the original foreign-language citation \cite{b6}.
 \bibliographystyle{IEEEtran}
@@
 
-\vspace{12pt}
-\color{red}
-IEEE conference templates contain guidance text for composing and formatting conference papers.
-Please ensure that all template text is removed from your conference paper prior to submission to the conference.
-Failure to remove the template text from your paper may result in your paper not being published.
-
 \end{document}

### 2024-09-05 src/paper.tex
update

@@
 \usepackage{tabularx, colortbl, makecell}
+\usepackage{etoolbox}
+\makeatletter
+\patchcmd{\@makecaption}
+  {\scshape}
+  {}
+  {}
+  {}
+\makeatother
 
@@
             Mixture                 & -                           & -                           & 3.39    & 3.14    & 2.68   & 79.3\%                & -                        \\
-            Target-discrete-wavlm   & -                           & 330M                           & 3.57    & 4.10    & 3.32   & 11.3\%                & 0.653                    \\
+            Target-discrete-WavLM   & -                           & 330M                           & 3.57    & 4.10    & 3.32   & 11.3\%                & 0.653                    \\
             \hline
@@
             \hline
-            Continuous-wavlm        & Continuous                  & 220M                        & 3.56    & 4.06    & 3.27   & 14.7\%                & 0.877                    \\
+            Continuous-WavLM       & Continuous                  & 220M                        & 3.56    & 4.06    & 3.27   & 14.7\%                & 0.877                    \\
             TSELM-L-Hybrid          & Hybrid                      & 468M                        & 3.50    & 4.06    & 3.22   & 19.8\%                & 0.924\_d                 \\
@@
             \end{tabular}
+            \linebreak
+            \caption{Sample table showing different categories of items with their quantities.}
+            \label{main_exp}
+            This table 
       \end{center}
-      \caption{This table }
+
   \end{table*}
@@
 \subsection{Baseline models}
-
-TSELM is compared with
+All models are reflected in Table \ref{main_exp}. 
+TSELM is compared with Spex+, a discriminative separation model \cite{spex_plus} trained on Libri2Mix \cite{librimix}. Since the discretization might lose some 
+speaker information compared with continuous methods. We compare the speaker 
+similarity of TSELM with the target audio produced by discretizating the clean audio, which is denoted by Target-discrete-WavLM.
 

### 2024-09-05 src/paper.tex
update

@@
 speaker information compared with continuous methods. We compare the speaker 
-similarity of TSELM with the target audio produced by discretizating the clean audio, which is denoted by Target-discrete-WavLM.
+similarity of TSELM with the target audio produced by discretizing the clean audio, which is denoted by Target-discrete-WavLM.
 

### 2024-09-05 src/paper.tex
update

@@
 speaker information compared with continuous methods. We compare the speaker 
-similarity of TSELM with the target audio produced by discretizing the clean audio, which is denoted by Target-discrete-WavLM.
+similarity of TSELM with the target audio produced by discretizing the clean audio, which is denoted by Target-discrete-WavLM, and it is the upper bound of our model  
+performance. Besides TSELM, we did two experiments 
+denoted by Continuous-WavLM and TSELM-L-Hybrid. For Continuous-WavLM, we directly
+passed the embeddings of the 6th hidden layer output of WavLM to the cross attention  
+and LM, using Mean Square Error loss between the output embeddings and the clean 
+embeddings. We then reconstruct the audio back to the
 

### 2024-09-05 src/paper.tex
update

@@
 performance. Besides TSELM, we did two experiments 
-denoted by Continuous-WavLM and TSELM-L-Hybrid. For Continuous-WavLM, we directly
+denoted by Continuous-WavLM and TSELM-L-Hybrid using the same training data. 
+For Continuous-WavLM, we directly
 passed the embeddings of the 6th hidden layer output of WavLM to the cross attention  
-and LM, using Mean Square Error loss between the output embeddings and the clean 
-embeddings. We then reconstruct the audio back to the
+and LM. Concatenation strategy is stilled applied to the mixed speech. Mean Square Error loss is applied between the output embeddings and the clean 
+embeddings. We use the HiFi-GAN in \cite{knn_vc} to reconstruct the audio. For 
+TSELM-L-Hybrid, inspired by MaskSR \cite{mask_sr}, we did not discretize the
 

### 2024-09-05 src/paper.tex
update

@@
 \usepackage{etoolbox}
+
 \makeatletter
@@
             \Xhline{2\arrayrulewidth} % Bold top line
-            \multirow{2}{*}{System} & \multirow{2}{*}{Model type} & \multirow{2}{*}{Model size} & \multicolumn{3}{c}{DNSMOS} & \multirow{2}{*}{dWER} & \multirow{2}{*}{Spk Sim} \\
+            \multirow{2}{*}{System} & \multirow{2}{*}{Model type} & \multirow{2}{*}{Model size} & \multicolumn{3}{c}{ DNSMOS $\uparrow$} & \multirow{2}{*}{dWER $\downarrow$} & \multirow{2}{*}{Spk Sim $\uparrow$} \\
+            \cline{4-6}
                                     &                             &                             & SIG     & BAK     & OVL    &                       &                          \\ 
+                                    % \cline{2-2}
             \hline
@@
             \linebreak
-            \caption{Sample table showing different categories of items with their quantities.}
+            \caption{The performance of different systems on Libri2Mix testset. For 
+            speaker similarity(last column). }
             \label{main_exp}
@@
 embeddings. We use the HiFi-GAN in \cite{knn_vc} to reconstruct the audio. For 
-TSELM-L-Hybrid, inspired by MaskSR \cite{mask_sr}, we did not discretize the
+TSELM-L-Hybrid, inspired by MaskSR \cite{mask_sr}, we kept discretizing the reference 
+speech while utilizing the continuous embeddings from the reference speech. We call 
+it hybrid instead of fully discretized because the mixture speech has continuous 
+features instead of discrete features.
+
+\section{Results and Discussions}
 
@@
 
-The preferred spelling of the word ``acknowledgment'' in America is without 
-an ``e'' after the ``g''. Avoid the stilted expression ``one of us (R. B. 
-G.) thanks $\ldots$''. Instead, try ``R. B. G. thanks$\ldots$''. Put sponsor 
-acknowledgments in the unnumbered footnote on the first page.
+We want to thank for Kunshan Super Computing SCNet for providing the computing resources.
 

### 2024-09-06 src/paper.tex
update

@@
             \linebreak
-            \caption{The performance of different systems on Libri2Mix testset. For 
-            speaker similarity(last column). }
+            \caption{The performance of different systems on Libri2Mix testset. For TSELM-L-Hybrid  
+            and TSELM, we compare the speaker similarity with the discretized target speech 
+            (Target-discrete-WavLM) instead of the target speech due to the observation that 
+            the process of discretization already losses the speaker information (0.653 for 
+            Target-discrete-WavLM). We use "\_d" to denote it.  }
             \label{main_exp}
-            This table 
       \end{center}
-
   \end{table*}
@@
 \section{Results and Discussions}
+Table \ref{main_exp} shows the performance of different systems on the Libri2Mix test.
+The model size for Target-discrete-WavLM denotes the model size of the encoder and 
+decoder, which is WavLM Large and HiFi-GAN respectively. DNSMOS is calculated over the 
+test sets since it is reference-free. dWER is calculated with the clean speech instead 
+of the discretized speech due to our observations that this does not make much difference. 
+For TSELM-L-Hybrid and TSELM, we compute the speaker similarity with the discretized
+target speech (Target-discrete-WavLM).
+
+% instead of the target speech due to the observation that the process of discretization already losses the speaker
+% information (0.653 for Target-discrete-WavLM).
 

### 2024-09-06 src/paper.tex
update

@@
                                     &                             &                             & SIG     & BAK     & OVL    &                       &                          \\ 
-                                    % \cline{2-2}
             \hline
@@
 For TSELM-L-Hybrid and TSELM, we compute the speaker similarity with the discretized
-target speech (Target-discrete-WavLM).
+target speech (Target-discrete-WavLM) instead of the target speech.
+% due to the observation that the process of discretization already losses the speaker
+% information (0.653 for Target-discrete-WavLM). 
+We observe that the process of discretization already losses the speaker
+information (0.653 for Target-discrete-WavLM), and it might be related to the inevitable speaker 
+information loss by the process of discretization. Future work should focus on developing better 
+tokenization methods for SSL models. 
+Since work focuses on using the discretized information 
+to do target speaker extraction instead of developing better tokenization methods, we think it is 
+reasonable to compare our outputs with the discretized speech since it serves as an upper bond.
 
-% instead of the target speech due to the observation that the process of discretization already losses the speaker
-% information (0.653 for Target-discrete-WavLM).
+We observe that our model performs better than Spex+ in terms of the DNSMOS scores but worse in dWER.
 

### 2024-09-06 src/paper.tex
update

@@
 We observe that our model performs better than Spex+ in terms of the DNSMOS scores but worse in dWER. 
+This suggests that our model has better speech quality compared with discriminative models but 
+worse in speech intelligibility. One possible reason might be related 
+to the discretization process on the mixture 
+speech. Our Kmeans algorithm is trained on clean speech instead of mixed speech. 
+Discretization on the mixed
+speech might cause the output to focus on wrong speakers. Our results from TSELM-L-Hybrid proves this. For TSELM-L-Hybrid, we use the continuous 
+embeddings from mixture speech and it has
 

### 2024-09-06 src/paper.tex
update

@@
 Discretization on the mixed
-speech might cause the output to focus on wrong speakers. Our results from TSELM-L-Hybrid proves this. For TSELM-L-Hybrid, we use the continuous 
-embeddings from mixture speech and it has
+speech might cause the output to focus on wrong speakers. Our results from TSELM-L-Hybrid 
+support 
+this. For TSELM-L-Hybrid, we use the continuous embeddings from the mixture speech, and it has 
+achieved similar dWER with Spex+. Another reason might be related to LM. Right now our encoder-only 
+LM satisfies roughly 50\% accuracy. We think using auto-regressive or masking models will achieve 
+better results.
 

### 2024-09-06 src/paper.tex
update

@@
 speech. Our Kmeans algorithm is trained on clean speech instead of mixed speech. 
-Discretization on the mixed
-speech might cause the output to focus on wrong speakers. Our results from TSELM-L-Hybrid 
+ For speech enhancement, this might be 
+good because the level of noise will usually be smaller than the speech. Kmeans might achieve the 
+effect of denoising. Discretization on the mixed
+speech, however, might cause the output to focus on wrong speakers. 
+Our results from TSELM-L-Hybrid 
 support 
-this. For TSELM-L-Hybrid, we use the continuous embeddings from the mixture speech, and it has 
+this. For TSELM-L-Hybrid, we use the continuous embeddings from the mixture speech without discretizing, and it has 
 achieved similar dWER with Spex+. Another reason might be related to LM. Right now our encoder-only 

### 2024-09-06 src/paper.tex
update

@@
     \begin{center}
-        \begin{tabular}{cccccccc}
+        \begin{tabular}{ccccccccc}
             \Xhline{2\arrayrulewidth} % Bold top line
-            \multirow{2}{*}{System} & \multirow{2}{*}{Model type} & \multirow{2}{*}{Model size} & \multicolumn{3}{c}{ DNSMOS $\uparrow$} & \multirow{2}{*}{dWER $\downarrow$} & \multirow{2}{*}{Spk Sim $\uparrow$} \\
-            \cline{4-6}
-                                    &                             &                             & SIG     & BAK     & OVL    &                       &                          \\ 
+            \multirow{2}{*}{System} & \multirow{2}{*}{Category} & \multirow{2}{*}{Model type} & \multirow{2}{*}{Model size} & \multicolumn{3}{c}{ DNSMOS $\uparrow$} & \multirow{2}{*}{dWER $\downarrow$} & \multirow{2}{*}{Spk Sim $\uparrow$} \\
+            \cline{5-7}
+              &                   &                             &                             & SIG     & BAK     & OVL    &                       &                          \\ 
             \hline
-            Mixture                 & -                           & -                           & 3.39    & 3.14    & 2.68   & 79.3\%                & -                        \\
-            Target-discrete-WavLM   & -                           & 330M                           & 3.57    & 4.10    & 3.32   & 11.3\%                & 0.653                    \\
+            Mixture                 & - & -                           & -                           & 3.39    & 3.14    & 2.68   & 79.3\%                & -                        \\
+            Target-discrete-WavLM   & G & -                          & 330M                           & 3.57    & 4.10    & 3.32   & 11.3\%                & 0.653                    \\
             \hline
-            Spex+                   & Continuous                  & 11M                         & 3.36    & 3.76    & 2.98   & 19.3\%                & 0.923                    \\
+            Spex+                   &  D & Continuous                  & 11M                         & 3.36    & 3.76    & 2.98   & 19.3\%                & 0.923                    \\
             \hline
-            Continuous-WavLM       & Continuous                  & 220M                        & 3.56    & 4.06    & 3.27   & 14.7\%                & 0.877                    \\
-            TSELM-L-Hybrid          & Hybrid                      & 468M                        & 3.50    & 4.06    & 3.22   & 19.8\%                & 0.924\_d                 \\
+            Continuous-WavLM   & G    & Continuous                  & 220M                        & 3.56    & 4.06    & 3.27   & 14.7\%                & 0.877                    \\
+            TSELM-L-Hybrid    & G       & Hybrid                      & 468M                        & 3.50    & 4.06    & 3.22   & 19.8\%                & 0.924\_d                 \\
             \hline
-            TSELM-S                 & Discrete                    & 354M                        & 3.50    & 4.07    & 3.24   & 28.1\%                & 0.892\_d                 \\
-            TSELM-M                 & Discrete                    & 389M                        & 3.49    & 4.05    & 3.22   & 28.4\%                & 0.901\_d                 \\
-            TSELM-L                 & Discrete                    & 468M                        & 3.49    & 4.05    & 3.22   & 27.1\%                & 0.905\_d \\
+            TSELM-S           & G       & Discrete                    & 354M                        & 3.50    & 4.07    & 3.24   & 28.1\%                & 0.892\_d                 \\
+            TSELM-M          & G        & Discrete                    & 389M                        & 3.49    & 4.05    & 3.22   & 28.4\%                & 0.901\_d                 \\
+            TSELM-L         & G         & Discrete                    & 468M                        & 3.49    & 4.05    & 3.22   & 27.1\%                & 0.905\_d \\
             \Xhline{2\arrayrulewidth} % Bold top line              

### 2024-09-06 src/paper.tex
update

@@
             TSELM-L-Hybrid    & G       & Hybrid                      & 468M                        & 3.50    & 4.06    & 3.22   & 19.8\%                & 0.924\_d                 \\
+            TSELM-S-NoConcat           & G       & Discrete                    & 354M                        & 3.47    & 4.03    & 3.19   & 69.6\%                & 0.868\_d                 \\
             \hline
@@
 
+We observe significant dWER increasing without concatenating the reference audio to the mixture, 
+as shown 
+the TSELM-S-NoConcat in Table \ref{main_exp}. WavLM \cite{wavlm} is demonstrated to have target speaker 
+separation capability.
+The input audio should have the mixture less than 50\% and have the first utterance as target speaker.
+The output will be a coarse denoised audio emphasizing the target speaker.
+If the whole input is mixture, we have found that WavLM sometimes will 
+extract the wrong speaker. Our current pipeline focuses on the separation strategy
+
 \section*{Acknowledgment}

### 2024-09-06 src/paper.tex
update

@@
 The input audio should have the mixture less than 50\% and have the first utterance as target speaker.
-The output will be a coarse denoised audio emphasizing the target speaker.
+The output will be a coarse denoised embedding emphasizing the target speaker.
 If the whole input is mixture, we have found that WavLM sometimes will 
-extract the wrong speaker. Our current pipeline focuses on the separation strategy
+extract the wrong speaker. Inspired by SELM's \cite{selm} success in speech denoising. Our pipeline is trying to transform
+the target speaker separation problem to speech enhancement problem by using WavLM's denoising capability.
 

### 2024-09-06 src/paper.tex
update

@@
 \begin{table*}
+    \caption{The performance of different systems on Libri2Mix testset. For TSELM-L-Hybrid  
+    and TSELM, we compare the speaker similarity with the discretized target speech 
+    (Target-discrete-WavLM) instead of the target speech due to the observation that 
+    the process of discretization already losses the speaker information (0.653 for 
+    Target-discrete-WavLM). We use "\_d" to denote it.  }
     \setlength{\tabcolsep}{12pt} % Adjust column spacing
@@
             \hline
-            Continuous-WavLM   & G    & Continuous                  & 220M                        & 3.56    & 4.06    & 3.27   & 14.7\%                & 0.877                    \\
+            Continuous-WavLM-L6   & G    & Continuous                  & 220M                        & 3.56    & 4.06    & 3.27   & 14.7\%                & 0.877                    \\
             TSELM-L-Hybrid    & G       & Hybrid                      & 468M                        & 3.50    & 4.06    & 3.22   & 19.8\%                & 0.924\_d                 \\
@@
             \linebreak
-            \caption{The performance of different systems on Libri2Mix testset. For TSELM-L-Hybrid  
-            and TSELM, we compare the speaker similarity with the discretized target speech 
-            (Target-discrete-WavLM) instead of the target speech due to the observation that 
-            the process of discretization already losses the speaker information (0.653 for 
-            Target-discrete-WavLM). We use "\_d" to denote it.  }
             \label{main_exp}
       \end{center}
+    %   \vspace{-10pt}
   \end{table*}
@@
 \section{Experiments}
+
+\begin{table}
+
+    \renewcommand{\arraystretch}{1.2}
+    \begin{center}
+        \begin{tabular}{ccccccc}
+            \Xhline{2\arrayrulewidth} % Bold top line
+            \multirow{2}{*}{SSL-Model} & \multirow{2}{*}{Type} & \multicolumn{3}{c}{ DNSMOS $\uparrow$} & \multirow{2}{*}{dWER $\downarrow$} & \multirow{2}{*}{Spk Sim $\uparrow$} \\
+            \cline{3-5}
+                                                       &                             & SIG     & BAK     & OVL    &                       &                          \\ 
+            \hline
+            \multirow{2}{*}{Hubert}                              &  Discrete                          & 3.56    & 4.09    & 3.30   & 81.3\%                & 0.865\_d                        \\
+                                             &  Hybrid                          & 3.57    & 4.10    & 3.32   & 35.1\%                & 0.907\_d                        \\
+            \hline
+            \multirow{2}{*}{WavLM-L6}                              &  Discrete                          & 2.08    & 2.07    & 1.64   & 122.1\%                & 0.589\_d                        \\
+            &  Hybrid                          & 3.54    & 3.84    & 3.12   & 30.0\%                & 0.849\_d                        \\
+            \hline
+            \hline
+            \multirow{2}{*}{WavLM}                                     &  Discrete                          & 3.49    & 4.05    & 3.22   & 27.1\%                & 0.905\_d                        \\
+                                              &  Hybrid                          & 3.50    & 4.06    & 3.22   & 19.8\%                & 0.924\_d                        \\
+
+            \Xhline{2\arrayrulewidth} % Bold top line              
+            \end{tabular}
+            \label{abla_1}
+
+      \end{center}
+      \caption{Iwdad}
+      \vspace{-25pt}
+    \end{table}
 
@@
 
+\section{Conclusion}
+
 \section*{Acknowledgment}

### 2024-09-06 src/paper.tex
update

@@
 
+  \begin{table}
+
+    \renewcommand{\arraystretch}{1.2}
+    \begin{center}
+        \begin{tabular}{ccccccc}
+            \Xhline{2\arrayrulewidth} % Bold top line
+            \multirow{2}{*}{SSL-Model} & \multirow{2}{*}{Type} & \multicolumn{3}{c}{ DNSMOS $\uparrow$} & \multirow{2}{*}{dWER $\downarrow$} & \multirow{2}{*}{Spk Sim $\uparrow$} \\
+            \cline{3-5}
+                                                       &                             & SIG     & BAK     & OVL    &                       &                          \\ 
+            \hline
+            \multirow{2}{*}{HuBERT}                              &  Discrete                          & 3.56    & 4.09    & 3.30   & 81.3\%                & 0.865\_d                        \\
+                                             &  Hybrid                          & 3.57    & 4.10    & 3.32   & 35.1\%                & 0.907\_d                        \\
+            \hline
+            \multirow{2}{*}{WavLM-L6}                              &  Discrete                          & 2.08    & 2.07    & 1.64   & 122.1\%                & 0.589\_d                        \\
+            &  Hybrid                          & 3.54    & 3.84    & 3.12   & 30.0\%                & 0.849\_d                        \\
+            \hline
+            \hline
+            \multirow{2}{*}{WavLM}                                     &  Discrete                          & 3.49    & 4.05    & 3.22   & 27.1\%                & 0.905\_d                        \\
+                                              &  Hybrid                          & 3.50    & 4.06    & 3.22   & 19.8\%                & 0.924\_d                        \\
+
+            \Xhline{2\arrayrulewidth} % Bold top line              
+            \end{tabular}
+            \linebreak
+            \caption{Performance of different SSL models and layer selections. HuBERT model subsitutes the WavLM Large to HuBERT Large as the SSL model.
+            The WavLM-L6 uses only the 6th layer of hidden output of WavLM Large. WavLM denotes our TSELM model which uses 6 different output layers. 
+            }
+            \label{hubert_wavlm_6}
+      \end{center}
+      \vspace{-25pt}
+    \end{table}
+
 We use pretrained SSL model WavLM Large \cite{wavlm} to 
@@
 \section{Experiments}
-
-\begin{table}
-
-    \renewcommand{\arraystretch}{1.2}
-    \begin{center}
-        \begin{tabular}{ccccccc}
-            \Xhline{2\arrayrulewidth} % Bold top line
-            \multirow{2}{*}{SSL-Model} & \multirow{2}{*}{Type} & \multicolumn{3}{c}{ DNSMOS $\uparrow$} & \multirow{2}{*}{dWER $\downarrow$} & \multirow{2}{*}{Spk Sim $\uparrow$} \\
-            \cline{3-5}
-                                                       &                             & SIG     & BAK     & OVL    &                       &                          \\ 
-            \hline
-            \multirow{2}{*}{Hubert}                              &  Discrete                          & 3.56    & 4.09    & 3.30   & 81.3\%                & 0.865\_d                        \\
-                                             &  Hybrid                          & 3.57    & 4.10    & 3.32   & 35.1\%                & 0.907\_d                        \\
-            \hline
-            \multirow{2}{*}{WavLM-L6}                              &  Discrete                          & 2.08    & 2.07    & 1.64   & 122.1\%                & 0.589\_d                        \\
-            &  Hybrid                          & 3.54    & 3.84    & 3.12   & 30.0\%                & 0.849\_d                        \\
-            \hline
-            \hline
-            \multirow{2}{*}{WavLM}                                     &  Discrete                          & 3.49    & 4.05    & 3.22   & 27.1\%                & 0.905\_d                        \\
-                                              &  Hybrid                          & 3.50    & 4.06    & 3.22   & 19.8\%                & 0.924\_d                        \\
-
-            \Xhline{2\arrayrulewidth} % Bold top line              
-            \end{tabular}
-            \label{abla_1}
-
-      \end{center}
-      \caption{Iwdad}
-      \vspace{-25pt}
-    \end{table}
 
@@
 
+In Table \ref{hubert_wavlm_6}, we have compared the performance of different SSL models and the selection between one layer or multiple layers to discretize. 
+Our results have shown that the using HuBERT as SSL model has achieved better DNSMOS scores but with worse dWER compared to our WavLM baseline.
+The better DNSMOS scores might be related to the vocoders but it does not reflect the speech intelligibility which is important in speech separation. 
+For dWER, this might be because that HuBERT is trained on clean speech and that it might not capture the rich speech information of mixed speeches. 
+Our results from WavLM-L6 have shown that for speech separation, using multiple layers to discretize is better than using only one layer.
+
+Finally, we have observed a performance gap between discrete methods and continuous methods.
+
 \section{Conclusion}

### 2024-09-06 src/paper.tex
update

@@
 \usepackage{etoolbox}
+\usepackage{hyperref}
 
@@
 
-\title{Target Speaker Extraction using Discrete Representations from 
-Self-Supervised Models and Language Models
+\title{TSELM: Target speaker extraction using discrete tokens and language models
 \thanks{Identify applicable funding agency here. If none, delete this.}
@@
 \and
-\IEEEauthorblockN{3\textsuperscript{re} Ming Li}
+\IEEEauthorblockN{3\textsuperscript{rd} Ming Li}
 \IEEEauthorblockA{\textit{Duke Kunshan University} \\
@@
 
-Finally, we have observed a performance gap between discrete methods and continuous methods.
+Finally, we have observed a performance gap between discrete methods and continuous methods (Continuous-WavLM-L6) on target 
+speaker extraction as shown in Table \ref{main_exp}. For Continuous-WavLM-L6,
+we use the 6th layer embedding output from WavLM from both the mixed speech and reference speech, and use MSE loss between the output from LM and the clean embeddings. This method 
+has the best performance in terms of DNSMOS and dWER. It has a better dWER of 13.6\% compared with TSELM-L. This might be related to the 
+information loss of discretization process. We hope future research will work to bridge the gap.
 

### 2024-09-06 src/paper.tex
update

@@
 has the best performance in terms of DNSMOS and dWER. It has a better dWER of 13.6\% compared with TSELM-L. This might be related to the 
-information loss of discretization process. We hope future research will work to bridge the gap.
+information loss of discretization process. We hope future research will work to bridge this gap.
 
 \section{Conclusion}
+In this work, we introduced a novel way using discrete tokens and language models for target speaker extraction. Experiments have 
+shown that our model can achieve excellent performance in terms of speech quality, and comparable performance in terms of speech intelligibility and 
+speaker similarity. However, we still have a gap between continuous methods especially in speech intelligibility.
 
-\section*{Acknowledgment}
+% \section*{Acknowledgment}
 
-We want to thank for Kunshan Super Computing SCNet for providing the computing resources.
+% We want to thank for Kunshan Super Computing SCNet for providing the computing resources.
 

### 2024-09-06 src/paper.tex
update

@@
 \section{Conclusion}
-In this work, we introduced a novel way using discrete tokens and language models for target speaker extraction. Experiments have 
+In this work, we introduced a novel way using discrete tokens and language models for target speaker extraction.
+We use multiple hidden layers of WavLM and Kmeans tokenizers as encoder, cross attention and language model as our separation model, and a scalable HiFi-GAN to reconstruct the 
+audio. 
+Experiments have 
 shown that our model can achieve excellent performance in terms of speech quality, and comparable performance in terms of speech intelligibility and 
-speaker similarity. However, we still have a gap between continuous methods especially in speech intelligibility.
+speaker similarity. However, we still have a gap between continuous methods especially in speech intelligibility and speaker similarity. Future research should focus on shrinking 
+this gap.
 

### 2024-09-06 src/paper.tex
update

@@
 \begin{abstract}
-This document is a model and instructions for \LaTeX.
-This and the IEEEtran.cls file define the components of your paper [title, text, heads, etc.]. *CRITICAL: Do Not Use Symbols, Special Characters, Footnotes, 
-or Math in Paper Title or Abstract. 
+We present TSELM, a novel target speaker extraction network using discrete tokens and language models. This model utilizes multiple discretized layers
+of WavLM Large as input tokens. It uses cross attention to inject target speaker information and language models to model the sequences. 
 \end{abstract}

### 2024-09-06 src/paper.tex
update

@@
 \title{TSELM: Target speaker extraction using discrete tokens and language models
-\thanks{Identify applicable funding agency here. If none, delete this.}
+\thanks{Our demos are available at: }
 }
@@
 We present TSELM, a novel target speaker extraction network using discrete tokens and language models. This model utilizes multiple discretized layers
-of WavLM Large as input tokens. It uses cross attention to inject target speaker information and language models to model the sequences. 
+of WavLM Large as input tokens. It uses cross attention to inject target speaker information and language models to model the sequences. It uses 
+a scalable HiFi-GAN to reconstruct the audio from the tokens. It uses 
+cross entropy loss to model the probability of output tokens, transforming the complex regression problems into classification problems. To the best of our 
+knowledge, we are the first to do target speaker extraction using discrete tokens. However, there is still a gap between our model and continuous methods. 
+Our codes and pretrained models are available at: .
 \end{abstract}

### 2024-09-06 src/paper.tex
update

@@
 \title{TSELM: Target speaker extraction using discrete tokens and language models
-\thanks{Our demos are available at: }
 }
@@
 knowledge, we are the first to do target speaker extraction using discrete tokens. However, there is still a gap between our model and continuous methods. 
-Our codes and pretrained models are available at: .
+Our codes and pretrained models are available at: \href{https://github.com/Beilong-Tang/TSELM}{https://github.com/Beilong-Tang/TSELM} .
 \end{abstract}
@@
 \section{Introduction}
-Speech separation, the so-called cocktail party problem \cite{cocktail}, focuses on separating each individual speaker's source from a mixture with multiple speakers.
+% Speech separation, the so-called cocktail party problem \cite{cocktail}, focuses on separating each individual speaker's source from a mixture with multiple speakers.
 This task is easy for humans but not for computers.
-In real life, speech signals are usually companied with background noise or other speakers' speeches. 
-These corrupted signals may not be optimal for tasks like speaker verification \cite{rao2019targetspeakerextractionoverlapped,9414017}, and speech recognition \cite{molkov2017SpeakerAwareNN, 8462661}, emphasizing the importance of having good and robust
-speech separation models.
+% In real life, speech signals are usually companied with background noise or other speakers' speeches. 
+% These corrupted signals may not be optimal for tasks like speaker verification \cite{rao2019targetspeakerextractionoverlapped,9414017}, and speech recognition \cite{molkov2017SpeakerAwareNN, 8462661}, emphasizing the importance of having good and robust
+% speech separation models.
 
@@
 of speech quality and intelligibility. To the best of our knowledge, we are the first to explore 
-using discrete tokens to conduct target speaker extraction.
+using discrete tokens to conduct target speaker extraction. Our demos are available at \href{https://beilong-tang.github.io/TSELM.demo/}{https://beilong-tang.github.io/TSELM.demo/}.
 

### 2024-09-06 src/paper.tex
update

@@
 Unlike blind speech separation, which focuses on separating each utterance from a mixture 
-of known speakers, target speaker extraction aims at only extracting the 
-target speaker's voice given another auxiliary information of the target speaker. Due to the 
-development of Deep Neural Network (DNN), many models nowadays are discriminative models. They 
+of known speakers, target speaker extraction (TSE) aims at only extracting the 
+target speaker's voice given another auxiliary information of the target speaker. Most models nowadays are discriminative models. They 
 utilize a masking strategy to minimize the distance between the clean speech and estimated 

### 2024-09-06 src/paper.tex
initial version

@@
 models may not generalize well to unseen data and might even introduce unwanted distortions \cite{distortion}. 
-To solve these issues, researchers have proposed generative models.
-This method aims to learn the underlying distribution of the target speaker's voice and use this knowledge to generate the clean speech of the target speaker from a mixture of voices rather
-than directly mapping from mixed speech to clean speech. Some generative models, like diffusion
+To solve these issues, researchers have proposed generative models. This method aims to learn the underlying distribution of the target speech and generate it rather
+than mapping from mixed speech to clean speech. 
+Some generative models, like diffusion
 models \cite{target_diff} and variational autoencoders (VAE) \cite{vae} have been studied. 

### 2024-09-06 src/paper.tex
update

@@
 \section{Introduction}
-% Speech separation, the so-called cocktail party problem \cite{cocktail}, focuses on separating each individual speaker's source from a mixture with multiple speakers.
-This task is easy for humans but not for computers.
-% In real life, speech signals are usually companied with background noise or other speakers' speeches. 
-% These corrupted signals may not be optimal for tasks like speaker verification \cite{rao2019targetspeakerextractionoverlapped,9414017}, and speech recognition \cite{molkov2017SpeakerAwareNN, 8462661}, emphasizing the importance of having good and robust
-% speech separation models.
 
-Unlike blind speech separation, which focuses on separating each utterance from a mixture 
-of known speakers, target speaker extraction (TSE) aims at only extracting the 
-target speaker's voice given another auxiliary information of the target speaker. Most models nowadays are discriminative models. They 
-utilize a masking strategy to minimize the distance between the clean speech and estimated 
-speech directly \cite{luo2019conv,spex_plus,sepformer,sef_net}. However, these discriminative 
-models may not generalize well to unseen data and might even introduce unwanted distortions \cite{distortion}. 
-To solve these issues, researchers have proposed generative models. This method aims to learn the underlying distribution of the target speech and generate it rather
-than mapping from mixed speech to clean speech. 
-Some generative models, like diffusion
-models \cite{target_diff} and variational autoencoders (VAE) \cite{vae} have been studied. 
-It has been demonstrated that generative models can achieve results comparable to those of discriminative models \cite{target_diff,tokensplit}.
+In contrast to blind speech separation, which seeks to isolate individual utterances from a mixture of known speakers, target speaker extraction (TSE) focuses on extracting only the voice of the target speaker using auxiliary information specific to that speaker.
+Current models are predominantly discriminative, employing masking strategies to directly minimize the distance between the estimated and clean speech signals \cite{luo2019conv,spex_plus,sepformer,sef_net}.
+However, these discriminative approaches often struggle to generalize to unseen data and may introduce undesirable distortions \cite{distortion}.
+To address these limitations, generative models have been proposed.
+These models aim to learn the underlying distribution of the target speech and generate it, rather than merely mapping mixed speech to clean speech.
+Generative models have been shown to achieve performance comparable to that of discriminative models \cite{target_diff,tokensplit} in blind speech separation and TSE.
 
-Discretization of audio has been studied due to the advancement of language models (LM). 
-This approach translates the audio into discrete tokens simulating text vocabularies and uses LMs to 
-model them. This approach simplifies audio generation tasks by transforming the complex 
-regression problems into classification problems \cite{dasb}. There are currently two approaches for
-audio discretization, the first one uses neural audio codecs \cite{dac}. This approach 
-typically captures the acoustic features of the audio \cite{speech_tokenizer}. The second approach 
-utilizes  self-supervised Learning (SSL) models like HuBERT \cite{hubert} and WavLM \cite{wavlm}.
-SSL models have demonstrated 
-excellent performances on many downstream tasks \cite{superb}. These SSL models extract  
-continuous representations containing rich semantic and timbre information from a given speech. 
-As demonstrated in \cite{dasb}, SSL models perform better than audio codec in tasks like speech 
-enhancement and speech separation. Therefore, in this 
-paper, we mainly explore the discretization of SSL models.
+The discretization of audio has gained significant attention with the advancement of language models (LMs).
+This method converts audio into discrete tokens, allowing LMs to model them, thereby simplifying audio generation tasks by transforming complex regression problems into classification tasks \cite{dasb}.
+Currently, there are two main approaches to audio discretization.
+The first involves the use of neural audio codecs \cite{dac}, which typically capture the acoustic features of the audio \cite{speech_tokenizer}.
+The second approach leverages self-supervised learning (SSL) models, such as HuBERT \cite{hubert} and WavLM \cite{wavlm}.
+SSL models have demonstrated outstanding performance across numerous downstream tasks \cite{superb}, as they extract continuous representations rich in semantic and timbral information from speech.
+As shown in \cite{dasb}, SSL models outperform neural audio codecs in tasks like speech enhancement and separation.
+Consequently, this paper primarily focuses on exploring the discretization of SSL models.
 

### 2024-09-06 src/paper.tex
update

@@
 \begin{abstract}
-We present TSELM, a novel target speaker extraction network using discrete tokens and language models. This model utilizes multiple discretized layers
-of WavLM Large as input tokens. It uses cross attention to inject target speaker information and language models to model the sequences. It uses 
-a scalable HiFi-GAN to reconstruct the audio from the tokens. It uses 
-cross entropy loss to model the probability of output tokens, transforming the complex regression problems into classification problems. To the best of our 
-knowledge, we are the first to do target speaker extraction using discrete tokens. However, there is still a gap between our model and continuous methods. 
-Our codes and pretrained models are available at: \href{https://github.com/Beilong-Tang/TSELM}{https://github.com/Beilong-Tang/TSELM} .
+  We propose TSELM, a novel target speaker extraction network that leverages discrete tokens and language models.
+The model utilizes multiple discretized layers from WavLM Large as input tokens and incorporates cross-attention mechanisms to integrate target speaker information.
+Language models are employed to capture the sequence dependencies, while a scalable HiFi-GAN is used to reconstruct the audio from the tokens.
+By applying a cross-entropy loss, TSELM models the probability distribution of output tokens, thus converting the complex regression problem of audio generation into a classification task.
+To the best of our knowledge, this is the first approach to target speaker extraction using discrete tokens.
+However, a performance gap remains between our method and continuous approaches.
+The code and pretrained models are available at: \href{https://github.com/Beilong-Tang/TSELM}{https://github.com/Beilong-Tang/TSELM}.
 \end{abstract}
@@
 \begin{IEEEkeywords}
-target speaker extraction, speech separation, language models, audio discretization
+target speaker extraction, speech separation, language models, audio discretization, Self-Supervised Models
 \end{IEEEkeywords}
@@
 enhancement \cite{selm} and blind speech separation \cite{dasb,tokensplit}, 
-however, this approach has 
-been rarely studied for target speaker extraction. In this paper, we present a novel way to do 
-target speaker extraction using discrete tokens and LMs (TSELM). Inspired by the blind speech separation 
+however, it has 
+rarely been studied for TSE. In this paper, we present a novel way to do 
+target speaker extraction using discrete tokens and LMs called \textbf{TSELM}. Inspired by the blind speech separation 
 networks proposed in DASB \cite{dasb}, our model has three stages: encoding, modeling and decoding.

### 2024-09-06 src/paper.tex
update

@@
 
-Discretization methods have been studied for speech 
-enhancement \cite{selm} and blind speech separation \cite{dasb,tokensplit}, 
-however, it has 
-rarely been studied for TSE. In this paper, we present a novel way to do 
-target speaker extraction using discrete tokens and LMs called \textbf{TSELM}. Inspired by the blind speech separation 
-networks proposed in DASB \cite{dasb}, our model has three stages: encoding, modeling and decoding.
-For the encoding stage, reference speech and mixed speech are tokenized using WavLM and 
-Kmeans as tokenizer. Unlike SELM \cite{selm}, which uses the 6th layer of WavLM as input to the Kmeans layer, 
-we follow the recipes in \cite{dasb} and uses the output from hidden 
-layers 1, 3, 7, 12, 18, 23 of WavLM as input to the Kmeans layer. 6 Kmeans models
-are trained and applied on each layer output respectively. 
-Our results indicate that using multiple layers as 
-input is better 
-than using only the 6th layer. The reference speech is fed to the encoder directly. 
-However, for the mixed speech, instead of directly passing it to the WavLM model, we first concatenated the reference speech on both sides 
-of it before passing. After tokenization, we use only the tokens 
-corresponding to the mixed speech. For the modeling stage, we utilized an attention 
-embedding mechanism to add each embeddings of all layers together. We used a Cross 
-Attention mechanism similar in \cite{sef_net} to inject the speaker information. 
-An encoder-only LM, following by a linear classifier, is applied after the cross attention module
-to output the reconstructed tokens. 
-For the decoding stage, we used the pretrained unit HiFi-GAN 
-in \cite{unit_hifi} to reconstruct the 
-discrete tokens back to audio. Unlike SELM \cite{selm}, where a conformer 
-detokenizer is trained 
-to reconstruct the WavLM embeddings using Kmeans center embeddings before HiFi-GAN, \cite{unit_hifi} has proposed a scalable HiFi-GAN using dropout mechanism to directly 
-reconstruct audio from multiple layers of tokens without a conformer detokenizer. It 
-has also eliminated the trouble of training a HiFi-GAN for each layer. The encoder and 
-decoder is freezed during the training. The model overview is in Fig.\ref{model}. 
-Through extensive studies, we have demonstrated this method has achieved comparable results in terms 
-of speech quality and intelligibility. To the best of our knowledge, we are the first to explore 
-using discrete tokens to conduct target speaker extraction. Our demos are available at \href{https://beilong-tang.github.io/TSELM.demo/}{https://beilong-tang.github.io/TSELM.demo/}.
+Discretization methods have been explored for tasks such as speech enhancement \cite{selm} and blind speech separation \cite{dasb,tokensplit}, but their application to target speaker extraction (TSE) has been limited.
+In this paper, we present a novel approach to target speaker extraction using discrete tokens and language models, named \textbf{TSELM}.
+Inspired by the blind speech separation networks proposed in DASB \cite{dasb}, our model is structured into three stages: encoding, modeling, and decoding.
+
+In the encoding stage, both reference and mixed speech are tokenized using WavLM and Kmeans as the tokenizer.
+Unlike SELM \cite{selm}, which utilizes the 6th layer of WavLM as input to the Kmeans layer, we follow the approach in \cite{dasb} and use outputs from WavLM's hidden layers 1, 3, 7, 12, 18, and 23 as input to six separate Kmeans models, one for each layer.
+Our results show that using multiple layers as input is superior to using only the 6th layer.
+The reference speech is passed directly to the encoder, while for mixed speech, we concatenate the reference speech to both sides of the mixture before passing it through the WavLM model.
+After tokenization, we retain only the tokens corresponding to the mixed speech.
+In the modeling stage, an attention embedding mechanism is employed to combine the embeddings from all layers.
+A cross-attention mechanism, similar to that used in \cite{usef_tes}, is applied to inject speaker-specific information.
+An encoder-only language model, followed by a linear classifier, is then used to generate the reconstructed tokens.
+In the decoding stage, we leverage the pretrained scalable HiFi-GAN from \cite{unit_hifi} to reconstruct the audio from the discrete tokens.
+Unlike SELM \cite{selm}, where a conformer detokenizer is trained to reconstruct WavLM embeddings before passing them through HiFi-GAN, the scalable HiFi-GAN in \cite{unit_hifi} uses a dropout mechanism to directly reconstruct audio from multiple layers of tokens, eliminating the need for a conformer detokenizer and the complexity of training a separate HiFi-GAN for each layer.
+Both the encoder and decoder are kept frozen during training, and an overview of the model is shown in Fig.\ref{model}.
+Extensive experiments demonstrate that our method achieves excellent speech quality and comparable intelligibility results.
+To the best of our knowledge, this is the first study to explore target speaker extraction using discrete tokens.
+Our demos are available at \href{https://beilong-tang.github.io/TSELM.demo/}{https://beilong-tang.github.io/TSELM.demo/}.
 
 \section{Method}
-Our model consists of three stages: encoding, modeling, and decoding. The encoder and decoder are 
-pretrained models and they are freezed during training. For the encoding stage, we use multiple layers of WavLM 
-and publicly available Kmeans 
-models in \cite{dasb} to produce the discretized tokens. We use a special concatenation 
-strategy to encode the mixture speech. For decoders, we use the scalable HiFi-GAN available in 
-\cite{dasb} to reconstruct the audio from discretized tokens. Our main focus is on the
-modeling stage. We apply an attention embedding mechanism to embed discrete tokens from different 
-layers into one single embedding. Encoder-only LM and linear classifier is applied afterwards to optimize the likelihood of probability 
-distribution of the clean tokens.
+% Our model consists of three stages: encoding, modeling, and decoding. The encoder and decoder are 
+% pretrained models and they are freezed during training. For the encoding stage, we use hidden layers 1, 3, 7, 12, 18, and 23 (denoted as \(n_l\)) of WavLM-Large 
+% and publicly available Kmeans 
+% models in \cite{dasb} to produce the discretized tokens. We use a concatenation 
+% strategy to encode the mixture speech. For decoders, we use the scalable HiFi-GAN available in 
+% \cite{dasb} to reconstruct the audio from discretized tokens. Our main focus is on the
+% modeling stage. We apply an attention embedding mechanism to embed discrete tokens from different 
+% layers into one single embedding. Encoder-only LM and linear classifier is applied afterwards to optimize the likelihood of probability 
+% distribution of the clean tokens.
 
@@
 
-We use pretrained SSL model WavLM Large \cite{wavlm} to 
-encode the speech into continuous representations. We use the output from 6 hidden 
-layers 1, 3, 7, 12, 18, 23. Given a speech signal \(s \in R^{T'} \), the output 
-of WavLM will be a tensor \(\bm{r}\) of shape \(n \times T \times E\) where 
-\(n\) specifies the number 
-of output layers (6 in this case), and  \(T\) is the time 
-dimension and \(E\) stands for the 
-embedding dimension, specifically 1024 in WavLM Large. The Kmeans tokenizer uses \(n\) numbers of  Kmeans model 
-separately on each output layer. Each model uses the same clustering number denoted by \(K\).
-After tokenization, the continuous embedding \(\bm{r}\) will be transformed to a tensor \(\bm{d}\) of shape \(n \times T\) where each value \(\bm{d}_{(n_i,t)} \in (0, K-1), n_i \in (0,n), t \in 
-(0, T)\). We choose \(K\) to be 1000 in our experiments. For reference speech and mixed speech, we 
-use the same Kmeans model and the same layer output of WavLM. The encoder is freezed during training.
-
-The encoding strategy on the mixed speech plays a pivotal role in the model performance. Assume we 
-have a reference speech \(s_r \in R^{T^r} \) and mixed speech \(s \in R^{T'}\). 
-We follow the 
-aforementioned procedure for 
-reference speech to get tensor \(\bm{d_r}\) of shape \(n \times T_r\). But for the mixed 
-speech, instead of directly following the procedure, we first concatenate it with 
-the reference speech to get \(s' = [s_r, s_m, s_r] \in R^{(T^r+T'+T^r)}\). Then we use this speech 
-as input for the encoder, obtaining output \(\bm{d'}\) of shape \(n \times (T_r+T+T_r)\) where \(T\) 
-denotes the length of output by directly passing the mixed speech without concatenation. \(\bm{d'}\) 
-contains the discrete tokens for two pieces of the same reference speech and one piece of the mixed 
-speech, we select tensor \(\bm{d}\) belonging only to the mixed speech of shape \(n\times T\) as the 
-encoder output. This process is inspired by the training schema of WavLM \cite{wavlm}. To ensure the 
-model correctly outputs rich information of the target speaker, it is trained by 
-having a clean speech overlapped with another interference less than 50\% of the length of the clean 
-speech and using the first utterance as the main speaker. By this way, the model identifiers the 
-main speaker and produces embedding focusing on the main speaker. Our later experiments showed that 
-this strategy plays an important role in the model performance.
-
+We use the pretrained self-supervised learning (SSL) model WavLM Large \cite{wavlm} to encode speech into continuous representations.
+Specifically, we extract the outputs from six hidden layers: 1, 3, 7, 12, 18, and 23.
+Given a speech signal \(s \in \mathbb{R}^{T'}\), the output of WavLM is a tensor \(\bm{r}\) with shape \(n \times T \times E\), where \(n\) is the number of output layers (6 in this case), \(T\) is the time dimension, and \(E\) represents the embedding dimension, which is 1024 in WavLM Large.
+For tokenization, we apply separate Kmeans models to each output layer, with each model using the same number of clusters, denoted by \(K\).
+After tokenization, the continuous embedding \(\bm{r}\) is transformed into a discrete tensor \(\bm{d}\) with shape \(n \times T\), where each value \(\bm{d}_{i} \in (0, K-1) \).
+In all our experiments, we set \(K = 1000\).
+For both reference and mixed speech, the same Kmeans model and the same layer combination from WavLM Large are used.
+The encoder remains frozen during training.
+The encoding strategy for mixed speech is crucial to the performance of the model.
+Given a reference speech \(s_r \in \mathbb{R}^{T^r}\) and a mixed speech \(s_m \in \mathbb{R}^{T'}\), we follow the previously described procedure to encode the reference speech into a tensor \(\bm{d_r}\) of shape \(n \times T_r\).
+However, for mixed speech, instead of applying the encoding directly, we first concatenate it with the reference speech, creating a signal \(s' = [s_r, s_m, s_r] \in \mathbb{R}^{(T^r + T' + T^r)}\).
+This concatenated signal is then input into the encoder, producing an output tensor \(\bm{d'}\) with shape \(n \times (T_r + T + T_r)\), where \(T\) represents the time dimension for the mixed speech without concatenation.
+The tensor \(\bm{d'}\) contains discrete tokens for the two segments of reference speech and the mixed speech.
+We extract the portion \(\bm{d}\) corresponding only to the mixed speech, resulting in an output tensor of shape \(n \times T\).
+This approach is inspired by the training schema of WavLM \cite{wavlm}, which trains the model by overlapping clean speech with an interfering signal that covers less than 50\% of the clean speech's duration, using the first utterance as the primary speaker.
+This allows WavLM to identify and focus on the main speaker when producing embeddings.
+Our experiments demonstrated that this concatenation strategy significantly enhances the model's performance by guiding it to prioritize the target speaker's information.
 \subsection{Modeling}
 \subsubsection{Attention Embedding}
-After obtaining the discrete tensor \(\bm{d}\) with shape \(n\times T\), we use 6
+After obtaining the discrete tensor \(\bm{d}\) with shape \(6 \times T\), we use 6
 learnable embedding tables each with \(K\) entires to embed the 6 layers 

### 2024-09-06 src/paper.tex
update

@@
     \centering
-    \includegraphics[width=\textwidth]{assets/model.pdf}
+    \includegraphics[width=0.9\textwidth]{assets/model.pdf}
     \caption{Overview of TSELM.}
@@
         \centering
-        \includegraphics[width=0.35\textwidth]{assets/cross_attention.pdf}
+        \includegraphics[width=0.25\textwidth]{assets/cross_attention.pdf}
         \caption{Details of Cross Attention mechanism.}
@@
     \setlength{\tabcolsep}{12pt} % Adjust column spacing
-    \renewcommand{\arraystretch}{1.3}
+    \renewcommand{\arraystretch}{1.2}
     \begin{center}
@@
             Mixture                 & - & -                           & -                           & 3.39    & 3.14    & 2.68   & 79.3\%                & -                        \\
-            Target-discrete-WavLM   & G & -                          & 330M                           & 3.57    & 4.10    & 3.32   & 11.3\%                & 0.653                    \\
+            Target-Discrete   & G & -                          & 330M                           & 3.57    & 4.10    & 3.32   & 11.3\%                & 0.653                    \\
             \hline
@@
 
-    \renewcommand{\arraystretch}{1.2}
+    \renewcommand{\arraystretch}{1.1}
     \begin{center}
@@
       \end{center}
-      \vspace{-25pt}
+      \vspace{-32.5pt}
     \end{table}
@@
 \subsubsection{Cross Attention}
-One of the key factors in target speaker extraction is to 
-inject the information of target speaker 
-into the mixture. Spex+ \cite{spex_plus} jointly trains a speaker verification task module 
-besides the separator, which might not be optimal for the separator task \cite{sef_net}. SEF-Net \cite{sef_net} has proposed an speaker embedding free way to inject the 
-target speaker information into the mixture by using cross attention module, and it has 
-achieved superior performance compared to other methods. Therefore, we apply 
-the cross attention module to inject the reference embedding into the mixture. The details 
-are in Fig.\ref{cross_attention}.
-The cross attention module consists of a stack of cross-multiple head attention modules, 
-and a FiLM module. 
+We apply cross attention module in \cite{usef_tes} to inject the reference embeddings into the mixture. The details 
+are shown in Fig.\ref{cross_attention}.
+The cross attention module consists of a stack of cross-multiple head attention modules, followed by
+a feature-wise linear modulation (FiLM) module. 
 We use \(E_m\) as query and \(E_r\) as key and value for 
-the attention module. The output of the cross-multiple head attention module \(E_{spk}\)
-is passed together with \(E_m\) to the feature-wise linear modulation (FiLM) get the final output of the module. The output of 
-FiLM is denoted as \(E_f = FiLM(E_m, E_{spk}) = \gamma E_{spk} \cdot E_m  + \beta E_{spk} \) where 
+the attention module. The output from the cross-multiple head attention module \(E_{spk}\)
+is passed together with \(E_m\) to the FiLM to obtain the final output. The output of 
+FiLM  \(E_f = FiLM(E_m, E_{spk}) = \gamma E_{spk} \cdot E_m  + \beta E_{spk} \) where 
 \(\gamma\) and \(\beta\) are learnable parameters denoting the scaling and shifting vectors 
-respectively. The output is then fed to the language model for later modeling.  
+respectively.
+
 \subsubsection{Language Modeling}
-We use encoder-only language models containing multiple self-attention modules to model the injected 
+We use encoder-only transformers containing multiple self-attention modules to model the 
 embedding \(E_f\). Due to encoder-only style, the LM is able to learn from all the positions. 
-Finally, 6 linear classifiers each with dimension \(K\) is used to produce the probability 
-distribution of each layer respectively.
-Cross-entropy loss is applied between 
-the output tokens and the clean tokens through discretizing the 
-ground truth clean audio.
+Finally, 6 linear classifiers each with dimension \(K\) is used to produce the logit scores of the tokens.
+Cross-entropy loss is applied between the predicted tokens and the clean tokens, which are obtained by discretizing the ground truth clean audio.
 
@@
 HiFi-GAN decoder in \cite{speechbrain}. The Kmeans tokenizer
-is trained on \texttt{train\_clean\_100}, \texttt{train\_clean\_360}, and \texttt{train\_other\_500} of
+is trained on \texttt{train\_clean\_[100,360,500]} of
 LibriSpeech \cite{librispeech}, and the scalable HiFi-GAN is trained on \texttt{train\_clean\_100} of 
 LibriTTS \cite{libritts}. The modeling stage is trained on 
-\texttt{train\_clean\_100} and \texttt{train\_clean\_360} of LibriSpeech. All training data are 
-generated on the fly with relative SNR between 0 dB to 5 dB. The mixture audio is segmented to 3 
-seconds and the reference speech is segmented to 4 seconds.
+\texttt{train\_clean\_[100,360]} of LibriSpeech. All training data are 
+generated on the fly with relative SNR between 0 to 5 dB. The mixture audio and reference audio is clipped to 3 and 4 seconds, respectively.
 
-We use the output from hidden layers 1, 3, 7, 12, 18, 23 from WavLM Large and Kmeans model with 
+We utilize the output from hidden layers 1, 3, 7, 12, 18, 23 from WavLM Large and Kmeans model with 
 \(K=1000\).
-We use embedding dimension 1024,  4 transformer 
-encoders each with 16 heads and MLP with hidden dimension of 1024 in the cross attention module. We 
-use layer norm after the cross attention module. 
-We use separate embedding tables in attention embedding module for reference and mixed speech due to our observations that not 
-sharing embeddings does slightly better than sharing embeddings. The LM of small version TSELM-S uses 
-embedding dimension \(d\) = 256, absolute sinusoidal positional embedding, conformer encoders as backbone of LM. The conformer encoder is composed of 
-6 layers with kernel size 31 each with 4 heads and an MLP with hidden dimension 2048. The medium version TSELM-M uses \(d\) = 512 with 8 layers and 8 heads and the large version TSELM-L uses 
+We use embedding dimension 1024.
+The cross-attention module consists of four transformer encoders, each with 16 attention heads and an MLP with a hidden dimension of 1024.
+Layer normalization is applied after the cross-attention module.
+The LM of small version TSELM-S uses 
+embedding dimension \(d\) = 256, absolute sinusoidal positional embedding, conformer encoders as backbone of LM.
+The conformer encoder consists of 6 layers with a kernel size of 31, each with 4 attention heads, and an MLP with a hidden dimension of 2048.
+The medium version TSELM-M uses \(d\) = 512 with 8 layers and 8 heads and the large version TSELM-L uses
 \(d\) = 768 with 12 layers and 16 heads. We use AdamW as 
 our optimizer for all the experiments. The learning rate 
-is \(5 \times 10^{-4}\) for TSELM-S and \(5 \times 10^{-5}\) for TSELM-M and TSELM-L. We use 8 16Gb ram GPUs. Our batch size is set to 128. We train the model for 40k steps.
+is \(5 \times 10^{-4}\) for TSELM-S and \(5 \times 10^{-5}\) for TSELM-M and TSELM-L. We train the model using 8 GPUs with 16 GB of RAM each each with batch size 16 for a total of 40,000 steps.
 
@@
 \subsection{Baseline models}
-All models are reflected in Table \ref{main_exp}. 
+Baseline models are reflected in Table \ref{main_exp}. 
 TSELM is compared with Spex+, a discriminative separation model \cite{spex_plus} trained on Libri2Mix \cite{librimix}. Since the discretization might lose some 
 speaker information compared with continuous methods. We compare the speaker 
-similarity of TSELM with the target audio produced by discretizing the clean audio, which is denoted by Target-discrete-WavLM, and it is the upper bound of our model  
-performance. Besides TSELM, we did two experiments 
-denoted by Continuous-WavLM and TSELM-L-Hybrid using the same training data. 
-For Continuous-WavLM, we directly
+similarity of TSELM with the target audio produced by discretizing the clean audio, which is denoted by Target-Discrete, and it is the upper bound of our model  
+performance. Besides TSELM, we did three main experiments 
+denoted by Continuous-WavLM-L6, TSELM-L-Hybrid and TSELM-S-NoConcat using the same training data. 
+For Continuous-WavLM-6, we directly
 passed the embeddings of the 6th hidden layer output of WavLM to the cross attention  
-and LM. Concatenation strategy is stilled applied to the mixed speech. Mean Square Error loss is applied between the output embeddings and the clean 
-embeddings. We use the HiFi-GAN in \cite{knn_vc} to reconstruct the audio. For 
+and LM. Concatenation strategy is stilled applied to the mixed speech. Mean Square Error (MSE) loss is applied between the output embeddings and the clean 
+embeddings. HiFi-GAN in \cite{knn_vc} is used to reconstruct the audio. For 
 TSELM-L-Hybrid, inspired by MaskSR \cite{mask_sr}, we kept discretizing the reference 
@@
 it hybrid instead of fully discretized because the mixture speech has continuous 
-features instead of discrete features.
+features instead of discrete features. For TSELM-S-NoConcat, we utilize the TSELM-S model architecture but without concatenation strategy.
 

### 2024-09-06 src/paper.tex
update

@@
             \hline
+            \hline
             Continuous-WavLM-L6   & G    & Continuous                  & 220M                        & 3.56    & 4.06    & 3.27   & 14.7\%                & 0.877                    \\
@@
 \subsection{Baseline models}
-Baseline models are reflected in Table \ref{main_exp}. 
-TSELM is compared with Spex+, a discriminative separation model \cite{spex_plus} trained on Libri2Mix \cite{librimix}. Since the discretization might lose some 
-speaker information compared with continuous methods. We compare the speaker 
-similarity of TSELM with the target audio produced by discretizing the clean audio, which is denoted by Target-Discrete, and it is the upper bound of our model  
-performance. Besides TSELM, we did three main experiments 
+Baseline models are presented in Table \ref{main_exp}. 
+TSELM is compared with Spex+ \cite{spex_plus}, a discriminative separation model trained on Libri2Mix \cite{librimix}.
+Since discretization can potentially lose speaker information compared to continuous methods.
+We compute the speaker
+similarity of output from TSELM with the target audio produced by discretizing the clean audio, denoted by Target-Discrete, representing the upper bound of our model  
+performance. Besides TSELM, we conduct three main experiments 
 denoted by Continuous-WavLM-L6, TSELM-L-Hybrid and TSELM-S-NoConcat using the same training data. 

### 2024-09-06 src/paper.tex
update

@@
 similarity of output from TSELM with the target audio produced by discretizing the clean audio, denoted by Target-Discrete, representing the upper bound of our model  
-performance. Besides TSELM, we conduct three main experiments 
-denoted by Continuous-WavLM-L6, TSELM-L-Hybrid and TSELM-S-NoConcat using the same training data. 
+performance. Besides TSELM, we conduct three main experiments, named
+ Continuous-WavLM-L6, TSELM-L-Hybrid and TSELM-S-NoConcat using the same training data. 
 For Continuous-WavLM-6, we directly
-passed the embeddings of the 6th hidden layer output of WavLM to the cross attention  
-and LM. Concatenation strategy is stilled applied to the mixed speech. Mean Square Error (MSE) loss is applied between the output embeddings and the clean 
-embeddings. HiFi-GAN in \cite{knn_vc} is used to reconstruct the audio. For 
-TSELM-L-Hybrid, inspired by MaskSR \cite{mask_sr}, we kept discretizing the reference 
-speech while utilizing the continuous embeddings from the reference speech. We call 
-it hybrid instead of fully discretized because the mixture speech has continuous 
-features instead of discrete features. For TSELM-S-NoConcat, we utilize the TSELM-S model architecture but without concatenation strategy.
+pass the embeddings from the 6th hidden layer output of WavLM Large to the cross attention  
+and LM without discretization. 
+The concatenation strategy is stilled applied to the mixed speech. Mean Square Error (MSE) loss is applied between the output embeddings and the clean 
+embeddings. HiFi-GAN in \cite{knn_vc} is used for audio reconstruction. For 
+TSELM-L-Hybrid, inspired by MaskSR \cite{mask_sr}, we discretize the reference 
+speech while utilizing the continuous embeddings from the mixed speech. We call 
+it hybrid because the mixture speech retains continuous features. In TSELM-S-NoConcat, we utilize the TSELM-S model architecture but without concatenation strategy.
 

### 2024-09-06 src/paper.tex
update

@@
 \begin{table*}
-    \caption{The performance of different systems on Libri2Mix testset. For TSELM-L-Hybrid  
-    and TSELM, we compare the speaker similarity with the discretized target speech 
-    (Target-discrete-WavLM) instead of the target speech due to the observation that 
-    the process of discretization already losses the speaker information (0.653 for 
-    Target-discrete-WavLM). We use "\_d" to denote it.  }
+    \caption{The performance of different systems on Libri2Mix testset. "G" means generative while "D" means discriminative. For discrete models,
+    we compute the speaker similarity with the discretized target speech 
+    (Target-discrete-WavLM). We use "\_d" to denote it.  }
     \setlength{\tabcolsep}{12pt} % Adjust column spacing
@@
 TSELM is compared with Spex+ \cite{spex_plus}, a discriminative separation model trained on Libri2Mix \cite{librimix}. 
-Since discretization can potentially lose speaker information compared to continuous methods.
-We compute the speaker
-similarity of output from TSELM with the target audio produced by discretizing the clean audio, denoted by Target-Discrete, representing the upper bound of our model  
-performance. Besides TSELM, we conduct three main experiments, named
+Mixture refers to the unprocessed mixed speech. 
+Target-Discrete refers to the discretized target speech. It serves as the upper bond for our model.  Besides TSELM, we conduct three main experiments, named
  Continuous-WavLM-L6, TSELM-L-Hybrid and TSELM-S-NoConcat using the same training data. 
@@
 \section{Results and Discussions}
-Table \ref{main_exp} shows the performance of different systems on the Libri2Mix test.
-The model size for Target-discrete-WavLM denotes the model size of the encoder and 
-decoder, which is WavLM Large and HiFi-GAN respectively. DNSMOS is calculated over the 
-test sets since it is reference-free. dWER is calculated with the clean speech instead 
-of the discretized speech due to our observations that this does not make much difference. 
-For TSELM-L-Hybrid and TSELM, we compute the speaker similarity with the discretized
-target speech (Target-discrete-WavLM) instead of the target speech.
-% due to the observation that the process of discretization already losses the speaker
-% information (0.653 for Target-discrete-WavLM). 
-We observe that the process of discretization already losses the speaker
-information (0.653 for Target-discrete-WavLM), and it might be related to the inevitable speaker 
-information loss by the process of discretization. Future work should focus on developing better 
-tokenization methods for SSL models. 
-Since work focuses on using the discretized information 
-to do target speaker extraction instead of developing better tokenization methods, we think it is 
-reasonable to compare our outputs with the discretized speech since it serves as an upper bond.
+Table \ref{main_exp} presents the performance of different systems evaluated on the Libri2Mix test.
+The model size for Target-Discrete refers to the total size of the encoder and 
+decoder, which are WavLM Large and scalable HiFi-GAN, respectively. DNSMOS is computed over the 
+testset since this metric is reference-free. dWER is calculated with respect to the clean speech. 
+For continuous methods, speaker similarity is directly computed against the clean speech. 
+However, since discretization inherently results in some loss of speaker information—Target-Discrete shows a speaker similarity score of 0.653 compared to continuous methods—we assess the speaker similarity of the output from the discrete methods against the target audio produced by discretizing the clean speech.
+This target audio output from Target-Discrete serves as the upper bond for our model performance.
+The observed speaker information loss is likely due to the tokenization process, which inherently reduces speaker fidelity.
+Future work should aim to enhance tokenization methods for SSL models to mitigate this loss.
+Since the primary goal of this research is to explore target speaker extraction using discretized information rather than to develop improved tokenization methods, we argue that comparing the outputs of our model with discretized speech is a reasonable approach, as it represents an upper bound on performance.
 
-We observe that our model performs better than Spex+ in terms of the DNSMOS scores but worse in dWER. 
-This suggests that our model has better speech quality compared with discriminative models but 
-worse in speech intelligibility. One possible reason might be related 
-to the discretization process on the mixture 
-speech. Our Kmeans algorithm is trained on clean speech instead of mixed speech. 
-For speech enhancement, this might be 
-good because the level of noise will usually be smaller than the speech. Kmeans might achieve the 
-effect of denoising. Discretization on the mixed
-speech, however, might cause the output to focus on wrong speakers. 
-Our results from TSELM-L-Hybrid 
-support 
-this. For TSELM-L-Hybrid, we use the continuous embeddings from the mixture speech without discretizing, and it has 
-achieved similar dWER with Spex+. Another reason might be related to LM. Right now our encoder-only 
-LM satisfies roughly 50\% accuracy. We think using auto-regressive or masking models will achieve 
-better results.
+We observe that our model outperforms Spex+ in terms of DNSMOS scores, indicating better speech quality, but performs slightly worse in dWER, suggesting lower speech intelligibility.
+One potential reason for this could be the discretization process applied to the mixed speech.
+Our Kmeans algorithm is trained on clean speech rather than mixed speech, which is advantageous for speech enhancement as it likely aids in denoising.
+However, when applied to mixed speech, this discretization might lead to the model focusing on the wrong speaker, as it may only retain dominant speaker information, causing a reduction in intelligibility.
+This hypothesis is supported by the results of TSELM-L-Hybrid, where continuous embeddings from the mixture speech were used without discretization, achieving dWER scores similar to Spex+.
+Another contributing factor could be the limitations of our current language model (LM).
+The encoder-only LM achieves around 50\% accuracy, and we believe using more advanced models, such as auto-regressive or masking-based LMs, could lead to improved performance in future iterations.
 
-We observe significant dWER increasing without concatenating the reference audio to the mixture, 
-as shown 
-the TSELM-S-NoConcat in Table \ref{main_exp}. WavLM \cite{wavlm} is demonstrated to have target speaker 
-separation capability.
-The input audio should have the mixture less than 50\% and have the first utterance as target speaker.
-The output will be a coarse denoised embedding emphasizing the target speaker.
-If the whole input is mixture, we have found that WavLM sometimes will 
-extract the wrong speaker. Inspired by SELM's \cite{selm} success in speech denoising. Our pipeline is trying to transform
-the target speaker separation problem to speech enhancement problem by using WavLM's denoising capability.
+We observe a significant increase in dWER when the mixture audio is not concatenated with the reference, as seen in the TSELM-S-NoConcat results in Table \ref{main_exp}.
+For WavLM to effectively perform target speaker separation, the input audio must follow specific conditions: the mixture should be less than 50\% of the total length, and the first utterance should be the target speaker.
+Under these conditions, WavLM outputs a slightly denoised embedding that emphasizes the target speaker.
+When the entire input is a mixture, however, we found that WavLM sometimes extracts the wrong speaker.
+Our current concatenation strategy is inspired by SELM's \cite{selm} success in speech denoising and aims to transform the target speaker extraction task into a more difficult speech enhancement problem leveraging WavLM's denoising capability.
 
-In Table \ref{hubert_wavlm_6}, we have compared the performance of different SSL models and the selection between one layer or multiple layers to discretize. 
-Our results have shown that the using HuBERT as SSL model has achieved better DNSMOS scores but with worse dWER compared to our WavLM baseline.
-The better DNSMOS scores might be related to the vocoders but it does not reflect the speech intelligibility which is important in speech separation. 
-For dWER, this might be because that HuBERT is trained on clean speech and that it might not capture the rich speech information of mixed speeches. 
-Our results from WavLM-L6 have shown that for speech separation, using multiple layers to discretize is better than using only one layer.
+In Table \ref{hubert_wavlm_6}, we compare the performance of HuBERT and WavLM as SSL model and examine the effects of using either one or multiple layers for discretization.
+Our findings indicate that using HuBERT as the SSL model results in better DNSMOS scores but much worse dWER compared to our WavLM baseline.
+The improved DNSMOS scores likely stem from the vocoder performance, yet they do not adequately reflect speech intelligibility, which is crucial for speech separation tasks.
+The poorer dWER scores observed with HuBERT may be attributed to its training on clean speech, which might not equip it to capture the complexity and richness of mixed speech.
+Moreover, our results from WavLM-L6 suggest that when performing speech separation, discretizing across multiple layers provides better results than relying on a single layer.
 
-Finally, we have observed a performance gap between discrete methods and continuous methods (Continuous-WavLM-L6) on target 
-speaker extraction as shown in Table \ref{main_exp}. For Continuous-WavLM-L6,
-we use the 6th layer embedding output from WavLM from both the mixed speech and reference speech, and use MSE loss between the output from LM and the clean embeddings. This method 
-has the best performance in terms of DNSMOS and dWER. It has a better dWER of 13.6\% compared with TSELM-L. This might be related to the 
-information loss of discretization process. We hope future research will work to bridge this gap.
+Finally, we observed a performance gap between discrete methods and continuous methods, as demonstrated by Continuous-WavLM-L6.
+Continuous-WavLM-L6 has best performance in terms of DNSMOS and dWER among all the experiments.
+It has a better dWER of 13.6\% compared with TSELM-L. The gap in performance may be attributed to the information loss inherent in the discretization process. 
+We hope future research will work to bridge this gap.
 
@@
 In this work, we introduced a novel way using discrete tokens and language models for target speaker extraction.
-We use multiple hidden layers of WavLM and Kmeans tokenizers as encoder, cross attention and language model as our separation model, and a scalable HiFi-GAN to reconstruct the 
-audio. 
+Our method leverages multiple hidden layers of WavLM and Kmeans tokenizers for encoding, employs cross-attention and a language model for separation, and utilizes a scalable HiFi-GAN for audio reconstruction.
 Experiments have 

### 2024-09-06 src/paper.tex
update

@@
 To address these limitations, generative models have been proposed.
-These models aim to learn the underlying distribution of the target speech and generate it, rather than merely mapping mixed speech to clean speech.
+These models aim to learn the underlying distribution of the target speech, rather than mapping mixed speech to clean speech.
 Generative models have been shown to achieve performance comparable to that of discriminative models \cite{target_diff,tokensplit} in blind speech separation and TSE.
@@
 This method converts audio into discrete tokens, allowing LMs to model them, thereby simplifying audio generation tasks by transforming complex regression problems into classification tasks \cite{dasb}.
-Currently, there are two main approaches to audio discretization.
-The first involves the use of neural audio codecs \cite{dac}, which typically capture the acoustic features of the audio \cite{speech_tokenizer}.
-The second approach leverages self-supervised learning (SSL) models, such as HuBERT \cite{hubert} and WavLM \cite{wavlm}.
-SSL models have demonstrated outstanding performance across numerous downstream tasks \cite{superb}, as they extract continuous representations rich in semantic and timbral information from speech.
-As shown in \cite{dasb}, SSL models outperform neural audio codecs in tasks like speech enhancement and separation.
+SSL models such as HuBERT \cite{hubert} and WavLM \cite{wavlm} have demonstrated outstanding performance across numerous downstream tasks \cite{superb}, as they extract continuous representations rich in semantic and timbral information from speech.
+As shown in \cite{dasb}, SSL models outperform neural audio codecs like \cite{dac} in tasks like speech enhancement and separation.
 Consequently, this paper primarily focuses on exploring the discretization of SSL models.
@@
 In the encoding stage, both reference and mixed speech are tokenized using WavLM and Kmeans as the tokenizer.
-Unlike SELM \cite{selm}, which utilizes the 6th layer of WavLM as input to the Kmeans layer, we follow the approach in \cite{dasb} and use outputs from WavLM's hidden layers 1, 3, 7, 12, 18, and 23 as input to six separate Kmeans models, one for each layer.
+Unlike SELM \cite{selm}, which utilizes the 6th layer of WavLM as input to the Kmeans layer, we follow the approach in \cite{dasb} and use outputs from WavLM's hidden layers 1, 3, 7, 12, 18, and 23 as input to 6 separate Kmeans models, one for each layer.
 Our results show that using multiple layers as input is superior to using only the 6th layer.
@@
 Moreover, our results from WavLM-L6 suggest that when performing speech separation, discretizing across multiple layers provides better results than relying on a single layer.
+This might be because that using multiple layer outputs can better tolerate errors compared to using just one layer output.
 
-Finally, we observed a performance gap between discrete methods and continuous methods, as demonstrated by Continuous-WavLM-L6.
-Continuous-WavLM-L6 has best performance in terms of DNSMOS and dWER among all the experiments.
+Finally, we observe a performance gap between discrete methods and continuous methods, as demonstrated by Continuous-WavLM-L6.
+Continuous-WavLM-L6 has the best performance in terms of DNSMOS and dWER among all the experiments, and it only uses the 6 layer output of WavLM. 
 It has a better dWER of 13.6\% compared with TSELM-L. The gap in performance may be attributed to the information loss inherent in the discretization process. 
@@
 
+\section{Acknowledgment}
+We want to thank Super Computing Network (SCNet) for providing the computing resources.
+
 % \section*{Acknowledgment}

### 2024-09-09 src/paper.tex
update

@@
     %   \vspace{-10pt}
+  \end{table*}
+
+  % Please add the following required packages to your document preamble:
+% \usepackage{multirow}
+\begin{table*}[]
+  \setlength{\tabcolsep}{5pt} % Adjust column spacing
+  \begin{center}
+  \begin{tabular}{cccccccccccccccccc}
+  \multirow{3}{*}{System} & \multicolumn{1}{l}{\multirow{3}{*}{Category}} & \multicolumn{1}{l}{\multirow{3}{*}{Type}} & \multicolumn{1}{l}{\multirow{3}{*}{Size}} & \multicolumn{5}{c}{Libri2Mix}                                                  & \multicolumn{5}{c}{WSJO\_2mix}                                                 &  &  &  &  \\
+                          & \multicolumn{1}{l}{}                          & \multicolumn{1}{l}{}                            & \multicolumn{1}{l}{}                            & \multicolumn{3}{c}{DNSMOS $\uparrow$} & dWER $\downarrow$ & Spk Sim $\uparrow$ & \multicolumn{3}{c}{DNSMOS $\uparrow$} & dWER $\downarrow$ & Spk Sim $\uparrow$ &  &  &  &  \\ \cline{5-7}
+                          & \multicolumn{1}{l}{}                          & \multicolumn{1}{l}{}                            & \multicolumn{1}{l}{}                            & SIG         & BAK        & OVL        &                   &                    & SIG         & BAK        & OVL        &                   &                    &  &  &  &  \\ \cline{1-9}
+  Mixture                 & -                                             & -                                               & -                                               & 3.39        & 3.14       & 2.68       & 79.3            & -                  & 3.39        & 3.14       & 2.68       & 79.3            & -                  &  &  &  &  \\
+  Target-Discrete         & G                                             & -                                               & 330M                                            & 3.57        & 4.10       & 3.32       & 11.3            & 0.653              & 3.57        & 4.10       & 3.32       & 11.3            & 0.653              &  &  &  &  \\ \cline{1-9}
+  Spex+                   & D                                             & C                                      & 11M                                             & 3.36        & 3.76       & 2.98       & 19.3            & 0.923              & 3.36        & 3.76       & 2.98       & 19.3            & 0.923              &  &  &  &  \\ \cline{1-9}
+  Continuous-WavLM-L6     & G                                             & C                                      & 220M                                            & 3.56        & 4.06       & 3.27       & 14.7            & 0.877              & 3.56        & 4.06       & 3.27       & 14.7            & 0.877              &  &  &  &  \\
+  TSELM-L-Hybrid          & G                                             & H                                          & 468M                                            & 3.50        & 4.06       & 3.22       & 19.8            & 0.924\_d           & 3.50        & 4.06       & 3.22       & 19.8            & 0.924\_d           &  &  &  &  \\
+  TSELM-S-NoConcat        & G                                             & D                                        & 354M                                            & 3.47        & 4.03       & 3.19       & 69.6            & 0.868\_d           & 3.47        & 4.03       & 3.19       & 69.6            & 0.868\_d           &  &  &  &  \\ \cline{1-9}
+  TSELM-S                 & G                                             & D                                        & 354M                                            & 3.50        & 4.07       & 3.24       & 28.1            & 0.892\_d           & 3.50        & 4.07       & 3.24       & 28.1            & 0.892\_d           &  &  &  &  \\
+  TSELM-M                 & G                                             & D                                        & 389M                                            & 3.49        & 4.05       & 3.22       & 28.4            & 0.901\_d           & 3.49        & 4.05       & 3.22       & 28.4            & 0.901\_d           &  &  &  &  \\
+  TSELM-L                 & G                                             & D                                        & 468M                                            & 3.49        & 4.05       & 3.22       & 27.1            & 0.905\_d           & 3.49        & 4.05       & 3.22       & 27.1            & 0.905\_d           &  &  &  &
+  \end{tabular}
+\end{center}
   \end{table*}

### 2024-09-09 src/paper.tex
update

--- 2024-09-06 src/paper.tex
@@
     %   \vspace{-10pt}
+  \end{table*}
+
+  % Please add the following required packages to your document preamble:
+% \usepackage{multirow}
+\begin{table*}
+  % \setlength{\tabcolsep}{5pt} % Adjust column spacing
+  \renewcommand{\arraystretch}{1.2}
+  \begin{center}
+  \begin{tabular}{cccccccccccccccccc}
+    \Xhline{2\arrayrulewidth} % Bold top line
+  \multirow{3}{*}{System} & \multicolumn{1}{l}{\multirow{3}{*}{Category}} & \multicolumn{1}{l}{\multirow{3}{*}{Type}} &  \multicolumn{5}{c}{Libri2Mix}                                                  & \multicolumn{5}{c}{WSJ0\_2mix}                                                  \\
+                          & \multicolumn{1}{l}{}                                                 & \multicolumn{1}{l}{}                            & \multicolumn{3}{c}{DNSMOS $\uparrow$} & dWER $\downarrow$ & Spk Sim $\uparrow$ & \multicolumn{3}{c}{DNSMOS $\uparrow$} & dWER $\downarrow$ & Spk Sim $\uparrow$  \\ \cline{4-6} \cline{9-11}
+                          & \multicolumn{1}{l}{}                                                    & \multicolumn{1}{l}{}                            & SIG         & BAK        & OVL        &                   &                    & SIG         & BAK        & OVL        &                   &                    \\ \hline
+  Mixture                 & -                                             & -                                                                                           & 3.39        & 3.14       & 2.68       & 79.3            & -                  & 3.39        & 3.14       & 2.68       & 79.3            & -                  \\
+  Target-Discrete         & G                                             & -                                                                                          & 3.57        & 4.10       & 3.32       & 11.3            & 0.653              & 3.57        & 4.10       & 3.32       & 11.3            & 0.653               \\ \hline
+  Spex+                   & D                                             & C                                                                                  & 3.36        & 3.76       & 2.98       & 19.3            & 0.923              & 3.36        & 3.76       & 2.98       & 19.3            & 0.923             \\ \hline
+  Contin-WavLM-L6     & G                                             & C                                                                                  & 3.56        & 4.06       & 3.27       & 14.7            & 0.877              & 3.56        & 4.06       & 3.27       & 14.7            & 0.877             \\
+  TSELM-L-Hybrid          & G                                             & H                                                                                     & 3.50        & 4.06       & 3.22       & 19.8            & 0.924\_d           & 3.50        & 4.06       & 3.22       & 19.8            & 0.924\_d             \\
+  TSELM-S-NoConcat        & G                                             & D                                                                                   & 3.47        & 4.03       & 3.19       & 69.6            & 0.868\_d           & 3.47        & 4.03       & 3.19       & 69.6            & 0.868\_d         \\ \hline
+  TSELM-S                 & G                                             & D                                                                                    & 3.50        & 4.07       & 3.24       & 28.1            & 0.892\_d           & 3.50        & 4.07       & 3.24       & 28.1            & 0.892\_d            \\
+  TSELM-M                 & G                                             & D                                                                                   & 3.49        & 4.05       & 3.22       & 28.4            & 0.901\_d           & 3.49        & 4.05       & 3.22       & 28.4            & 0.901\_d             \\
+  TSELM-L                 & G                                             & D                                                                                  & 3.49        & 4.05       & 3.22       & 27.1            & 0.905\_d           & 3.49        & 4.05       & 3.22       & 27.1            & 0.905\_d        \\
+  \Xhline{2\arrayrulewidth} % Bold top line     
+  \end{tabular}
+\end{center}
   \end{table*}

### 2024-09-09 src/paper.tex
update

--- 2024-09-06 src/paper.tex
@@
     %   \vspace{-10pt}
+  \end{table*}
+
+  % Please add the following required packages to your document preamble:
+% \usepackage{multirow}
+\begin{table*}
+  % \setlength{\tabcolsep}{5pt} % Adjust column spacing
+  \renewcommand{\arraystretch}{1.2}
+  \begin{center}
+  \begin{tabular}{cccccccccccccccccc}
+    \Xhline{2\arrayrulewidth} % Bold top line
+  \multirow{3}{*}{System} & \multicolumn{1}{l}{\multirow{3}{*}{Category}} & \multicolumn{1}{l}{\multirow{3}{*}{Type}} &  \multicolumn{5}{c}{Libri2Mix}                    &                               & \multicolumn{5}{c}{WSJ0\_2mix}                                                  \\
+  \cline{4-8} \cline{10-14}
+                          & \multicolumn{1}{l}{}                                                 & \multicolumn{1}{l}{}                            & \multicolumn{3}{c}{DNSMOS $\uparrow$} & dWER $\downarrow$ & Spk Sim $\uparrow$ &  & \multicolumn{3}{c}{DNSMOS $\uparrow$} & dWER $\downarrow$ & Spk Sim $\uparrow$  \\ \cline{4-6} \cline{10-12}
+                          & \multicolumn{1}{l}{}                                                    & \multicolumn{1}{l}{}                            & SIG         & BAK        & OVL        &                   &        &             & SIG         & BAK        & OVL        &                   &                    \\ \hline
+  Mixture                 & -                                             & -                                                                                           & 3.39        & 3.14       & 2.68       & 79.3            & -        &           & 3.39        & 3.14       & 2.68       & 79.3            & -                  \\
+  Target-Discrete         & G                                             & -                                                                                          & 3.57        & 4.10       & 3.32       & 11.3            & 0.653     &          & 3.57        & 4.10       & 3.32       & 11.3            & 0.653               \\ \hline
+  Spex+                   & D                                             & C                                                                                  & 3.36        & 3.76       & 2.98       & 19.3            & 0.923     &          & 3.36        & 3.76       & 2.98       & 19.3            & 0.923             \\ \hline
+  Contin-WavLM-L6     & G                                             & C                                                                                  & 3.56        & 4.06       & 3.27       & 14.7            & 0.877     &          & 3.56        & 4.06       & 3.27       & 14.7            & 0.877             \\
+  TSELM-L-Hybrid          & G                                             & H                                                                                     & 3.50        & 4.06       & 3.22       & 19.8            & 0.924\_d  &          & 3.50        & 4.06       & 3.22       & 19.8            & 0.924\_d             \\
+  TSELM-S-NoConcat        & G                                             & D                                                                                   & 3.47        & 4.03       & 3.19       & 69.6            & 0.868\_d    &        & 3.47        & 4.03       & 3.19       & 69.6            & 0.868\_d         \\ \hline
+  TSELM-S                 & G                                             & D                                                                                    & 3.50        & 4.07       & 3.24       & 28.1            & 0.892\_d      &      & 3.50        & 4.07       & 3.24       & 28.1            & 0.892\_d            \\
+  TSELM-M                 & G                                             & D                                                                                   & 3.49        & 4.05       & 3.22       & 28.4            & 0.901\_d    &        & 3.49        & 4.05       & 3.22       & 28.4            & 0.901\_d             \\
+  TSELM-L                 & G                                             & D                                                                                  & 3.49        & 4.05       & 3.22       & 27.1            & 0.905\_d    &        & 3.49        & 4.05       & 3.22       & 27.1            & 0.905\_d        \\
+  \Xhline{2\arrayrulewidth} % Bold top line     
+  \end{tabular}
+\end{center}
   \end{table*}

### 2024-09-09 src/paper.tex
update

@@
 
-\begin{table*}
-    \caption{The performance of different systems on Libri2Mix testset. "G" means generative while "D" means discriminative. For discrete models,
-    we compute the speaker similarity with the discretized target speech 
-    (Target-discrete-WavLM). We use "\_d" to denote it.  }
-    \setlength{\tabcolsep}{12pt} % Adjust column spacing
-    \renewcommand{\arraystretch}{1.2}
-    \begin{center}
-        \begin{tabular}{ccccccccc}
-            \Xhline{2\arrayrulewidth} % Bold top line
-            \multirow{2}{*}{System} & \multirow{2}{*}{Category} & \multirow{2}{*}{Model type} & \multirow{2}{*}{Model size} & \multicolumn{3}{c}{ DNSMOS $\uparrow$} & \multirow{2}{*}{dWER $\downarrow$} & \multirow{2}{*}{Spk Sim $\uparrow$} \\
-            \cline{5-7}
-              &                   &                             &                             & SIG     & BAK     & OVL    &                       &                          \\ 
-            \hline
-            Mixture                 & - & -                           & -                           & 3.39    & 3.14    & 2.68   & 79.3\%                & -                        \\
-            Target-Discrete   & G & -                          & 330M                           & 3.57    & 4.10    & 3.32   & 11.3\%                & 0.653                    \\
-            \hline
-            Spex+                   &  D & Continuous                  & 11M                         & 3.36    & 3.76    & 2.98   & 19.3\%                & 0.923                    \\
-            \hline
-            \hline
-            Continuous-WavLM-L6   & G    & Continuous                  & 220M                        & 3.56    & 4.06    & 3.27   & 14.7\%                & 0.877                    \\
-            TSELM-L-Hybrid    & G       & Hybrid                      & 468M                        & 3.50    & 4.06    & 3.22   & 19.8\%                & 0.924\_d                 \\
-            TSELM-S-NoConcat           & G       & Discrete                    & 354M                        & 3.47    & 4.03    & 3.19   & 69.6\%                & 0.868\_d                 \\
-            \hline
-            TSELM-S           & G       & Discrete                    & 354M                        & 3.50    & 4.07    & 3.24   & 28.1\%                & 0.892\_d                 \\
-            TSELM-M          & G        & Discrete                    & 389M                        & 3.49    & 4.05    & 3.22   & 28.4\%                & 0.901\_d                 \\
-            TSELM-L         & G         & Discrete                    & 468M                        & 3.49    & 4.05    & 3.22   & 27.1\%                & 0.905\_d \\
-            \Xhline{2\arrayrulewidth} % Bold top line              
-            \end{tabular}
-            \linebreak
-            \label{main_exp}
-      \end{center}
-    %   \vspace{-10pt}
-  \end{table*}
-
   % Please add the following required packages to your document preamble:
@@
   Target-Discrete         & G                                             & -                                                                                          & 3.57        & 4.10       & 3.32       & 11.3            & 0.653     &          & 3.57        & 4.10       & 3.32       & 11.3            & 0.653               \\ \hline
-  Spex+                   & D                                             & C                                                                                  & 3.36        & 3.76       & 2.98       & 19.3            & 0.923     &          & 3.36        & 3.76       & 2.98       & 19.3            & 0.923             \\ \hline
-  Contin-WavLM-L6     & G                                             & C                                                                                  & 3.56        & 4.06       & 3.27       & 14.7            & 0.877     &          & 3.56        & 4.06       & 3.27       & 14.7            & 0.877             \\
+  Spex+                   & D                                             & -                                                                                  & 3.36        & 3.76       & 2.98       & 19.3            & 0.923     &          & 3.36        & 3.76       & 2.98       & 19.3            & 0.923             \\ \hline
+  Continuous-WavLM-L6     & G                                             & C                                                                                  & 3.56        & 4.06       & 3.27       & 14.7            & 0.877     &          & 3.56        & 4.06       & 3.27       & 14.7            & 0.877             \\
   TSELM-L-Hybrid          & G                                             & H                                                                                     & 3.50        & 4.06       & 3.22       & 19.8            & 0.924\_d  &          & 3.50        & 4.06       & 3.22       & 19.8            & 0.924\_d             \\
-  TSELM-S-NoConcat        & G                                             & D                                                                                   & 3.47        & 4.03       & 3.19       & 69.6            & 0.868\_d    &        & 3.47        & 4.03       & 3.19       & 69.6            & 0.868\_d         \\ \hline
+  TSELM-S-NoCat       & G                                             & D                                                                                   & 3.47        & 4.03       & 3.19       & 69.6            & 0.868\_d    &        & 3.47        & 4.03       & 3.19       & 69.6            & 0.868\_d         \\ \hline
   TSELM-S                 & G                                             & D                                                                                    & 3.50        & 4.07       & 3.24       & 28.1            & 0.892\_d      &      & 3.50        & 4.07       & 3.24       & 28.1            & 0.892\_d            \\

### 2024-09-09 src/paper.tex
update

@@
   % \setlength{\tabcolsep}{5pt} % Adjust column spacing
+  \caption{The performance of different systems on Libri2Mix testset. For TSELM-L-Hybrid  
+  and TSELM, we compare the speaker similarity with the discretized target speech 
+  (Target-discrete-WavLM) instead of the target speech due to the observation that 
+  the process of discretization already losses the speaker information (0.653 for 
+  Target-discrete-WavLM). We use "\_d" to denote it. }
   \renewcommand{\arraystretch}{1.2}
@@
   \begin{table}
-
+    \caption{Performance of different SSL models and layer selections. HuBERT model subsitutes the WavLM Large to HuBERT Large as the SSL model.
+            The WavLM-L6 uses only the 6th layer of hidden output of WavLM Large. WavLM denotes our TSELM model which uses 6 different output layers. 
+            }
+            \vspace{-20.5pt}
     \renewcommand{\arraystretch}{1.1}
@@
             \hline
-            \hline
             \multirow{2}{*}{WavLM}                                     &  Discrete                          & 3.49    & 4.05    & 3.22   & 27.1\%                & 0.905\_d                        \\
@@
             \linebreak
-            \caption{Performance of different SSL models and layer selections. HuBERT model subsitutes the WavLM Large to HuBERT Large as the SSL model.
-            The WavLM-L6 uses only the 6th layer of hidden output of WavLM Large. WavLM denotes our TSELM model which uses 6 different output layers. 
-            }
             \label{hubert_wavlm_6}
       \end{center}
-      \vspace{-32.5pt}
+      \vspace{-18.5pt}
     \end{table}

### 2024-09-09 src/paper.tex
update

@@
 Kunshan, China \\
-bangzeng@whu.edu.cn}
+zeng.bang@dukekunshan.edu.cn}
 % \and
@@
   We propose TSELM, a novel target speaker extraction network that leverages discrete tokens and language models.
-The model utilizes multiple discretized layers from WavLM Large as input tokens and incorporates cross-attention mechanisms to integrate target speaker information.
+TSELM utilizes multiple discretized layers from WavLM Large as input tokens and incorporates cross-attention mechanisms to integrate target speaker information.
 Language models are employed to capture the sequence dependencies, while a scalable HiFi-GAN is used to reconstruct the audio from the tokens.
@@
 To the best of our knowledge, this is the first approach to target speaker extraction using discrete tokens.
-However, a performance gap remains between our method and continuous approaches.
 The code and pretrained models are available at: \href{https://github.com/Beilong-Tang/TSELM}{https://github.com/Beilong-Tang/TSELM}.
@@
     \centering
-    \includegraphics[width=0.9\textwidth]{assets/model.pdf}
+    \includegraphics[width=0.77\textwidth]{assets/model.pdf}
     \caption{Overview of TSELM.}
@@
 % \usepackage{multirow}
-\begin{table*}
-  % \setlength{\tabcolsep}{5pt} % Adjust column spacing
-  \caption{The performance of different systems on Libri2Mix testset. For TSELM-L-Hybrid  
-  and TSELM, we compare the speaker similarity with the discretized target speech 
-  (Target-discrete-WavLM) instead of the target speech due to the observation that 
-  the process of discretization already losses the speaker information (0.653 for 
-  Target-discrete-WavLM). We use "\_d" to denote it. }
-  \renewcommand{\arraystretch}{1.2}
-  \begin{center}
-  \begin{tabular}{cccccccccccccccccc}
-    \Xhline{2\arrayrulewidth} % Bold top line
-  \multirow{3}{*}{System} & \multicolumn{1}{l}{\multirow{3}{*}{Category}} & \multicolumn{1}{l}{\multirow{3}{*}{Type}} &  \multicolumn{5}{c}{Libri2Mix}                    &                               & \multicolumn{5}{c}{WSJ0\_2mix}                                                  \\
-  \cline{4-8} \cline{10-14}
-                          & \multicolumn{1}{l}{}                                                 & \multicolumn{1}{l}{}                            & \multicolumn{3}{c}{DNSMOS $\uparrow$} & dWER $\downarrow$ & Spk Sim $\uparrow$ &  & \multicolumn{3}{c}{DNSMOS $\uparrow$} & dWER $\downarrow$ & Spk Sim $\uparrow$  \\ \cline{4-6} \cline{10-12}
-                          & \multicolumn{1}{l}{}                                                    & \multicolumn{1}{l}{}                            & SIG         & BAK        & OVL        &                   &        &             & SIG         & BAK        & OVL        &                   &                    \\ \hline
-  Mixture                 & -                                             & -                                                                                           & 3.39        & 3.14       & 2.68       & 79.3            & -        &           & 3.39        & 3.14       & 2.68       & 79.3            & -                  \\
-  Target-Discrete         & G                                             & -                                                                                          & 3.57        & 4.10       & 3.32       & 11.3            & 0.653     &          & 3.57        & 4.10       & 3.32       & 11.3            & 0.653               \\ \hline
-  Spex+                   & D                                             & -                                                                                  & 3.36        & 3.76       & 2.98       & 19.3            & 0.923     &          & 3.36        & 3.76       & 2.98       & 19.3            & 0.923             \\ \hline
-  Continuous-WavLM-L6     & G                                             & C                                                                                  & 3.56        & 4.06       & 3.27       & 14.7            & 0.877     &          & 3.56        & 4.06       & 3.27       & 14.7            & 0.877             \\
-  TSELM-L-Hybrid          & G                                             & H                                                                                     & 3.50        & 4.06       & 3.22       & 19.8            & 0.924\_d  &          & 3.50        & 4.06       & 3.22       & 19.8            & 0.924\_d             \\
-  TSELM-S-NoCat       & G                                             & D                                                                                   & 3.47        & 4.03       & 3.19       & 69.6            & 0.868\_d    &        & 3.47        & 4.03       & 3.19       & 69.6            & 0.868\_d         \\ \hline
-  TSELM-S                 & G                                             & D                                                                                    & 3.50        & 4.07       & 3.24       & 28.1            & 0.892\_d      &      & 3.50        & 4.07       & 3.24       & 28.1            & 0.892\_d            \\
-  TSELM-M                 & G                                             & D                                                                                   & 3.49        & 4.05       & 3.22       & 28.4            & 0.901\_d    &        & 3.49        & 4.05       & 3.22       & 28.4            & 0.901\_d             \\
-  TSELM-L                 & G                                             & D                                                                                  & 3.49        & 4.05       & 3.22       & 27.1            & 0.905\_d    &        & 3.49        & 4.05       & 3.22       & 27.1            & 0.905\_d        \\
-  \Xhline{2\arrayrulewidth} % Bold top line     
-  \end{tabular}
-\end{center}
-  \end{table*}
-
-  \begin{table}
-    \caption{Performance of different SSL models and layer selections. HuBERT model subsitutes the WavLM Large to HuBERT Large as the SSL model.
-            The WavLM-L6 uses only the 6th layer of hidden output of WavLM Large. WavLM denotes our TSELM model which uses 6 different output layers. 
-            }
-            \vspace{-20.5pt}
-    \renewcommand{\arraystretch}{1.1}
-    \begin{center}
-        \begin{tabular}{ccccccc}
-            \Xhline{2\arrayrulewidth} % Bold top line
-            \multirow{2}{*}{SSL-Model} & \multirow{2}{*}{Type} & \multicolumn{3}{c}{ DNSMOS $\uparrow$} & \multirow{2}{*}{dWER $\downarrow$} & \multirow{2}{*}{Spk Sim $\uparrow$} \\
-            \cline{3-5}
-                                                       &                             & SIG     & BAK     & OVL    &                       &                          \\ 
-            \hline
-            \multirow{2}{*}{HuBERT}                              &  Discrete                          & 3.56    & 4.09    & 3.30   & 81.3\%                & 0.865\_d                        \\
-                                             &  Hybrid                          & 3.57    & 4.10    & 3.32   & 35.1\%                & 0.907\_d                        \\
-            \hline
-            \multirow{2}{*}{WavLM-L6}                              &  Discrete                          & 2.08    & 2.07    & 1.64   & 122.1\%                & 0.589\_d                        \\
-            &  Hybrid                          & 3.54    & 3.84    & 3.12   & 30.0\%                & 0.849\_d                        \\
-            \hline
-            \multirow{2}{*}{WavLM}                                     &  Discrete                          & 3.49    & 4.05    & 3.22   & 27.1\%                & 0.905\_d                        \\
-                                              &  Hybrid                          & 3.50    & 4.06    & 3.22   & 19.8\%                & 0.924\_d                        \\
-
-            \Xhline{2\arrayrulewidth} % Bold top line              
-            \end{tabular}
-            \linebreak
-            \label{hubert_wavlm_6}
-      \end{center}
-      \vspace{-18.5pt}
-    \end{table}
 
@@
 \subsection{Evaluation}
+
 We use the \texttt{dev} set of Libri2Mix \cite{librimix} to test our model performance and compare it with 
@@
 it hybrid because the mixture speech retains continuous features. In TSELM-S-NoConcat, we utilize the TSELM-S model architecture but without concatenation strategy.
+
+\begin{table*}
+  % \setlength{\tabcolsep}{5pt} % Adjust column spacing
+  \caption{The performance of different systems on Libri2Mix testset. For TSELM-L-Hybrid  
+  and TSELM, we compare the speaker similarity with the discretized target speech 
+  (Target-discrete-WavLM) instead of the target speech due to the observation that 
+  the process of discretization already losses the speaker information (0.653 for 
+  Target-discrete-WavLM). We use "\_d" to denote it. }
+  \renewcommand{\arraystretch}{1.2}
+  \begin{center}
+  \begin{tabular}{cccccccccccccccccc}
+    \Xhline{2\arrayrulewidth} % Bold top line
+  \multirow{3}{*}{System} & \multicolumn{1}{l}{\multirow{3}{*}{Category}} & \multicolumn{1}{l}{\multirow{3}{*}{Type}} &  \multicolumn{5}{c}{Libri2Mix}                    &                               & \multicolumn{5}{c}{WSJ0\_2mix}                                                  \\
+  \cline{4-8} \cline{10-14}
+                          & \multicolumn{1}{l}{}                                                 & \multicolumn{1}{l}{}                            & \multicolumn{3}{c}{DNSMOS $\uparrow$} & dWER $\downarrow$ & Spk Sim $\uparrow$ &  & \multicolumn{3}{c}{DNSMOS $\uparrow$} & dWER $\downarrow$ & Spk Sim $\uparrow$  \\ \cline{4-6} \cline{10-12}
+                          & \multicolumn{1}{l}{}                                                    & \multicolumn{1}{l}{}                            & SIG         & BAK        & OVL        &                   &        &             & SIG         & BAK        & OVL        &                   &                    \\ \hline
+  Mixture                 & -                                             & -                                                                                           & 3.39        & 3.14       & 2.68       & 79.3            & -        &           & 3.39        & 3.14       & 2.68       & 79.3            & -                  \\
+  Target-Discrete         & G                                             & -                                                                                          & 3.57        & 4.10       & 3.32       & 11.3            & 0.653     &          & 3.57        & 4.10       & 3.32       & 11.3            & 0.653               \\ \hline
+  Spex+                   & D                                             & -                                                                                  & 3.36        & 3.76       & 2.98       & 19.3            & 0.923     &          & 3.36        & 3.76       & 2.98       & 19.3            & 0.923             \\ \hline
+  Continuous-WavLM-L6     & G                                             & C                                                                                  & 3.56        & 4.06       & 3.27       & 14.7            & 0.877     &          & 3.56        & 4.06       & 3.27       & 14.7            & 0.877             \\
+  TSELM-L-Hybrid          & G                                             & H                                                                                     & 3.50        & 4.06       & 3.22       & 19.8            & 0.924\_d  &          & 3.50        & 4.06       & 3.22       & 19.8            & 0.924\_d             \\
+  TSELM-S-NoCat       & G                                             & D                                                                                   & 3.47        & 4.03       & 3.19       & 69.6            & 0.868\_d    &        & 3.47        & 4.03       & 3.19       & 69.6            & 0.868\_d         \\ \hline
+  TSELM-S                 & G                                             & D                                                                                    & 3.50        & 4.07       & 3.24       & 28.1            & 0.892\_d      &      & 3.50        & 4.07       & 3.24       & 28.1            & 0.892\_d            \\
+  TSELM-M                 & G                                             & D                                                                                   & 3.49        & 4.05       & 3.22       & 28.4            & 0.901\_d    &        & 3.49        & 4.05       & 3.22       & 28.4            & 0.901\_d             \\
+  TSELM-L                 & G                                             & D                                                                                  & 3.49        & 4.05       & 3.22       & 27.1            & 0.905\_d    &        & 3.49        & 4.05       & 3.22       & 27.1            & 0.905\_d        \\
+  \Xhline{2\arrayrulewidth} % Bold top line     
+  \end{tabular}
+  \label{main_exp}
+\end{center}
+  \end{table*}
+
+  \begin{table}
+    \caption{Performance of different SSL models and layer selections. HuBERT model subsitutes the WavLM Large to HuBERT Large as the SSL model.
+            The WavLM-L6 uses only the 6th layer of hidden output of WavLM Large. WavLM denotes our TSELM model which uses 6 different output layers. 
+            }
+            \vspace{-20.5pt}
+    \renewcommand{\arraystretch}{1.1}
+    \begin{center}
+        \begin{tabular}{ccccccc}
+            \Xhline{2\arrayrulewidth} % Bold top line
+            \multirow{2}{*}{SSL-Model} & \multirow{2}{*}{Type} & \multicolumn{3}{c}{ DNSMOS $\uparrow$} & \multirow{2}{*}{dWER $\downarrow$} & \multirow{2}{*}{Spk Sim $\uparrow$} \\
+            \cline{3-5}
+                                                       &                             & SIG     & BAK     & OVL    &                       &                          \\ 
+            \hline
+            \multirow{2}{*}{HuBERT}                              &  Discrete                          & 3.56    & 4.09    & 3.30   & 81.3\%                & 0.865\_d                        \\
+                                             &  Hybrid                          & 3.57    & 4.10    & 3.32   & 35.1\%                & 0.907\_d                        \\
+            \hline
+            \multirow{2}{*}{WavLM-L6}                              &  Discrete                          & 2.08    & 2.07    & 1.64   & 122.1\%                & 0.589\_d                        \\
+            &  Hybrid                          & 3.54    & 3.84    & 3.12   & 30.0\%                & 0.849\_d                        \\
+            \hline
+            \multirow{2}{*}{WavLM}                                     &  Discrete                          & 3.49    & 4.05    & 3.22   & 27.1\%                & 0.905\_d                        \\
+                                              &  Hybrid                          & 3.50    & 4.06    & 3.22   & 19.8\%                & 0.924\_d                        \\
+
+            \Xhline{2\arrayrulewidth} % Bold top line              
+            \end{tabular}
+            \linebreak
+            \label{hubert_wavlm_6}
+      \end{center}
+      \vspace{-15.5pt}
+    \end{table}
 

### 2024-09-09 src/paper.tex
update

@@
 
-In contrast to blind speech separation, which seeks to isolate individual utterances from a mixture of known speakers, target speaker extraction (TSE) focuses on extracting only the voice of the target speaker using auxiliary information specific to that speaker.
+In contrast to blind speech separation, which seeks to isolate individual utterances from a mixture of known speakers, target speaker extraction (TSE) focuses on extracting only the voice of the target speaker using auxiliary information.
 Current models are predominantly discriminative, employing masking strategies to directly minimize the distance between the estimated and clean speech signals \cite{luo2019conv,spex_plus,sepformer,sef_net}.

### 2024-09-09 src/paper.tex
update

@@
 However, these discriminative approaches often struggle to generalize to unseen data and may introduce undesirable distortions \cite{distortion}.
-To address these limitations, generative models have been proposed.
-These models aim to learn the underlying distribution of the target speech, rather than mapping mixed speech to clean speech.
-Generative models have been shown to achieve performance comparable to that of discriminative models \cite{target_diff,tokensplit} in blind speech separation and TSE.
+To address these limitations, generative models aim to learn the underlying distribution of the target speech, rather than mapping mixed speech to clean speech.
+Recently, generative models have been shown to achieve performance comparable to that of discriminative models in blind speech separation \cite{tokensplit} and TSE \cite{target_diff}.
 
 The discretization of audio has gained significant attention with the advancement of language models (LMs).
-This method converts audio into discrete tokens, allowing LMs to model them, thereby simplifying audio generation tasks by transforming complex regression problems into classification tasks \cite{dasb}.
+This method converts audio into discrete tokens, and leverages LMs to model them, thereby simplifying audio generation tasks by transforming complex regression problems into classification tasks \cite{dasb}.
 SSL models such as HuBERT \cite{hubert} and WavLM \cite{wavlm} have demonstrated outstanding performance across numerous downstream tasks \cite{superb}, as they extract continuous representations rich in semantic and timbral information from speech.
-As shown in \cite{dasb}, SSL models outperform neural audio codecs like \cite{dac} in tasks like speech enhancement and separation.
+As shown in \cite{dasb}, SSL models outperform neural audio codecs \cite{dac} in tasks like speech enhancement and separation.
 Consequently, this paper primarily focuses on exploring the discretization of SSL models.
@@
 
-In the encoding stage, both reference and mixed speech are tokenized using WavLM and Kmeans as the tokenizer.
-Unlike SELM \cite{selm}, which utilizes the 6th layer of WavLM as input to the Kmeans layer, we follow the approach in \cite{dasb} and use outputs from WavLM's hidden layers 1, 3, 7, 12, 18, and 23 as input to 6 separate Kmeans models, one for each layer.
-Our results show that using multiple layers as input is superior to using only the 6th layer.
+In the encoding stage, both reference and mixed speech are tokenized using WavLM and Kmeans.
 The reference speech is passed directly to the encoder, while for mixed speech, we concatenate the reference speech to both sides of the mixture before passing it through the WavLM model.

### 2024-09-09 src/paper.tex
minor_polish_first

@@
 However, for mixed speech, instead of applying the encoding directly, we first concatenate it with the reference speech, creating a signal \(s' = [s_r, s_m, s_r] \in \mathbb{R}^{(T^r + T' + T^r)}\).
-This concatenated signal is then input into the encoder, producing an output tensor \(\bm{d'}\) with shape \(n \times (T_r + T + T_r)\), where \(T\) represents the time dimension for the mixed speech without concatenation.
+This concatenated signal is then input into the encoder, producing an output tensor \(\bm{d'}\) with shape \(n \times (T_r + T + T_r)\), where \(T\) represents the length for the mixed speech embedding.
 The tensor \(\bm{d'}\) contains discrete tokens for the two segments of reference speech and the mixed speech.
-We extract the portion \(\bm{d}\) corresponding only to the mixed speech, resulting in an output tensor of shape \(n \times T\).
-This approach is inspired by the training schema of WavLM \cite{wavlm}, which trains the model by overlapping clean speech with an interfering signal that covers less than 50\% of the clean speech's duration, using the first utterance as the primary speaker.
-This allows WavLM to identify and focus on the main speaker when producing embeddings.
+We extract the portion \(\bm{d}\) corresponding to the mixed speech, resulting in an output tensor of shape \(n \times T\).
+
+This approach is inspired by WavLM \cite{wavlm}, which trains the model by overlapping clean speech with an interfering signal covering less than 50\% of the speech, using the first utterance as the primary speaker.
+This allows WavLM to focus on producing target speaker dependent embeddings.
 Our experiments demonstrated that this concatenation strategy significantly enhances the model's performance by guiding it to prioritize the target speaker's information.
@@
 
-We use the \texttt{dev} set of Libri2Mix \cite{librimix} to test our model performance and compare it with 
+We use the \texttt{test} set of Libri2Mix \cite{librimix} to test our model performance and compare it with 
 other baseline models.

### 2024-09-09 src/paper.tex
update

@@
 
-The discretization of audio has gained significant attention with the advancement of language models (LMs).
+The discretization of audio has gained significant attention with the advancement of language models (LMs). It has been explored in
+tasks such as speech enhancement \cite{selm} and blind speech separation \cite{dasb,tokensplit}.
 This method converts audio into discrete tokens, and leverages LMs to model them, thereby simplifying audio generation tasks by transforming complex regression problems into classification tasks \cite{dasb}.
-SSL models such as HuBERT \cite{hubert} and WavLM \cite{wavlm} have demonstrated outstanding performance across numerous downstream tasks \cite{superb}, as they extract continuous representations rich in semantic and timbral information from speech.
+SSL models such as HuBERT \cite{hubert} and WavLM \cite{wavlm} have demonstrated outstanding performances across numerous downstream tasks \cite{superb}, as they extract continuous representations rich in semantic and timbral information from speech.
 As shown in \cite{dasb}, SSL models outperform neural audio codecs \cite{dac} in tasks like speech enhancement and separation.
@@
 
-Discretization methods have been explored for tasks such as speech enhancement \cite{selm} and blind speech separation \cite{dasb,tokensplit}, but their application to target speaker extraction (TSE) has been limited.
-In this paper, we present a novel approach to target speaker extraction using discrete tokens and language models, named \textbf{TSELM}.
-Inspired by the blind speech separation networks proposed in DASB \cite{dasb}, our model is structured into three stages: encoding, modeling, and decoding.
+The discretization approach for Target Speech Extraction (TSE) has received limited attention in the literature.
+One of the earliest works to introduce discrete tokens in the context of TSE is presented by \cite{gen_tse}, which investigates the use of self-supervised learning (SSL) models such as HuBERT and vq-wav2vec \cite{}.
+However, this study does not explore the WavLM SSL model, which has shown superior performance in speech separation tasks.
+Additionally, it primarily utilizes the output from a single layer of the SSL model for discretization.
+Furthermore, the evaluation in \cite{gen_tse} focuses solely on speech quality, neglecting key metrics such as speech intelligibility and speaker similarity, both of which are critical for the TSE task.
+To address these limitations, we propose TSELM, a novel approach that leverages multiple hidden layers of WavLM for discretization and incorporates evaluation metrics for speech intelligibility and speaker similarity.
 
+TSELM has three stages: encoding, modeling and decoding.
 In the encoding stage, both reference and mixed speech are tokenized using WavLM and Kmeans.

### 2024-09-09 src/paper.tex
update

@@
 The discretization approach for Target Speech Extraction (TSE) has received limited attention in the literature.
-One of the earliest works to introduce discrete tokens in the context of TSE is presented by \cite{gen_tse}, which investigates the use of self-supervised learning (SSL) models such as HuBERT and vq-wav2vec \cite{}.
-However, this study does not explore the WavLM SSL model, which has shown superior performance in speech separation tasks.
+One of the earliest works to introduce discrete tokens in the context of TSE is presented by \cite{gen_tse}, which investigates the use of self-supervised learning (SSL) models such as HuBERT and vq-wav2vec \cite{vq_wav2vec}.
+However, this study does not explore the WavLM SSL model, which has shown superior performance in speech separation tasks \cite{wavlm}.
 Additionally, it primarily utilizes the output from a single layer of the SSL model for discretization.
@@
 vocoders due to the fact that the vocoder output does not focus strictly on frame alignment
-\cite{tokensplit,selm}. We used DNSMOS \cite{dnsmos} to measure the speech quality, and differential 
+\cite{tokensplit,selm}. We use DNSMOS \cite{dnsmos} to measure the speech quality, and differential 
 word error 
@@
 Target-Discrete refers to the discretized target speech. It serves as the upper bond for our model.  Besides TSELM, we conduct three main experiments, named
- Continuous-WavLM-L6, TSELM-L-Hybrid and TSELM-S-NoConcat using the same training data. 
+ Continuous-WavLM-L6, TSELM-L-Hybrid and TSELM-S-NoCat using the same training data. 
 For Continuous-WavLM-6, we directly
@@
 speech while utilizing the continuous embeddings from the mixed speech. We call 
-it hybrid because the mixture speech retains continuous features. In TSELM-S-NoConcat, we utilize the TSELM-S model architecture but without concatenation strategy.
+it hybrid because the mixture speech retains continuous features. In TSELM-S-NoCat, we utilize the TSELM-S model architecture but without concatenation strategy.
 
@@
 
-We observe a significant increase in dWER when the mixture audio is not concatenated with the reference, as seen in the TSELM-S-NoConcat results in Table \ref{main_exp}.
+We observe a significant increase in dWER when the mixture audio is not concatenated with the reference, as seen in the TSELM-S-NoCat results in Table \ref{main_exp}.
 For WavLM to effectively perform target speaker separation, the input audio must follow specific conditions: the mixture should be less than 50\% of the total length, and the first utterance should be the target speaker.

### 2024-09-09 src/paper.tex
update

@@
 SSL models such as HuBERT \cite{hubert} and WavLM \cite{wavlm} have demonstrated outstanding performances across numerous downstream tasks \cite{superb}, as they extract continuous representations rich in semantic and timbral information from speech.
-As shown in \cite{dasb}, SSL models outperform neural audio codecs \cite{dac} in tasks like speech enhancement and separation.
-Consequently, this paper primarily focuses on exploring the discretization of SSL models.
 
-The discretization approach for Target Speech Extraction (TSE) has received limited attention in the literature.
-One of the earliest works to introduce discrete tokens in the context of TSE is presented by \cite{gen_tse}, which investigates the use of self-supervised learning (SSL) models such as HuBERT and vq-wav2vec \cite{vq_wav2vec}.
-However, this study does not explore the WavLM SSL model, which has shown superior performance in speech separation tasks \cite{wavlm}.
-Additionally, it primarily utilizes the output from a single layer of the SSL model for discretization.
-Furthermore, the evaluation in \cite{gen_tse} focuses solely on speech quality, neglecting key metrics such as speech intelligibility and speaker similarity, both of which are critical for the TSE task.
-To address these limitations, we propose TSELM, a novel approach that leverages multiple hidden layers of WavLM for discretization and incorporates evaluation metrics for speech intelligibility and speaker similarity.
+Discretization in Target Speech Extraction (TSE) has seen limited study.
+\cite{gen_tse} is among the first to use discrete tokens in TSE, leveraging SSL models like HuBERT and vq-wav2vec \cite{vq_wav2vec}.
+However, it overlooks the WavLM model, which excels in speech separation, and focuses on single-layer outputs for discretization.
+Moreover, its evaluation is limited to speech quality, neglecting intelligibility and speaker similarity, both crucial for TSE.
+We address these gaps by proposing TSELM, which uses multiple WavLM layers for discretization and adds metrics for intelligibility and speaker similarity.
 
@@
 TSELM is compared with Spex+ \cite{spex_plus}, a discriminative separation model trained on Libri2Mix \cite{librimix}. 
+We also compare our model with UniCATS(vq-wav2vec) from \cite{gen_tse}, which uses discrete tokens from wav2vec to conduct TSE. 
 Mixture refers to the unprocessed mixed speech. 
-Target-Discrete refers to the discretized target speech. It serves as the upper bond for our model.  Besides TSELM, we conduct three main experiments, named
+Target-Discrete refers to the discretized target speech. 
+It serves as the upper bond for our model.  Besides TSELM, we conduct three main experiments, named
  Continuous-WavLM-L6, TSELM-L-Hybrid and TSELM-S-NoCat using the same training data. 
@@
   % \setlength{\tabcolsep}{5pt} % Adjust column spacing
-  \caption{The performance of different systems on Libri2Mix testset. For TSELM-L-Hybrid  
+  \caption{Results on Libri2Mix testset and wsj0\_2mix\_extra testset. For TSELM-L-Hybrid  
   and TSELM, we compare the speaker similarity with the discretized target speech 
@@
                           & \multicolumn{1}{l}{}                                                    & \multicolumn{1}{l}{}                            & SIG         & BAK        & OVL        &                   &        &             & SIG         & BAK        & OVL        &                   &                    \\ \hline
-  Mixture                 & -                                             & -                                                                                           & 3.39        & 3.14       & 2.68       & 79.3            & -        &           & 3.39        & 3.14       & 2.68       & 79.3            & -                  \\
-  Target-Discrete         & G                                             & -                                                                                          & 3.57        & 4.10       & 3.32       & 11.3            & 0.653     &          & 3.57        & 4.10       & 3.32       & 11.3            & 0.653               \\ \hline
-  Spex+                   & D                                             & -                                                                                  & 3.36        & 3.76       & 2.98       & 19.3            & 0.923     &          & 3.36        & 3.76       & 2.98       & 19.3            & 0.923             \\ \hline
-  Continuous-WavLM-L6     & G                                             & C                                                                                  & 3.56        & 4.06       & 3.27       & 14.7            & 0.877     &          & 3.56        & 4.06       & 3.27       & 14.7            & 0.877             \\
-  TSELM-L-Hybrid          & G                                             & H                                                                                     & 3.50        & 4.06       & 3.22       & 19.8            & 0.924\_d  &          & 3.50        & 4.06       & 3.22       & 19.8            & 0.924\_d             \\
-  TSELM-S-NoCat       & G                                             & D                                                                                   & 3.47        & 4.03       & 3.19       & 69.6            & 0.868\_d    &        & 3.47        & 4.03       & 3.19       & 69.6            & 0.868\_d         \\ \hline
-  TSELM-S                 & G                                             & D                                                                                    & 3.50        & 4.07       & 3.24       & 28.1            & 0.892\_d      &      & 3.50        & 4.07       & 3.24       & 28.1            & 0.892\_d            \\
-  TSELM-M                 & G                                             & D                                                                                   & 3.49        & 4.05       & 3.22       & 28.4            & 0.901\_d    &        & 3.49        & 4.05       & 3.22       & 28.4            & 0.901\_d             \\
-  TSELM-L                 & G                                             & D                                                                                  & 3.49        & 4.05       & 3.22       & 27.1            & 0.905\_d    &        & 3.49        & 4.05       & 3.22       & 27.1            & 0.905\_d        \\
+  Mixture                 & -                                             & -                                                                                           & 3.39        & 3.14       & 2.68       & 79.3            & -        &           & 3.42        & 3.28       & 2.81       & 63.6            & -                  \\
+  Target-Discrete         & G                                             & -                                                                                          & 3.57        & 4.10       & 3.32       & 11.3            & 0.653     &          & 3.56        & 4.09       & 3.30       & 10.1            & 0.657               \\ \hline
+  Spex+                   & D                                             & -                                                                                  & 3.36        & 3.76       & 2.98       & 19.3            & 0.923     &          & 3.49        & 4.00       & 3.21       & 15.0            & 0.943             \\
+  SkiM-UniCATS                   & G                                             & D                                                                                  & -        & -      & -       & -            & -     &          & 3.62        & 4.10       & 3.37       & -            & -             \\ \hline
+  Continuous-WavLM-L6     & G                                             & C                                                                                  & 3.56        & 4.06       & 3.27       & 14.7            & 0.877     &          & 3.61        & 4.08       & 3.35       & 8.0            & 0.892             \\
+  TSELM-L-Hybrid          & G                                             & H                                                                                     & 3.50        & 4.06       & 3.22       & 19.8            & 0.924\_d  &          & 3.57        & 4.10       & 3.31       & 12.6            & 0.915\_d             \\
+  TSELM-S-NoCat       & G                                             & D                                                                                   & 3.47        & 4.03       & 3.19       & 69.6            & 0.868\_d    &        & 3.55        & 4.08       & 3.28       & 64.5            & 0.888\_d         \\ \hline
+  TSELM-S                 & G                                             & D                                                                                    & 3.50        & 4.07       & 3.24       & 28.1            & 0.892\_d      &      & 3.57        & 4.10       & 3.32       & 19.4            & 0.915\_d            \\
+  TSELM-M                 & G                                             & D                                                                                   & 3.49        & 4.05       & 3.22       & 28.4            & 0.901\_d    &        & 3.57        & 4.10       & 3.32       & 18.8            & 0.921\_d             \\
+  TSELM-L                 & G                                             & D                                                                                  & 3.49        & 4.05       & 3.22       & 27.1            & 0.905\_d    &        & 3.57        & 4.10       & 3.31       & 17.8            & 0.924\_d        \\
   \Xhline{2\arrayrulewidth} % Bold top line     
@@
 \section{Results and Discussions}
-Table \ref{main_exp} presents the performance of different systems evaluated on the Libri2Mix test.
-The model size for Target-Discrete refers to the total size of the encoder and 
-decoder, which are WavLM Large and scalable HiFi-GAN, respectively. DNSMOS is computed over the 
-testset since this metric is reference-free. dWER is calculated with respect to the clean speech. 
+Table \ref{main_exp} presents the performance of different systems evaluated on the Libri2Mix test and wsj0\_2mix\_extra testset. 
+DNSMOS is computed over the 
+output since this metric is reference-free. dWER is calculated with respect to the clean speech. 
 For continuous methods, speaker similarity is directly computed against the clean speech. 
@@
 Our current concatenation strategy is inspired by SELM's \cite{selm} success in speech denoising and aims to transform the target speaker extraction task into a more difficult speech enhancement problem leveraging WavLM's denoising capability.
+However, this is a suboptimal solution and we think future work should focus on developing a speaker-aware tokenization method.
 

### 2024-09-09 src/paper.tex
update

@@
 The improved DNSMOS scores likely stem from the vocoder performance, yet they do not adequately reflect speech intelligibility, which is crucial for speech separation tasks.
+SkIM-UniCATS uses only DNSMOS as evaluation, which might not be enough
+in terms of speech intelligibility and speaker similarity.
 The poorer dWER scores observed with HuBERT may be attributed to its training on clean speech, which might not equip it to capture the complexity and richness of mixed speech.
@@
 \section{Conclusion}
-In this work, we introduced a novel way using discrete tokens and language models for target speaker extraction.
+In this work, we introduce a novel way using discrete tokens and language models for target speaker extraction.
 Our method leverages multiple hidden layers of WavLM and Kmeans tokenizers for encoding, employs cross-attention and a language model for separation, and utilizes a scalable HiFi-GAN for audio reconstruction.
@@
 \section{Acknowledgment}
-We want to thank Super Computing Network (SCNet) for providing the computing resources.
+We woudld like to thank Super Computing Network (SCNet) for providing the computing resources.
 

### 2024-09-09 src/paper.tex
update

@@
 By applying a cross-entropy loss, TSELM models the probability distribution of output tokens, thus converting the complex regression problem of audio generation into a classification task.
-To the best of our knowledge, this is the first approach to target speaker extraction using discrete tokens.
 The code and pretrained models are available at: \href{https://github.com/Beilong-Tang/TSELM}{https://github.com/Beilong-Tang/TSELM}.
@@
 
-The discretization of audio has gained significant attention with the advancement of language models (LMs). It has been explored in
+The discretization of audio has gained significant attention with the advancement of language models (LMs) \cite{l1, l2, l3, l4, l5}. It has been explored in
 tasks such as speech enhancement \cite{selm} and blind speech separation \cite{dasb,tokensplit}.
 This method converts audio into discrete tokens, and leverages LMs to model them, thereby simplifying audio generation tasks by transforming complex regression problems into classification tasks \cite{dasb}.
-SSL models such as HuBERT \cite{hubert} and WavLM \cite{wavlm} have demonstrated outstanding performances across numerous downstream tasks \cite{superb}, as they extract continuous representations rich in semantic and timbral information from speech.
+Self-Supervised Learning (SSL) models such as HuBERT \cite{hubert} and WavLM \cite{wavlm} have demonstrated outstanding performances across numerous downstream tasks \cite{superb}, as they extract continuous representations rich in semantic and timbral information from speech.
 
@@
 \cite{gen_tse} is among the first to use discrete tokens in TSE, leveraging SSL models like HuBERT and vq-wav2vec \cite{vq_wav2vec}.
-However, it overlooks the WavLM model, which excels in speech separation, and focuses on single-layer outputs for discretization.
+However, it overlooks the WavLM model, which excels in speech separation.
+Also, it mostly focuses on single-layer outputs for discretization.
 Moreover, its evaluation is limited to speech quality, neglecting intelligibility and speaker similarity, both crucial for TSE.
@@
 Continuous-WavLM-L6 has the best performance in terms of DNSMOS and dWER among all the experiments, and it only uses the 6 layer output of WavLM. 
-It has a better dWER of 13.6\% compared with TSELM-L. The gap in performance may be attributed to the information loss inherent in the discretization process. 
+The gap in performance may be attributed to the information loss inherent in the discretization process. 
 We hope future research will work to bridge this gap.

### 2024-09-09 src/paper.tex
update

@@
 Discretization in Target Speech Extraction (TSE) has seen limited study.
-\cite{gen_tse} is among the first to use discrete tokens in TSE, leveraging SSL models like HuBERT and vq-wav2vec \cite{vq_wav2vec}.
+SkiM-UniCATS \cite{gen_tse} is among the first to use discrete tokens in TSE, leveraging SSL models like HuBERT and vq-wav2vec \cite{vq_wav2vec}.
 However, it overlooks the WavLM model, which excels in speech separation.
-Also, it mostly focuses on single-layer outputs for discretization.
+Also, it mainly focuses on single-layer outputs for discretization.
 Moreover, its evaluation is limited to speech quality, neglecting intelligibility and speaker similarity, both crucial for TSE.
@@
 Extensive experiments demonstrate that our method achieves excellent speech quality and comparable intelligibility results.
-To the best of our knowledge, this is the first study to explore target speaker extraction using discrete tokens.
 Our demos are available at \href{https://beilong-tang.github.io/TSELM.demo/}{https://beilong-tang.github.io/TSELM.demo/}.
@@
 
-We use the \texttt{test} set of Libri2Mix \cite{librimix} to test our model performance and compare it with 
-other baseline models.
+We evaluate our models using Libri2Mix\cite{librimix} and WSJ0-2mix \cite{wsj0}.
+We follow the recipes\footnote{\href{https://github.com/xuchenglin28/speaker_extraction}{https://github.com/xuchenglin28/speaker\_extraction}} to from the reference speeches for 
+WSJ0-2mix.
+We use the clean testset of Libri2Mix\footnote{\href{https://github.com/JorisCos/LibriMix}{https://github.com/JorisCos/LibriMix}}, and the reference speeches are randomly selected.
 
@@
 TSELM is compared with Spex+ \cite{spex_plus}, a discriminative separation model trained on Libri2Mix \cite{librimix}. 
-We also compare our model with UniCATS(vq-wav2vec) from \cite{gen_tse}, which uses discrete tokens from wav2vec to conduct TSE. 
+We also compare our model with SkiM-UniCATS(vq-wav2vec) from \cite{gen_tse}, which uses discrete tokens from vq-wav2vec to conduct TSE. 
 Mixture refers to the unprocessed mixed speech. 
-Target-Discrete refers to the discretized target speech. 
-It serves as the upper bond for our model.  Besides TSELM, we conduct three main experiments, named
+Target-Discrete refers to the discretized target speech using our encoder and decoder. 
+It serves as the upper bond for our model performance.  Besides TSELM, we conduct three main experiments, named
  Continuous-WavLM-L6, TSELM-L-Hybrid and TSELM-S-NoCat using the same training data. 
@@
 and LM without discretization. 
-The concatenation strategy is stilled applied to the mixed speech. Mean Square Error (MSE) loss is applied between the output embeddings and the clean 
+The concatenation strategy is still applied to the mixed speech. Mean Square Error (MSE) loss is applied between the output embeddings and the clean 
 embeddings. HiFi-GAN in \cite{knn_vc} is used for audio reconstruction. For 
@@
 speech while utilizing the continuous embeddings from the mixed speech. We call 
-it hybrid because the mixture speech retains continuous features. In TSELM-S-NoCat, we utilize the TSELM-S model architecture but without concatenation strategy.
+it hybrid because the mixture speech retains continuous features. In TSELM-S-NoCat, we utilize the TSELM-S model architecture but abandon concatenation strategy.
 
@@
   % \setlength{\tabcolsep}{5pt} % Adjust column spacing
-  \caption{Results on Libri2Mix testset and wsj0\_2mix\_extra testset. For TSELM-L-Hybrid  
-  and TSELM, we compare the speaker similarity with the discretized target speech 
-  (Target-discrete-WavLM) instead of the target speech due to the observation that 
-  the process of discretization already losses the speaker information (0.653 for 
-  Target-discrete-WavLM). We use "\_d" to denote it. }
+  \caption{Results on Libri2Mix (clean) and WSJ0-2mix: In the "Category" column, "G" refers to generative models, while "D" refers to discriminative models.
+The "Type" column categorizes methods as "D" (discrete), "H" (hybrid), or "C" (continuous).
+  For discrete methods, speaker similarity is compared against the discretized target speech (denoted as Target-discrete-WavLM) instead of the original target speech. It is denoted as "\_d".}
   \renewcommand{\arraystretch}{1.2}
@@
     \Xhline{2\arrayrulewidth} % Bold top line
-  \multirow{3}{*}{System} & \multicolumn{1}{l}{\multirow{3}{*}{Category}} & \multicolumn{1}{l}{\multirow{3}{*}{Type}} &  \multicolumn{5}{c}{Libri2Mix}                    &                               & \multicolumn{5}{c}{WSJ0\_2mix}                                                  \\
+  \multirow{3}{*}{System} & \multicolumn{1}{l}{\multirow{3}{*}{Category}} & \multicolumn{1}{l}{\multirow{3}{*}{Type}} &  \multicolumn{5}{c}{Libri2Mix Clean}                    &                               & \multicolumn{5}{c}{WSJ0\_2mix}                                                  \\
   \cline{4-8} \cline{10-14}
@@
 \section{Results and Discussions}
-Table \ref{main_exp} presents the performance of different systems evaluated on the Libri2Mix test and wsj0\_2mix\_extra testset. 
+Table \ref{main_exp} presents the performance of different systems evaluated on the Libri2Mix test and WSJ0-2mix testset. 
 DNSMOS is computed over the 
@@
 For continuous methods, speaker similarity is directly computed against the clean speech. 
-However, since discretization inherently results in some loss of speaker information—Target-Discrete shows a speaker similarity score of 0.653 compared to continuous methods—we assess the speaker similarity of the output from the discrete methods against the target audio produced by discretizing the clean speech.
+However, since discretization inherently results in some loss of speaker information—Target-Discrete shows a speaker similarity score of 0.653 for Libri2Mix compared to continuous methods—we assess the speaker similarity of the output from the discrete methods against the target audio produced by discretizing the clean speech.
 This target audio output from Target-Discrete serves as the upper bond for our model performance.
@@
 When the entire input is a mixture, however, we found that WavLM sometimes extracts the wrong speaker.
-Our current concatenation strategy is inspired by SELM's \cite{selm} success in speech denoising and aims to transform the target speaker extraction task into a more difficult speech enhancement problem leveraging WavLM's denoising capability.
-However, this is a suboptimal solution and we think future work should focus on developing a speaker-aware tokenization method.
+Our current concatenation strategy, inspired by SELM's \cite{selm} success in speech denoising, reframes the target speaker extraction task as a more challenging speech enhancement problem, utilizing WavLM's denoising capabilities.
+However, this approach remains suboptimal, and we believe future work should prioritize developing a speaker-aware tokenization method.
 
@@
 The improved DNSMOS scores likely stem from the vocoder performance, yet they do not adequately reflect speech intelligibility, which is crucial for speech separation tasks.
-SkIM-UniCATS uses only DNSMOS as evaluation, which might not be enough
-in terms of speech intelligibility and speaker similarity.
 The poorer dWER scores observed with HuBERT may be attributed to its training on clean speech, which might not equip it to capture the complexity and richness of mixed speech.
@@
 This might be because that using multiple layer outputs can better tolerate errors compared to using just one layer output.
+Although SkiM-UniCATS \cite{gen_tse} achieves satisfying DNSMOS scores, it does not ensure high speaker similarity, as indicated in Table \ref{main_exp}.
+Additionally, results in Table \ref{hubert_wavlm_6} show that it also does not guarantee superior speech intelligibility.
 
@@
 shown that our model can achieve excellent performance in terms of speech quality, and comparable performance in terms of speech intelligibility and 
-speaker similarity. However, we still have a gap between continuous methods especially in speech intelligibility and speaker similarity. Future research should focus on shrinking 
-this gap.
-
-\section{Acknowledgment}
-We woudld like to thank Super Computing Network (SCNet) for providing the computing resources.
+speaker similarity. However, our models rely on WavLM's denoising property, and future work should focus on developing speaker-aware tokenization method.
 

### 2024-09-09 src/paper.tex
update

@@
 Experiments have 
-shown that our model can achieve excellent performance in terms of speech quality, and comparable performance in terms of speech intelligibility and 
-speaker similarity. However, our models rely on WavLM's denoising property, and future work should focus on developing speaker-aware tokenization method.
+shown that our model can achieve excellent performance in terms of speech quality, and comparable performance in terms of speech intelligibility.
+However, our model relies on WavLM's denoising property, and future work should focus on developing speaker-aware tokenization method.
 

### 2024-09-09 src/paper.tex
update

--- 2024-09-09 src/paper.tex
@@
 shown that our model can achieve excellent performance in terms of speech quality, and comparable performance in terms of speech intelligibility and 
-speaker similarity. However, our models rely on WavLM's denoising property, and future work should focus on developing speaker-aware tokenization method.
+speaker similarity. However, we observe a gap between discrete methods and continuous methods especially in speech intelligibility and speaker similarity. Future research should focus on shrinking 
+this gap.
 

### 2024-09-11 src/paper.tex
update

--- 2024-09-09 src/paper.tex
@@
 
-\title{TSELM: Target speaker extraction using discrete tokens and language models
+\title{TSELM: Target Speaker Extraction using Discrete Tokens and Language Models
 }
@@
   We propose TSELM, a novel target speaker extraction network that leverages discrete tokens and language models.
-TSELM utilizes multiple discretized layers from WavLM Large as input tokens and incorporates cross-attention mechanisms to integrate target speaker information.
+TSELM utilizes multiple discretized layers from WavLM as input tokens and incorporates cross-attention mechanisms to integrate target speaker information.
 Language models are employed to capture the sequence dependencies, while a scalable HiFi-GAN is used to reconstruct the audio from the tokens.
 By applying a cross-entropy loss, TSELM models the probability distribution of output tokens, thus converting the complex regression problem of audio generation into a classification task.
-The code and pretrained models are available at: \href{https://github.com/Beilong-Tang/TSELM}{https://github.com/Beilong-Tang/TSELM}.
+  Experimental results show that TSELM achieves excellent results in speech 
+  quality and comparable results in speech intelligibility. 
 \end{abstract}
@@
 
-In contrast to blind speech separation, which seeks to isolate individual utterances from a mixture of known speakers, target speaker extraction (TSE) focuses on extracting only the voice of the target speaker using auxiliary information.
+In contrast to blind speech separation, which seeks to isolate individual utterances from a mixture of known speakers, Target Speaker Extraction (TSE) focuses on extracting only the voice of the target speaker using auxiliary information.
 Current models are predominantly discriminative, employing masking strategies to directly minimize the distance between the estimated and clean speech signals \cite{luo2019conv,spex_plus,sepformer,sef_net}.
@@
 
-Discretization in Target Speech Extraction (TSE) has seen limited study.
+There are only few works about discretization in Target Speech Extraction (TSE).
 SkiM-UniCATS \cite{gen_tse} is among the first to use discrete tokens in TSE, leveraging SSL models like HuBERT and vq-wav2vec \cite{vq_wav2vec}.
@@
 Moreover, its evaluation is limited to speech quality, neglecting intelligibility and speaker similarity, both crucial for TSE.
-We address these gaps by proposing TSELM, which uses multiple WavLM layers for discretization and adds metrics for intelligibility and speaker similarity.
+We try to address these potential issues by proposing TSELM, which uses multiple WavLM layers for discretization and adds metrics for intelligibility and speaker similarity.
+Our demos are available at
+\footnote{\href{https://beilong-tang.github.io/TSELM.demo/}{https://beilong-tang.github.io/TSELM.demo/}}.
 
+\section{Method}
 TSELM has three stages: encoding, modeling and decoding.
@@
 Extensive experiments demonstrate that our method achieves excellent speech quality and comparable intelligibility results.
-Our demos are available at \href{https://beilong-tang.github.io/TSELM.demo/}{https://beilong-tang.github.io/TSELM.demo/}.
-
-\section{Method}
-% Our model consists of three stages: encoding, modeling, and decoding. The encoder and decoder are 
-% pretrained models and they are freezed during training. For the encoding stage, we use hidden layers 1, 3, 7, 12, 18, and 23 (denoted as \(n_l\)) of WavLM-Large 
-% and publicly available Kmeans 
-% models in \cite{dasb} to produce the discretized tokens. We use a concatenation 
-% strategy to encode the mixture speech. For decoders, we use the scalable HiFi-GAN available in 
-% \cite{dasb} to reconstruct the audio from discretized tokens. Our main focus is on the
-% modeling stage. We apply an attention embedding mechanism to embed discrete tokens from different 
-% layers into one single embedding. Encoder-only LM and linear classifier is applied afterwards to optimize the likelihood of probability 
-% distribution of the clean tokens.
 
@@
 Specifically, we extract the outputs from six hidden layers: 1, 3, 7, 12, 18, and 23.
-Given a speech signal \(s \in \mathbb{R}^{T'}\), the output of WavLM is a tensor \(\bm{r}\) with shape \(n \times T \times E\), where \(n\) is the number of output layers (6 in this case), \(T\) is the time dimension, and \(E\) represents the embedding dimension, which is 1024 in WavLM Large.
-For tokenization, we apply separate Kmeans models to each output layer, with each model using the same number of clusters, denoted by \(K\).
+Given a speech signal \(s \in \mathbb{R}^{T'}\), the output of WavLM is a tensor \(\bm{r}\) with shape \(n \times T \times E\), where \(n\) is the number of output layers (6 in this case), \(T\) is the time dimension, and \(E\) represents the embedding dimension.
+For tokenization, we apply a separate Kmeans model to each output layer, with each model using the same number of clusters, denoted by \(K\).
 After tokenization, the continuous embedding \(\bm{r}\) is transformed into a discrete tensor \(\bm{d}\) with shape \(n \times T\), where each value \(\bm{d}_{i} \in (0, K-1) \).
@@
 Given a reference speech \(s_r \in \mathbb{R}^{T^r}\) and a mixed speech \(s_m \in \mathbb{R}^{T'}\), we follow the previously described procedure to encode the reference speech into a tensor \(\bm{d_r}\) of shape \(n \times T_r\).
-However, for mixed speech, instead of applying the encoding directly, we first concatenate it with the reference speech, creating a signal \(s' = [s_r, s_m, s_r] \in \mathbb{R}^{(T^r + T' + T^r)}\).
+However, for the mixed speech, instead of applying the encoding directly, we first concatenate it with the reference speech, creating a signal \(s' = [s_r, s_m, s_r] \in \mathbb{R}^{(T^r + T' + T^r)}\).
 This concatenated signal is then input into the encoder, producing an output tensor \(\bm{d'}\) with shape \(n \times (T_r + T + T_r)\), where \(T\) represents the length for the mixed speech embedding.
@@
 aggregate the tensor by using attention mechanism to sum all the 6 tensors. This summation 
-keeps the information of each layer while reducing the system complexity by reducing the 
+keeps the information of each layer while reducing the 
 dimension of layers. After attention embedding, we obtain reference embedding \(E_r\) and 
@@
 The cross attention module consists of a stack of cross-multiple head attention modules, followed by
-a feature-wise linear modulation (FiLM) module. 
-We use \(E_m\) as query and \(E_r\) as key and value for 
+a Feature-wise Linear Modulation (FiLM) module. 
+We use \(E_m\) as the query and \(E_r\) as the key and value for 
 the attention module. The output from the cross-multiple head attention module \(E_{spk}\)
@@
 
-\section{Experiments}
+\section{Experiments Setup}
 
@@
 \(K=1000\).
-We use embedding dimension 1024.
+We use 1024 as the embedding dimension.
 The cross-attention module consists of four transformer encoders, each with 16 attention heads and an MLP with a hidden dimension of 1024.
@@
 our optimizer for all the experiments. The learning rate 
-is \(5 \times 10^{-4}\) for TSELM-S and \(5 \times 10^{-5}\) for TSELM-M and TSELM-L. We train the model using 8 GPUs with 16 GB of RAM each each with batch size 16 for a total of 40,000 steps.
+is \(5 \times 10^{-4}\) for TSELM-S and \(5 \times 10^{-5}\) for TSELM-M and TSELM-L. We train the model using 8 GPUs with 32 GB of RAM, each with batch size 16 for a total of 40,000 steps.
 
@@
 We evaluate our models using Libri2Mix\cite{librimix} and WSJ0-2mix \cite{wsj0}.
-We follow the recipes\footnote{\href{https://github.com/xuchenglin28/speaker_extraction}{https://github.com/xuchenglin28/speaker\_extraction}} to from the reference speeches for 
+We follow the recipes\footnote{\href{https://github.com/xuchenglin28/speaker_extraction}{https://github.com/xuchenglin28/speaker\_extraction}} to form the reference speeches for 
 WSJ0-2mix.
@@
 
-It is shown that metrics like PESQ, SI-SNR, STOI do not reflect speech quality of output of 
-vocoders due to the fact that the vocoder output does not focus strictly on frame alignment
-\cite{tokensplit,selm}. We use DNSMOS \cite{dnsmos} to measure the speech quality, and differential 
-word error 
-rate (dWER) \cite{dwer} to measure the speech intelligibility. For speaker similarity, we use the 
+It is shown that metrics like PESQ, SI-SNR, STOI do not accurately reflect the speech quality of 
+vocoder outputs due to the fact that the vocoder output does not focus strictly on frame alignment
+\cite{tokensplit,selm}. We use DNSMOS \cite{dnsmos} to measure the speech quality, and the differential 
+Word Error 
+Rate (dWER) \cite{dwer} to measure the speech intelligibility. For speaker similarity, we use the 
 public WeSpeaker \cite{wespeaker}.
@@
 speech while utilizing the continuous embeddings from the mixed speech. We call 
-it hybrid because the mixture speech retains continuous features. In TSELM-S-NoCat, we utilize the TSELM-S model architecture but abandon concatenation strategy.
+it hybrid because the mixture speech retains continuous features.
+In TSELM-S-NoCat, we utilize the TSELM-S model architecture but abandon concatenation strategy.
+The code and pretrained models are available at \footnote{\href{https://github.com/Beilong-Tang/TSELM}{https://github.com/Beilong-Tang/TSELM}}.
 
@@
                           & \multicolumn{1}{l}{}                                                    & \multicolumn{1}{l}{}                            & SIG         & BAK        & OVL        &                   &        &             & SIG         & BAK        & OVL        &                   &                    \\ \hline
-  Mixture                 & -                                             & -                                                                                           & 3.39        & 3.14       & 2.68       & 79.3            & -        &           & 3.42        & 3.28       & 2.81       & 63.6            & -                  \\
-  Target-Discrete         & G                                             & -                                                                                          & 3.57        & 4.10       & 3.32       & 11.3            & 0.653     &          & 3.56        & 4.09       & 3.30       & 10.1            & 0.657               \\ \hline
-  Spex+                   & D                                             & -                                                                                  & 3.36        & 3.76       & 2.98       & 19.3            & 0.923     &          & 3.49        & 4.00       & 3.21       & 15.0            & 0.943             \\
+  Mixture                 & -                                             & -                                                                                           & 3.38        & 3.10       & 2.65       & 79.2            & -        &           & 3.42        & 3.28       & 2.81       & 63.6            & -                  \\
+  Target-Discrete         & G                                             & -                                                                                          & 3.47       & 4.03       & 3.19       & 11.8            & 0.654     &          & 3.56        & 4.09       & 3.30       & 10.1            & 0.657               \\ \hline
+  Spex+                   & D                                             & -                                                                                  & 3.38        & 3.77       & 3.00       & 19.0            & 0.922     &          & 3.49        & 4.00       & 3.21       & 15.0            & 0.943             \\
   SkiM-UniCATS                   & G                                             & D                                                                                  & -        & -      & -       & -            & -     &          & 3.62        & 4.10       & 3.37       & -            & -             \\ \hline
-  Continuous-WavLM-L6     & G                                             & C                                                                                  & 3.56        & 4.06       & 3.27       & 14.7            & 0.877     &          & 3.61        & 4.08       & 3.35       & 8.0            & 0.892             \\
-  TSELM-L-Hybrid          & G                                             & H                                                                                     & 3.50        & 4.06       & 3.22       & 19.8            & 0.924\_d  &          & 3.57        & 4.10       & 3.31       & 12.6            & 0.915\_d             \\
-  TSELM-S-NoCat       & G                                             & D                                                                                   & 3.47        & 4.03       & 3.19       & 69.6            & 0.868\_d    &        & 3.55        & 4.08       & 3.28       & 64.5            & 0.888\_d         \\ \hline
-  TSELM-S                 & G                                             & D                                                                                    & 3.50        & 4.07       & 3.24       & 28.1            & 0.892\_d      &      & 3.57        & 4.10       & 3.32       & 19.4            & 0.915\_d            \\
-  TSELM-M                 & G                                             & D                                                                                   & 3.49        & 4.05       & 3.22       & 28.4            & 0.901\_d    &        & 3.57        & 4.10       & 3.32       & 18.8            & 0.921\_d             \\
-  TSELM-L                 & G                                             & D                                                                                  & 3.49        & 4.05       & 3.22       & 27.1            & 0.905\_d    &        & 3.57        & 4.10       & 3.31       & 17.8            & 0.924\_d        \\
+  Continuous-WavLM-L6     & G                                             & C                                                                                  & 3.57        & 4.06       & 3.28       & 14.6            & 0.870     &          & 3.61        & 4.08       & 3.35       & 8.0            & 0.892             \\
+  TSELM-L-Hybrid          & G                                             & H                                                                                     & 3.49        & 4.05       & 3.22       & 20.0            & 0.917\_d  &          & 3.57        & 4.10       & 3.31       & 12.6            & 0.915\_d             \\
+  TSELM-S-NoCat       & G                                             & D                                                                                   & 3.48        & 4.02       & 3.19       & 71.5            & 0.854\_d    &        & 3.55        & 4.08       & 3.28       & 64.5            & 0.888\_d         \\ \hline
+  TSELM-S                 & G                                             & D                                                                                    & 3.50        & 4.06       & 3.23       & 28.1            & 0.883\_d      &      & 3.57        & 4.10       & 3.32       & 19.4            & 0.915\_d            \\
+  TSELM-M                 & G                                             & D                                                                                   & 3.49        & 4.04       & 3.21       & 29.0            & 0.892\_d    &        & 3.57        & 4.10       & 3.32       & 18.8            & 0.921\_d             \\
+  TSELM-L                 & G                                             & D                                                                                  & 3.49        & 4.04       & 3.21       & 27.5            & 0.895\_d    &        & 3.57        & 4.10       & 3.31       & 17.8            & 0.924\_d        \\
   \Xhline{2\arrayrulewidth} % Bold top line     
@@
 \end{center}
+\vspace{-15.5pt}
   \end{table*}
@@
   \begin{table}
-    \caption{Performance of different SSL models and layer selections. HuBERT model subsitutes the WavLM Large to HuBERT Large as the SSL model.
-            The WavLM-L6 uses only the 6th layer of hidden output of WavLM Large. WavLM denotes our TSELM model which uses 6 different output layers. 
+    \caption{Performance of different SSL models and layer selections on Libri2Mix clean. HuBERT model subsitutes the WavLM Large to HuBERT Large as the SSL model.
+            The WavLM-L6 uses only the 6th layer of hidden output of WavLM Large. WavLM denotes our TSELM-L model which uses 6 hidden layers. 
             }
@@
             \hline
-            \multirow{2}{*}{HuBERT}                              &  Discrete                          & 3.56    & 4.09    & 3.30   & 81.3\%                & 0.865\_d                        \\
-                                             &  Hybrid                          & 3.57    & 4.10    & 3.32   & 35.1\%                & 0.907\_d                        \\
+            \multirow{2}{*}{HuBERT}                              &  Discrete                          & 3.57    & 4.09    & 3.31   & 82.2                & 0.854\_d                        \\
+                                             &  Hybrid                          & 3.57    & 4.10    & 3.32   & 36.1                & 0.900\_d                        \\
             \hline
-            \multirow{2}{*}{WavLM-L6}                              &  Discrete                          & 2.08    & 2.07    & 1.64   & 122.1\%                & 0.589\_d                        \\
-            &  Hybrid                          & 3.54    & 3.84    & 3.12   & 30.0\%                & 0.849\_d                        \\
+            \multirow{2}{*}{WavLM-L6}                              &  Discrete                          & 1.74    & 1.58    & 1.40   & 165.4                & 0.516\_d                        \\
+            &  Hybrid                          & 3.54    & 3.93    & 3.18   & 29.3                & 0.838\_d                        \\
             \hline
-            \multirow{2}{*}{WavLM}                                     &  Discrete                          & 3.49    & 4.05    & 3.22   & 27.1\%                & 0.905\_d                        \\
-                                              &  Hybrid                          & 3.50    & 4.06    & 3.22   & 19.8\%                & 0.924\_d                        \\
+            \multirow{2}{*}{WavLM}                                     &  Discrete                          & 3.49    & 4.04    & 3.21   & 27.5                & 0.895\_d                        \\
+                                              &  Hybrid                          & 3.49    & 4.05    & 3.22   & 20.0                & 0.917\_d                        \\
 
@@
 shown that our model can achieve excellent performance in terms of speech quality, and comparable performance in terms of speech intelligibility.
-However, our model relies on WavLM's denoising property, and future work should focus on developing speaker-aware tokenization method.
+However, we observe a gap between discrete methods and continuous methods especially in speech intelligibility and speaker similarity.
+Future research should focus on shrinking
+this gap.
 

### 2024-09-11 src/paper.tex
update

@@
     \label{model}
+    \vspace{-12pt}
     \end{figure*}
@@
         \label{cross_attention}
+        \vspace{-17pt}
         \end{figure}
@@
 
-  % Please add the following required packages to your document preamble:
-% \usepackage{multirow}
-
 We use the pretrained self-supervised learning (SSL) model WavLM Large \cite{wavlm} to encode speech into continuous representations.
@@
 \subsection{Modeling}
+
+\begin{table*}
+  % \setlength{\tabcolsep}{5pt} % Adjust column spacing
+  \caption{Results on Libri2Mix (clean) and WSJ0-2mix: In the "Category" column, "G" refers to generative models, while "D" refers to discriminative models.
+The "Type" column categorizes methods as "D" (discrete), "H" (hybrid), or "C" (continuous).
+  For discrete methods, speaker similarity is compared against the discretized target speech (denoted as Target-discrete-WavLM) instead of the original target speech. It is denoted as "\_d".}
+  \renewcommand{\arraystretch}{1.2}
+  \begin{center}
+  \begin{tabular}{cccccccccccccccccc}
+    \Xhline{2\arrayrulewidth} % Bold top line
+  \multirow{3}{*}{System} & \multicolumn{1}{l}{\multirow{3}{*}{Category}} & \multicolumn{1}{l}{\multirow{3}{*}{Type}} &  \multicolumn{5}{c}{Libri2Mix Clean}                    &                               & \multicolumn{5}{c}{WSJ0\_2mix}                                                  \\
+  \cline{4-8} \cline{10-14}
+                          & \multicolumn{1}{l}{}                                                 & \multicolumn{1}{l}{}                            & \multicolumn{3}{c}{DNSMOS $\uparrow$} & dWER $\downarrow$ & Spk Sim $\uparrow$ &  & \multicolumn{3}{c}{DNSMOS $\uparrow$} & dWER $\downarrow$ & Spk Sim $\uparrow$  \\ \cline{4-6} \cline{10-12}
+                          & \multicolumn{1}{l}{}                                                    & \multicolumn{1}{l}{}                            & SIG         & BAK        & OVL        &                   &        &             & SIG         & BAK        & OVL        &                   &                    \\ \hline
+  Mixture                 & -                                             & -                                                                                           & 3.38        & 3.10       & 2.65       & 79.2            & -        &           & 3.42        & 3.28       & 2.81       & 63.6            & -                  \\
+  Target-Discrete         & G                                             & -                                                                                          & 3.47       & 4.03       & 3.19       & 11.8            & 0.654     &          & 3.56        & 4.09       & 3.30       & 10.1            & 0.657               \\ \hline
+  Spex+\cite{spex_plus}                   & D                                             & -                                                                                  & 3.38        & 3.77       & 3.00       & 19.0            & 0.922     &          & 3.49        & 4.00       & 3.21       & 15.0            & 0.943             \\
+  SkiM-UniCATS\cite{gen_tse}                   & G                                             & D                                                                                  & -        & -      & -       & -            & -     &          & 3.62        & 4.10       & 3.37       & -            & -             \\ \hline
+  Continuous-WavLM-L6     & G                                             & C                                                                                  & 3.57        & 4.06       & 3.28       & 14.6            & 0.870     &          & 3.61        & 4.08       & 3.35       & 8.0            & 0.892             \\
+  TSELM-L-Hybrid          & G                                             & H                                                                                     & 3.49        & 4.05       & 3.22       & 20.0            & 0.917\_d  &          & 3.57        & 4.10       & 3.31       & 12.6            & 0.915\_d             \\
+  TSELM-S-NoCat       & G                                             & D                                                                                   & 3.48        & 4.02       & 3.19       & 71.5            & 0.854\_d    &        & 3.55        & 4.08       & 3.28       & 64.5            & 0.888\_d         \\ \hline
+  TSELM-S                 & G                                             & D                                                                                    & 3.50        & 4.06       & 3.23       & 28.1            & 0.883\_d      &      & 3.57        & 4.10       & 3.32       & 19.4            & 0.915\_d            \\
+  TSELM-M                 & G                                             & D                                                                                   & 3.49        & 4.04       & 3.21       & 29.0            & 0.892\_d    &        & 3.57        & 4.10       & 3.32       & 18.8            & 0.921\_d             \\
+  TSELM-L                 & G                                             & D                                                                                  & 3.49        & 4.04       & 3.21       & 27.5            & 0.895\_d    &        & 3.57        & 4.10       & 3.31       & 17.8            & 0.924\_d        \\
+  \Xhline{2\arrayrulewidth} % Bold top line     
+  \end{tabular}
+  \label{main_exp}
+\end{center}
+\vspace{-15.5pt}
+  \end{table*}
+
+  \begin{table}
+    \caption{Performance of different SSL models and layer selections on Libri2Mix clean.
+WavLM-L6 uses only the 6th layer of hidden output of the WavLM Large model.
+WavLM denotes our TSELM-L model which uses 6 hidden layers.
+            }
+            \vspace{-15pt}
+    \renewcommand{\arraystretch}{1.1}
+    \begin{center}
+      \setlength{\tabcolsep}{5pt}
+        \begin{tabular}{ccccccc}
+            \Xhline{2\arrayrulewidth} % Bold top line
+            \multirow{2}{*}{SSL-Model} & \multirow{2}{*}{Type} & \multicolumn{3}{c}{ DNSMOS $\uparrow$} & \multirow{2}{*}{dWER $\downarrow$} & \multirow{2}{*}{Spk Sim $\uparrow$} \\
+            \cline{3-5}
+                                                       &                             & SIG     & BAK     & OVL    &                       &                          \\ 
+            \hline
+            \multirow{2}{*}{HuBERT}                              &  Discrete                          & 3.57    & 4.09    & 3.31   & 82.2                & 0.854\_d                        \\
+                                             &  Hybrid                          & 3.57    & 4.10    & 3.32   & 36.1                & 0.900\_d                        \\
+            \hline
+            \multirow{2}{*}{WavLM-L6}                              &  Discrete                          & 1.74    & 1.58    & 1.40   & 165.4                & 0.516\_d                        \\
+            &  Hybrid                          & 3.54    & 3.93    & 3.18   & 29.3                & 0.838\_d                        \\
+            \hline
+            \multirow{2}{*}{WavLM}                                     &  Discrete                          & 3.49    & 4.04    & 3.21   & 27.5                & 0.895\_d                        \\
+                                              &  Hybrid                          & 3.49    & 4.05    & 3.22   & 20.0                & 0.917\_d                        \\
+
+            \Xhline{2\arrayrulewidth} % Bold top line              
+            \end{tabular}
+            \linebreak
+            \label{hubert_wavlm_6}
+      \end{center}
+      \vspace{-17pt}
+    \end{table}
+
 \subsubsection{Attention Embedding}
@@
 Word Error 
-Rate (dWER) \cite{dwer} to measure the speech intelligibility. For speaker similarity, we use the 
-public WeSpeaker \cite{wespeaker}.
+Rate (dWER) \cite{dwer} using the base model of Whisper \cite{whisper} to measure the speech intelligibility. For speaker similarity, we use the \texttt{ResNet221\_LM}
+from the public WeSpeaker \cite{wespeaker} to calculate the embedding cosine speaker similarity.
 
@@
 it hybrid because the mixture speech retains continuous features.
-In TSELM-S-NoCat, we utilize the TSELM-S model architecture but abandon concatenation strategy.
+In TSELM-S-NoCat, we utilize the TSELM-S model architecture but abandon the mixture concatenation strategy in the encoding step.
 The code and pretrained models are available at \footnote{\href{https://github.com/Beilong-Tang/TSELM}{https://github.com/Beilong-Tang/TSELM}}.
-
-\begin{table*}
-  % \setlength{\tabcolsep}{5pt} % Adjust column spacing
-  \caption{Results on Libri2Mix (clean) and WSJ0-2mix: In the "Category" column, "G" refers to generative models, while "D" refers to discriminative models.
-The "Type" column categorizes methods as "D" (discrete), "H" (hybrid), or "C" (continuous).
-  For discrete methods, speaker similarity is compared against the discretized target speech (denoted as Target-discrete-WavLM) instead of the original target speech. It is denoted as "\_d".}
-  \renewcommand{\arraystretch}{1.2}
-  \begin{center}
-  \begin{tabular}{cccccccccccccccccc}
-    \Xhline{2\arrayrulewidth} % Bold top line
-  \multirow{3}{*}{System} & \multicolumn{1}{l}{\multirow{3}{*}{Category}} & \multicolumn{1}{l}{\multirow{3}{*}{Type}} &  \multicolumn{5}{c}{Libri2Mix Clean}                    &                               & \multicolumn{5}{c}{WSJ0\_2mix}                                                  \\
-  \cline{4-8} \cline{10-14}
-                          & \multicolumn{1}{l}{}                                                 & \multicolumn{1}{l}{}                            & \multicolumn{3}{c}{DNSMOS $\uparrow$} & dWER $\downarrow$ & Spk Sim $\uparrow$ &  & \multicolumn{3}{c}{DNSMOS $\uparrow$} & dWER $\downarrow$ & Spk Sim $\uparrow$  \\ \cline{4-6} \cline{10-12}
-                          & \multicolumn{1}{l}{}                                                    & \multicolumn{1}{l}{}                            & SIG         & BAK        & OVL        &                   &        &             & SIG         & BAK        & OVL        &                   &                    \\ \hline
-  Mixture                 & -                                             & -                                                                                           & 3.38        & 3.10       & 2.65       & 79.2            & -        &           & 3.42        & 3.28       & 2.81       & 63.6            & -                  \\
-  Target-Discrete         & G                                             & -                                                                                          & 3.47       & 4.03       & 3.19       & 11.8            & 0.654     &          & 3.56        & 4.09       & 3.30       & 10.1            & 0.657               \\ \hline
-  Spex+                   & D                                             & -                                                                                  & 3.38        & 3.77       & 3.00       & 19.0            & 0.922     &          & 3.49        & 4.00       & 3.21       & 15.0            & 0.943             \\
-  SkiM-UniCATS                   & G                                             & D                                                                                  & -        & -      & -       & -            & -     &          & 3.62        & 4.10       & 3.37       & -            & -             \\ \hline
-  Continuous-WavLM-L6     & G                                             & C                                                                                  & 3.57        & 4.06       & 3.28       & 14.6            & 0.870     &          & 3.61        & 4.08       & 3.35       & 8.0            & 0.892             \\
-  TSELM-L-Hybrid          & G                                             & H                                                                                     & 3.49        & 4.05       & 3.22       & 20.0            & 0.917\_d  &          & 3.57        & 4.10       & 3.31       & 12.6            & 0.915\_d             \\
-  TSELM-S-NoCat       & G                                             & D                                                                                   & 3.48        & 4.02       & 3.19       & 71.5            & 0.854\_d    &        & 3.55        & 4.08       & 3.28       & 64.5            & 0.888\_d         \\ \hline
-  TSELM-S                 & G                                             & D                                                                                    & 3.50        & 4.06       & 3.23       & 28.1            & 0.883\_d      &      & 3.57        & 4.10       & 3.32       & 19.4            & 0.915\_d            \\
-  TSELM-M                 & G                                             & D                                                                                   & 3.49        & 4.04       & 3.21       & 29.0            & 0.892\_d    &        & 3.57        & 4.10       & 3.32       & 18.8            & 0.921\_d             \\
-  TSELM-L                 & G                                             & D                                                                                  & 3.49        & 4.04       & 3.21       & 27.5            & 0.895\_d    &        & 3.57        & 4.10       & 3.31       & 17.8            & 0.924\_d        \\
-  \Xhline{2\arrayrulewidth} % Bold top line     
-  \end{tabular}
-  \label{main_exp}
-\end{center}
-\vspace{-15.5pt}
-  \end{table*}
-
-  \begin{table}
-    \caption{Performance of different SSL models and layer selections on Libri2Mix clean. HuBERT model subsitutes the WavLM Large to HuBERT Large as the SSL model.
-            The WavLM-L6 uses only the 6th layer of hidden output of WavLM Large. WavLM denotes our TSELM-L model which uses 6 hidden layers. 
-            }
-            \vspace{-20.5pt}
-    \renewcommand{\arraystretch}{1.1}
-    \begin{center}
-        \begin{tabular}{ccccccc}
-            \Xhline{2\arrayrulewidth} % Bold top line
-            \multirow{2}{*}{SSL-Model} & \multirow{2}{*}{Type} & \multicolumn{3}{c}{ DNSMOS $\uparrow$} & \multirow{2}{*}{dWER $\downarrow$} & \multirow{2}{*}{Spk Sim $\uparrow$} \\
-            \cline{3-5}
-                                                       &                             & SIG     & BAK     & OVL    &                       &                          \\ 
-            \hline
-            \multirow{2}{*}{HuBERT}                              &  Discrete                          & 3.57    & 4.09    & 3.31   & 82.2                & 0.854\_d                        \\
-                                             &  Hybrid                          & 3.57    & 4.10    & 3.32   & 36.1                & 0.900\_d                        \\
-            \hline
-            \multirow{2}{*}{WavLM-L6}                              &  Discrete                          & 1.74    & 1.58    & 1.40   & 165.4                & 0.516\_d                        \\
-            &  Hybrid                          & 3.54    & 3.93    & 3.18   & 29.3                & 0.838\_d                        \\
-            \hline
-            \multirow{2}{*}{WavLM}                                     &  Discrete                          & 3.49    & 4.04    & 3.21   & 27.5                & 0.895\_d                        \\
-                                              &  Hybrid                          & 3.49    & 4.05    & 3.22   & 20.0                & 0.917\_d                        \\
-
-            \Xhline{2\arrayrulewidth} % Bold top line              
-            \end{tabular}
-            \linebreak
-            \label{hubert_wavlm_6}
-      \end{center}
-      \vspace{-15.5pt}
-    \end{table}
 
@@
 For continuous methods, speaker similarity is directly computed against the clean speech. 
-However, since discretization inherently results in some loss of speaker information—Target-Discrete shows a speaker similarity score of 0.653 for Libri2Mix compared to continuous methods—we assess the speaker similarity of the output from the discrete methods against the target audio produced by discretizing the clean speech.
+However, since discretization inherently results in some loss of speaker information—Target-Discrete shows a speaker similarity score of 0.653 on Libri2Mix —we follow \cite{dasb} to assess the speaker similarity of the output from the discrete methods against the target audio produced by discretizing the clean speech.
 This target audio output from Target-Discrete serves as the upper bond for our model performance.
@@
 
-We observe that our model outperforms Spex+ in terms of DNSMOS scores, indicating better speech quality, but performs slightly worse in dWER, suggesting lower speech intelligibility.
+We observe that TSELM-l outperforms Spex+ in terms of DNSMOS scores, indicating better speech quality, but performs slightly worse in dWER, suggesting lower speech intelligibility.
 One potential reason for this could be the discretization process applied to the mixed speech.
@@
 However, when applied to mixed speech, this discretization might lead to the model focusing on the wrong speaker, as it may only retain dominant speaker information, causing a reduction in intelligibility.
-This hypothesis is supported by the results of TSELM-L-Hybrid, where continuous embeddings from the mixture speech were used without discretization, achieving dWER scores similar to Spex+.
-Another contributing factor could be the limitations of our current language model (LM).
-The encoder-only LM achieves around 50\% accuracy, and we believe using more advanced models, such as auto-regressive or masking-based LMs, could lead to improved performance in future iterations.
+This hypothesis is supported by the results of TSELM-L-Hybrid, where continuous embeddings from the mixture speech were used without discretization, achieving dWER scores better than Spex+ on WSJ0-2mix.
+% Another contributing factor could be the limitations of our current language model (LM).
+The encoder-only LM achieves around 55\% accuracy for token prediction on Libri2Mix testset, and we believe using more advanced models, such as auto-regressive or masking-based LMs, could lead to improved performance in future iterations.
 
-We observe a significant increase in dWER when the mixture audio is not concatenated with the reference, as seen in the TSELM-S-NoCat results in Table \ref{main_exp}.
+We observe a significant increase in dWER when the mixture audio is not concatenated with the reference in the encoding step, as seen in the TSELM-S-NoCat results in Table \ref{main_exp}.
 For WavLM to effectively perform target speaker separation, the input audio must follow specific conditions: the mixture should be less than 50\% of the total length, and the first utterance should be the target speaker.
@@
 Our current concatenation strategy, inspired by SELM's \cite{selm} success in speech denoising, reframes the target speaker extraction task as a more challenging speech enhancement problem, utilizing WavLM's denoising capabilities.
-However, this approach remains suboptimal, and we believe future work should prioritize developing a speaker-aware tokenization method.
+However, this approach remains suboptimal, and we believe our future work should prioritize developing a speaker-aware tokenization method.
 
-In Table \ref{hubert_wavlm_6}, we compare the performance of HuBERT and WavLM as SSL model and examine the effects of using either one or multiple layers for discretization.
+In Table \ref{hubert_wavlm_6}, we compare the performance of HuBERT and WavLM as SSL models and examine the effects of using either one or multiple layers for discretization.
 Our findings indicate that using HuBERT as the SSL model results in better DNSMOS scores but much worse dWER compared to our WavLM baseline.
@@
 This might be because that using multiple layer outputs can better tolerate errors compared to using just one layer output.
-Although SkiM-UniCATS \cite{gen_tse} achieves satisfying DNSMOS scores, it does not ensure high speaker similarity, as indicated in Table \ref{main_exp}.
-Additionally, results in Table \ref{hubert_wavlm_6} show that it also does not guarantee superior speech intelligibility.
 
@@
 The gap in performance may be attributed to the information loss inherent in the discretization process. 
-We hope future research will work to bridge this gap.
+We hope our future research will bridge this gap.
 

### 2024-09-12 src/paper.tex
update

@@
 
-The discretization of audio has gained significant attention with the advancement of language models (LMs) \cite{l1, l2, l3, l4, l5}. It has been explored in
+The discretization of audio has gained significant attention with the advancement of language models (LMs) \cite{l1, l2, l3, l4, l5}.
+It has achieved superior performances compared with discriminative models in
 tasks such as speech enhancement \cite{selm} and blind speech separation \cite{dasb,tokensplit}.
-This method converts audio into discrete tokens, and leverages LMs to model them, thereby simplifying audio generation tasks by transforming complex regression problems into classification tasks \cite{dasb}.
+These methods convert audio into discrete tokens, and leverages LMs to model them, thereby simplifying audio generation tasks by transforming complex regression problems into classification tasks \cite{dasb}.
+
 Self-Supervised Learning (SSL) models such as HuBERT \cite{hubert} and WavLM \cite{wavlm} have demonstrated outstanding performances across numerous downstream tasks \cite{superb}, as they extract continuous representations rich in semantic and timbral information from speech.
@@
 However, we observe a gap between discrete methods and continuous methods especially in speech intelligibility and speaker similarity.
-Future research should focus on shrinking
+We will focus on shrinking
 this gap.

### 2024-09-12 src/paper.tex
update

@@
 However, these discriminative approaches often struggle to generalize to unseen data and may introduce undesirable distortions \cite{distortion}.
-To address these limitations, generative models aim to learn the underlying distribution of the target speech, rather than mapping mixed speech to clean speech.
-Recently, generative models have been shown to achieve performance comparable to that of discriminative models in blind speech separation \cite{tokensplit} and TSE \cite{target_diff}.
+To solve these issues, researchers have proposed generative models.
+This method aims to learn the underlying distribution of the target speaker's voice and use this knowledge to generate the clean speech of the target speaker from a mixture of voices rather
+than directly mapping from mixed speech to clean speech. Some generative models, like diffusion
+models \cite{target_diff} and variational autoencoders (VAE) \cite{vae} have been studied.
+It has been demonstrated that generative models can achieve results comparable to those of discriminative models \cite{target_diff,tokensplit}.
 
-The discretization of audio has gained significant attention with the advancement of language models (LMs) \cite{l1, l2, l3, l4, l5}.
-It has achieved superior performances compared with discriminative models in
-tasks such as speech enhancement \cite{selm} and blind speech separation \cite{dasb,tokensplit}.
-These methods convert audio into discrete tokens, and leverages LMs to model them, thereby simplifying audio generation tasks by transforming complex regression problems into classification tasks \cite{dasb}.
+The modeling of discretization of audio has gained significant attention with the advancement of language models (LMs) in modeling texts \cite{l1, l2, l3, l4, l5}.
+Researchers are trying to convert audio into discrete tokens and leverage LMs to
+model them, thereby simplifying audio generation tasks by transforming complex regression problems into classification tasks \cite{dasb}.
+LMs have demonstrated its scalability and unification of different modalities in audio synthesis tasks \cite{audio_gen,deshmukh2023pengi,chen2023lauragpt}.
+It has also achieved superior performances compared with discriminative models in
+tasks such as speech enhancement \cite{selm,mask_sr} and blind speech separation \cite{dasb,tokensplit}.
 
-Self-Supervised Learning (SSL) models such as HuBERT \cite{hubert} and WavLM \cite{wavlm} have demonstrated outstanding performances across numerous downstream tasks \cite{superb}, as they extract continuous representations rich in semantic and timbral information from speech.
+Some discretization methods \cite{selm,tokensplit,dasb} use Kmeans on the output of Self-Supervised Learning (SSL) models such as HuBERT \cite{hubert} and WavLM \cite{wavlm}.
+SSL models have demonstrated outstanding performances across numerous downstream tasks \cite{superb}, as they extract continuous representations rich in semantic and timbral information from speech.
 

### 2024-09-12 src/paper.tex
update

@@
 \begin{IEEEkeywords}
-target speaker extraction, speech separation, language models, audio discretization, Self-Supervised Models
+target speaker extraction, speech separation, language models, audio discretization, self-supervised models
 \end{IEEEkeywords}
@@
 model them, thereby simplifying audio generation tasks by transforming complex regression problems into classification tasks \cite{dasb}.
-LMs have demonstrated its scalability and unification of different modalities in audio synthesis tasks \cite{audio_gen,deshmukh2023pengi,chen2023lauragpt}.
+LMs have demonstrated scalability and unification of different modalities in audio synthesis tasks \cite{audio_gen,deshmukh2023pengi,chen2023lauragpt}.
 It has also achieved superior performances compared with discriminative models in
-tasks such as speech enhancement \cite{selm,mask_sr} and blind speech separation \cite{dasb,tokensplit}.
+tasks such as speech enhancement \cite{selm,mask_sr} and blind speech separation \cite{tokensplit}.
 
@@
 This allows WavLM to focus on producing target speaker dependent embeddings.
-Our experiments demonstrated that this concatenation strategy significantly enhances the model's performance by guiding it to prioritize the target speaker's information.
+Our experiments demonstrate that this concatenation strategy significantly enhances the model's performance by guiding it to prioritize the target speaker's information.
 \subsection{Modeling}
@@
 keeps the information of each layer while reducing the 
-dimension of layers. After attention embedding, we obtain reference embedding \(E_r\) and 
+dimension of layers and system complexity. After attention embedding, we obtain reference embedding \(E_r\) and 
 mixture embedding \(E_m\).
@@
 vocoder outputs due to the fact that the vocoder output does not focus strictly on frame alignment
-\cite{tokensplit,selm}. We use DNSMOS \cite{dnsmos} to measure the speech quality, and the differential 
+\cite{tokensplit,selm}. Instead, we use DNSMOS \cite{dnsmos} to measure the speech quality, and the differential 
 Word Error 
@@
 
-We observe that TSELM-l outperforms Spex+ in terms of DNSMOS scores, indicating better speech quality, but performs slightly worse in dWER, suggesting lower speech intelligibility.
+We observe that TSELM-L outperforms Spex+ in terms of DNSMOS scores, indicating better speech quality, but performs slightly worse in dWER, suggesting lower speech intelligibility.
 One potential reason for this could be the discretization process applied to the mixed speech.
@@
 The improved DNSMOS scores likely stem from the vocoder performance, yet they do not adequately reflect speech intelligibility, which is crucial for speech separation tasks.
-The poorer dWER scores observed with HuBERT may be attributed to its training on clean speech, which might not equip it to capture the complexity and richness of mixed speech.
+The poorer dWER scores observed with this HuBERT model may be attributed to its training on clean speech, which might not equip it to capture the complexity and richness of mixed speech.
 Moreover, our results from WavLM-L6 suggest that when performing speech separation, discretizing across multiple layers provides better results than relying on a single layer.

### 2024-09-12 src/paper.tex
update

@@
         \includegraphics[width=0.25\textwidth]{assets/cross_attention.pdf}
-        \caption{Details of Cross Attention mechanism.}
+        \caption{Details of Cross-Attention mechanism.}
         \label{cross_attention}
@@
 \subsubsection{Cross Attention}
-We apply cross attention module in \cite{usef_tes} to inject the reference embeddings into the mixture. The details 
+We apply cross-attention module in \cite{usef_tes} to inject the reference embeddings into the mixture. The details 
 are shown in Fig.\ref{cross_attention}.
-The cross attention module consists of a stack of cross-multiple head attention modules, followed by
+The cross-attention module consists of a stack of cross-multiple head attention modules, followed by
 a Feature-wise Linear Modulation (FiLM) module. 
@@
 For Continuous-WavLM-6, we directly
-pass the embeddings from the 6th hidden layer output of WavLM Large to the cross attention  
+pass the embeddings from the 6th hidden layer output of WavLM Large to the cross- attention  
 and LM without discretization. 

### 2024-09-12 src/paper.tex
update

@@
     \includegraphics[width=0.77\textwidth]{assets/model.pdf}
-    \caption{Overview of TSELM.}
+    \caption{Overview of our proposed target speaker extraction framework with discrete tokens and language models.}
     \label{model}
@@
         \includegraphics[width=0.25\textwidth]{assets/cross_attention.pdf}
-        \caption{Details of Cross-Attention mechanism.}
+        \caption{Details of the Cross-Attention mechanism in modeling.}
         \label{cross_attention}
@@
 SkiM-UniCATS \cite{gen_tse} is among the first to use discrete tokens in TSE, leveraging SSL models like HuBERT and vq-wav2vec \cite{vq_wav2vec}.
-However, it overlooks the WavLM model, which excels in speech separation.
+However, it overlooks the WavLM model, which excels in speech separation \cite{wavlm}.
 Also, it mainly focuses on single-layer outputs for discretization.
@@
 In the encoding stage, both reference and mixed speech are tokenized using WavLM and Kmeans.
-The reference speech is passed directly to the encoder, while for mixed speech, we concatenate the reference speech to both sides of the mixture before passing it through the WavLM model.
+The reference speech is passed directly to the encoder, while for the mixed speech, we concatenate the reference speech to both sides of the mixture before passing it through the WavLM model.
 After tokenization, we retain only the tokens corresponding to the mixed speech.
@@
 An encoder-only language model, followed by a linear classifier, is then used to generate the reconstructed tokens.
-In the decoding stage, we leverage the pretrained scalable HiFi-GAN from \cite{unit_hifi} to reconstruct the audio from the discrete tokens.
+In the decoding stage, we leverage the pretrained scalable HiFi-GAN in \cite{unit_hifi} to reconstruct the audio from the discrete tokens.
 Unlike SELM \cite{selm}, where a conformer detokenizer is trained to reconstruct WavLM embeddings before passing them through HiFi-GAN, the scalable HiFi-GAN in \cite{unit_hifi} uses a dropout mechanism to directly reconstruct audio from multiple layers of tokens, eliminating the need for a conformer detokenizer and the complexity of training a separate HiFi-GAN for each layer.
-Both the encoder and decoder are kept frozen during training, and an overview of the model is shown in Fig.\ref{model}.
+Both the encoder and decoder are kept frozen during training.
+An overview of TSELM is shown in Fig.\ref{model}.
 Extensive experiments demonstrate that our method achieves excellent speech quality and comparable intelligibility results.
@@
 
-We use the pretrained self-supervised learning (SSL) model WavLM Large \cite{wavlm} to encode speech into continuous representations.
+We use the pretrained SSL model WavLM Large \cite{wavlm} to encode speech into continuous representations.
 Specifically, we extract the outputs from six hidden layers: 1, 3, 7, 12, 18, and 23.
@@
 The encoder remains frozen during training.
+
 The encoding strategy for mixed speech is crucial to the performance of the model.
@@
   % \setlength{\tabcolsep}{5pt} % Adjust column spacing
-  \caption{Results on Libri2Mix (clean) and WSJ0-2mix: In the "Category" column, "G" refers to generative models, while "D" refers to discriminative models.
+  \caption{Results on Libri2Mix clean and WSJ0-2mix: In the "Category" column, "G" refers to generative models, while "D" refers to discriminative models.
 The "Type" column categorizes methods as "D" (discrete), "H" (hybrid), or "C" (continuous).
-  For discrete methods, speaker similarity is compared against the discretized target speech (denoted as Target-discrete-WavLM) instead of the original target speech. It is denoted as "\_d".}
+  For discrete methods, speaker similarity is compared against the discretized target speech (denoted as Target-Discrete) instead of the original target speech. It is denoted as "\_d".}
   \renewcommand{\arraystretch}{1.2}
   \begin{center}
+    \setlength{\tabcolsep}{4.9pt}
   \begin{tabular}{cccccccccccccccccc}
@@
   Spex+\cite{spex_plus}                   & D                                             & -                                                                                  & 3.38        & 3.77       & 3.00       & 19.0            & 0.922     &          & 3.49        & 4.00       & 3.21       & 15.0            & 0.943             \\
-  SkiM-UniCATS\cite{gen_tse}                   & G                                             & D                                                                                  & -        & -      & -       & -            & -     &          & 3.62        & 4.10       & 3.37       & -            & -             \\ \hline
+  SkiM-UniCATS(vq-wav2vec)\cite{gen_tse}                   & G                                             & D                                                                                  & -        & -      & -       & -            & -     &          & 3.62        & 4.10       & 3.37       & -            & -             \\ \hline
   Continuous-WavLM-L6     & G                                             & C                                                                                  & 3.57        & 4.06       & 3.28       & 14.6            & 0.870     &          & 3.61        & 4.08       & 3.35       & 8.0            & 0.892             \\
@@
 We use 1024 as the embedding dimension.
-The cross-attention module consists of four transformer encoders, each with 16 attention heads and an MLP with a hidden dimension of 1024.
+The cross-attention module consists of 4 transformer encoders, each with 16 attention heads and an MLP with a hidden dimension of 1024.
 Layer normalization is applied after the cross-attention module.
 The LM of small version TSELM-S uses 
-embedding dimension \(d\) = 256, absolute sinusoidal positional embedding, conformer encoders as backbone of LM.
+embedding dimension \(d\) = 256, absolute sinusoidal positional embedding, conformer encoders as the backbone of LM.
 The conformer encoder consists of 6 layers with a kernel size of 31, each with 4 attention heads, and an MLP with a hidden dimension of 2048.
@@
 our optimizer for all the experiments. The learning rate 
-is \(5 \times 10^{-4}\) for TSELM-S and \(5 \times 10^{-5}\) for TSELM-M and TSELM-L. We train the model using 8 GPUs with 32 GB of RAM, each with batch size 16 for a total of 40,000 steps.
+is \(5 \times 10^{-4}\) for TSELM-S and \(5 \times 10^{-5}\) for TSELM-M and TSELM-L. We train our models using 8 GPUs with 32 GB of RAM, each with batch size 16 for a total of 40,000 steps.
 
@@
 Target-Discrete refers to the discretized target speech using our encoder and decoder. 
-It serves as the upper bond for our model performance.  Besides TSELM, we conduct three main experiments, named
+It serves as the upper bond for our model performance.  Besides TSELM, we conduct 3 main experiments, named
  Continuous-WavLM-L6, TSELM-L-Hybrid and TSELM-S-NoCat using the same training data. 
-For Continuous-WavLM-6, we directly
-pass the embeddings from the 6th hidden layer output of WavLM Large to the cross- attention  
-and LM without discretization. 
-The concatenation strategy is still applied to the mixed speech. Mean Square Error (MSE) loss is applied between the output embeddings and the clean 
+For Continuous-WavLM-L6, we directly
+pass the embeddings from the 6th hidden layer output of WavLM Large to the cross-attention without discretization. 
+The concatenation strategy is still applied to the mixed speech. Mean Square Error loss is applied between the output embeddings and the clean 
 embeddings. HiFi-GAN in \cite{knn_vc} is used for audio reconstruction. For 
 TSELM-L-Hybrid, inspired by MaskSR \cite{mask_sr}, we discretize the reference 
-speech while utilizing the continuous embeddings from the mixed speech. We call 
-it hybrid because the mixture speech retains continuous features.
+speech while utilizing the continuous embeddings from the mixed speech.
 In TSELM-S-NoCat, we utilize the TSELM-S model architecture but abandon the mixture concatenation strategy in the encoding step.
@@
 \section{Results and Discussions}
-Table \ref{main_exp} presents the performance of different systems evaluated on the Libri2Mix test and WSJ0-2mix testset. 
+Table \ref{main_exp} presents the performance of different systems evaluated on the Libri2Mix testset and WSJ0-2mix testset. 
 DNSMOS is computed over the 
@@
 For continuous methods, speaker similarity is directly computed against the clean speech. 
-However, since discretization inherently results in some loss of speaker information—Target-Discrete shows a speaker similarity score of 0.653 on Libri2Mix —we follow \cite{dasb} to assess the speaker similarity of the output from the discrete methods against the target audio produced by discretizing the clean speech.
-This target audio output from Target-Discrete serves as the upper bond for our model performance.
+However, since discretization inherently results in some loss of speaker information—Target-Discrete shows a speaker similarity score of 0.654 on Libri2Mix —we follow \cite{dasb} to assess the speaker similarity of the output from the discrete methods against the target audio produced by discretizing the clean speech.
 The observed speaker information loss is likely due to the tokenization process, which inherently reduces speaker fidelity.
 Future work should aim to enhance tokenization methods for SSL models to mitigate this loss.
-Since the primary goal of this research is to explore target speaker extraction using discretized information rather than to develop improved tokenization methods, we argue that comparing the outputs of our model with discretized speech is a reasonable approach, as it represents an upper bound on performance.
+Since the primary goal of this research is to explore target speaker extraction using discretized information rather than to develop improved tokenization methods, we argue that comparing the speaker similarity output with discretized clean speech is a reasonable approach, as it represents an upper bound of performance.
 
@@
 Our Kmeans algorithm is trained on clean speech rather than mixed speech, which is advantageous for speech enhancement as it likely aids in denoising.
-However, when applied to mixed speech, this discretization might lead to the model focusing on the wrong speaker, as it may only retain dominant speaker information, causing a reduction in intelligibility.
-This hypothesis is supported by the results of TSELM-L-Hybrid, where continuous embeddings from the mixture speech were used without discretization, achieving dWER scores better than Spex+ on WSJ0-2mix.
+However, when applied to mixed speech, this discretization might lead to the model focusing on the wrong speaker, as it is most likely to retain only the dominant speaker information, causing a reduction in intelligibility.
+This hypothesis is supported by the results of TSELM-L-Hybrid, where continuous embeddings from the mixture speech are used without discretization, achieving dWER scores better than Spex+ on WSJ0-2mix.
 % Another contributing factor could be the limitations of our current language model (LM).
@@
 In Table \ref{hubert_wavlm_6}, we compare the performance of HuBERT and WavLM as SSL models and examine the effects of using either one or multiple layers for discretization.
-Our findings indicate that using HuBERT as the SSL model results in better DNSMOS scores but much worse dWER compared to our WavLM baseline.
+Our findings indicate that using HuBERT as the SSL model results in slightly better DNSMOS scores but much worse dWER compared to our WavLM baseline.
 The improved DNSMOS scores likely stem from the vocoder performance, yet they do not adequately reflect speech intelligibility, which is crucial for speech separation tasks.
@@
 Finally, we observe a performance gap between discrete methods and continuous methods, as demonstrated by Continuous-WavLM-L6.
-Continuous-WavLM-L6 has the best performance in terms of DNSMOS and dWER among all the experiments, and it only uses the 6 layer output of WavLM. 
+Continuous-WavLM-L6 has the best performance in terms of DNSMOS and dWER among all the experiments while using only the 6th layer output of WavLM Large. 
 The gap in performance may be attributed to the information loss inherent in the discretization process. 
@@
 However, we observe a gap between discrete methods and continuous methods especially in speech intelligibility and speaker similarity.
-We will focus on shrinking
+Our future work will focus on shrinking
 this gap.

### 2024-12-23 src/paper.tex
update
u

@@
 
-\author{\IEEEauthorblockN{1\textsuperscript{st} Beilong Tang}
-\IEEEauthorblockA{\textit{Duke Kunshan University} \\
-% \textit{name of organization (of Aff.)}\\
-Kunshan, China \\
-bt132@duke.edu}
-\and
-\IEEEauthorblockN{2\textsuperscript{nd} Bang Zeng}
-\IEEEauthorblockA{\textit{Duke Kunshan University} \\
-% \textit{name of organization (of Aff.)}\\
-Kunshan, China \\
-zeng.bang@dukekunshan.edu.cn}
-% \and
-% \IEEEauthorblockN{3\textsuperscript{rd} Zhan Jin}
-% \IEEEauthorblockA{\textit{Duke Kunshan University} \\
-% Kunshan, China \\
-% zhan.jin@whu.edu.cn}
-\and
-\IEEEauthorblockN{3\textsuperscript{rd} Ming Li}
-\IEEEauthorblockA{\textit{Duke Kunshan University} \\
-% \textit{name of organization (of Aff.)}\\
-Kunshan, China \\
-ming.li369@dukekunshan.edu.cn}
-}
+\author{Anonymous ICME submission}
 
@@
 \begin{IEEEkeywords}
-target speaker extraction, speech separation, language models, audio discretization, self-supervised models
+target speaker extraction, audio discretization, language models, speech separation, self-supervised models
 \end{IEEEkeywords}
@@
     \label{model}
-    \vspace{-12pt}
+    \vspace{-4pt}
     \end{figure*}
@@
         \label{cross_attention}
-        \vspace{-17pt}
+        \vspace{-5pt}
         \end{figure}
@@
 SSL models have demonstrated outstanding performances across numerous downstream tasks \cite{superb}, as they extract continuous representations rich in semantic and timbral information from speech.
+In addition, some works \cite{laura} use neural audio codec for discretization.
+However, their performances on Speech Separation are limited \cite{dasb}.
 
@@
 We use the pretrained SSL model WavLM Large \cite{wavlm} to encode speech into continuous representations.
-Specifically, we extract the outputs from six hidden layers: 1, 3, 7, 12, 18, and 23.
+Specifically, we extract the outputs from six hidden layers: 1, 3, 7, 12, 18, and 23, following \cite{dasb}.
 Given a speech signal \(s \in \mathbb{R}^{T'}\), the output of WavLM is a tensor \(\bm{r}\) with shape \(n \times T \times E\), where \(n\) is the number of output layers (6 in this case), \(T\) is the time dimension, and \(E\) represents the embedding dimension.
@@
 \end{center}
-\vspace{-15.5pt}
+\vspace{-8pt}
   \end{table*}
@@
             \hline
-            \multirow{2}{*}{WavLM-L6}                              &  Discrete                          & 1.74    & 1.58    & 1.40   & 165.4                & 0.516\_d                        \\
+            \multirow{2}{*}{WavLM-L6}                              &  Discrete                          & 2.08    & 2.07    & 1.64   & 122.14                & 0.589\_d                        \\
             &  Hybrid                          & 3.54    & 3.93    & 3.18   & 29.3                & 0.838\_d                        \\
@@
       \end{center}
-      \vspace{-17pt}
+      \vspace{-8pt}
     \end{table}
@@
 \bibliographystyle{IEEEtran}
-\bibliography{references}
+\bibliography{paper}
 

### 2024-12-23 src/paper.tex
u

@@
 Our demos are available at
-\footnote{\href{https://beilong-tang.github.io/TSELM.demo/}{https://beilong-tang.github.io/TSELM.demo/}}.
+\footnote{\href{https://tselmdemo.github.io/TSELM.demo/}{https://tselmdemo.github.io/TSELM.demo/}}.
 
@@
 In TSELM-S-NoCat, we utilize the TSELM-S model architecture but abandon the mixture concatenation strategy in the encoding step.
-The code and pretrained models are available at \footnote{\href{https://github.com/Beilong-Tang/TSELM}{https://github.com/Beilong-Tang/TSELM}}.
+The code and pretrained models are available at \footnote{\href{https://github.com/tselmdemo/tselm}{https://github.com/tselmdemo/tselm}}.
 
